---
title: "Debug Code"
format: html
editor: visual
---

# Extra Debugging Code

### Check whether Unit x Avg Weight = Total Weight for every Unicode (result should only return TRUE and NA for check column)

```{r}
check_1 <- all_revenue_farm_new %>%
  mutate(check = round(Units * `Avg Weight`, 2) == round(`Total Weight`, 2)) 
check_1
```

### Check whether the same item has different Item Code (must return 0)

```{r}
check_2 <- volume_farm_raw %>%
  mutate(
    Unicode = toupper(Unicode),
    Abattoir = toupper(Abattoir),
    Month = toupper(Month),
    Tab = toupper(Tab)
  ) %>%
  group_by(Unicode, Abattoir, Month, Tab) %>%
  summarise(n_item_codes = n_distinct(`Item Code`), .groups = "drop") %>%
  filter(n_item_codes > 1)
check_2
```

### Checking Unmatched Customers (the result should ideally return 0)

```{r}
all_captured <- bind_rows(
  farm_sales_400000_10001812_new,
  farm_sales_400028_10001812_new,
  meat_sales_kill_400000_10201816_new,
  meat_sales_kill_400028_10201816_new,
  meat_sales_boning_400000_11901816_new,
  meat_sales_boning_400028_11901816_new,
  meat_sales_boxed_meat_400000_10501816_new,
  meat_sales_boxed_meat_400028_10501816_new,
  meat_sales_400000_10001814_new,
  laverton_sales_kill_400000_10201854_new,
  laverton_sales_kill_400028_10201854_new,
  laverton_sales_boning_400000_11901854_new,
  laverton_sales_boning_400028_11901854_new,
  laverton_sales_boxed_meat_400000_10501854_new,
  laverton_sales_boxed_meat_400028_10501854_new,
  edible_offal_sales_400000_10001816_new,
  inedible_offal_sales_400000_10801816_new,
  edible_offal_sales_400028_10001854_new,
  inedible_offal_sales_400000_10801854_new,
  corowa_6way_frz_400000_10501816_new,
  corowa_commodity_frz_400000_10501816_new,
  corowa_commodity_frz_400028_10501816_new,
  laverton_6way_frz_400028_10501854_new,
  laverton_6way_frz_400000_10501854_new,
  laverton_commodity_frz_400028_10501854_new,
  laverton_commodity_chil_400000_10501854_new,
  meat_trade_data_new,
  all_revenue_farm_new
)
check_3 <- customer_data %>%
  anti_join(all_captured, by = intersect(names(customer_data), names(all_captured)))
check_3
```

### Code to print out offal data before it was grouped

```{r}
Corowa_edible_check <- volume_bone_price_calculated %>%
  filter(Abattoir == "COROWA") %>%
  mutate(Type = toupper(Type)) %>%
  filter(Type %in% c("INEDIBLE", "OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL")
Laverton_edible_check <- volume_bone_price_calculated %>%
  filter(Abattoir == "LAVERTON") %>%
  mutate(Type = toupper(Type)) %>%
  filter(Type %in% c("INEDIBLE", "OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL")
write.csv(Corowa_edible_check, "Corowa_edible_check.csv", row.names = FALSE)
write.csv(Laverton_edible_check, "Laverton_edible_check.csv", row.names = FALSE)
```

### Check volume_commodity_corowa = 400000 + 400028 (The differences must be 0)

```{r}
total_combined <- sum(volume_commodity_corowa$`Total Weight`, na.rm = TRUE)
total_400000   <- sum(volume_commodity_corowa_400000$`Total Weight`, na.rm = TRUE)
total_400028   <- sum(volume_commodity_corowa_400028$`Total Weight`, na.rm = TRUE)
check_4 <- data.frame(
  total_combined  = total_combined,
  sum_400000_400028 = total_400000 + total_400028,
  difference      = total_combined - (total_400000 + total_400028)
)
```

### Check for negative Total Weight in volume_commodity_corowa_400000 (It must give 0 observations)

```{r}
check_5 <- volume_commodity_corowa_400000 %>%
  filter(`Total Weight` < 0)
```

### Check for item in VA procuments but not in commodity data for corowa

```{r}
anti_join(
  volume_commodity_corowa_400028 %>% distinct(`Item Code`),
  volume_commodity_corowa        %>% distinct(`Item Code`),
  by = "Item Code"
)
```

### Code to check for problem related to column

```{r}
lapply(list(
  all_revenue_offal_data_calculated,
  all_revenue_farm_calculated,
  all_revenue_6way_sow_data_calculated,
  all_revenue_commodity_corowa_calculated,
  all_revenue_commodity_laverton_calculated,
  all_revenue_meat_trade_data_calculated,
  all_revenue_meat_sales_data_calculated,
  all_revenue_new_team_calculated,
  all_vevenue_corowa_laverton_expense_farm),
       function(df) grep("\\.x$|\\.y$", names(df), value = TRUE))
```
