---
title: "Debug Code"
format: html
editor: visual
---

# Extra Debugging Code

### Check whether Unit x Avg Weight = Total Weight for every Unicode (result should only return TRUE and NA for check column)

```{r}
check_1 <- all_revenue_farm_new %>%
  mutate(check = round(Units * `Avg Weight`, 2) == round(`Total Weight`, 2)) 
check_1
```

### Check whether the same item has different Item Code (must return 0)

```{r}
check_2 <- volume_farm_raw %>%
  mutate(
    Unicode = toupper(Unicode),
    Abattoir = toupper(Abattoir),
    Month = toupper(Month),
    Tab = toupper(Tab)
  ) %>%
  group_by(Unicode, Abattoir, Month, Tab) %>%
  summarise(n_item_codes = n_distinct(`Item Code`), .groups = "drop") %>%
  filter(n_item_codes > 1)
check_2
```

### Checking Unmatched Customers (the result should ideally return 0)

```{r}
all_captured <- bind_rows(
  farm_sales_400000_10001812_new,
  farm_sales_400028_10001812_new,
  meat_sales_kill_400000_10201816_new,
  meat_sales_kill_400028_10201816_new,
  meat_sales_boning_400000_11901816_new,
  meat_sales_boning_400028_11901816_new,
  meat_sales_boxed_meat_400000_10501816_new,
  meat_sales_boxed_meat_400028_10501816_new,
  meat_sales_400000_10001814_new,
  laverton_sales_kill_400000_10201854_new,
  laverton_sales_kill_400028_10201854_new,
  laverton_sales_boning_400000_11901854_new,
  laverton_sales_boning_400028_11901854_new,
  laverton_sales_boxed_meat_400000_10501854_new,
  laverton_sales_boxed_meat_400028_10501854_new,
  edible_offal_sales_400000_10001816_new,
  inedible_offal_sales_400000_10801816_new,
  edible_offal_sales_400028_10001854_new,
  inedible_offal_sales_400000_10801854_new,
  corowa_6way_frz_400000_10501816_new,
  corowa_commodity_frz_400000_10501816_new,
  corowa_commodity_frz_400028_10501816_new,
  laverton_6way_frz_400028_10501854_new,
  laverton_6way_frz_400000_10501854_new,
  laverton_commodity_frz_400028_10501854_new,
  laverton_commodity_chil_400000_10501854_new,
  meat_trade_data_new,
  all_revenue_farm_new
)
check_3 <- customer_data %>%
  anti_join(all_captured, by = intersect(names(customer_data), names(all_captured)))
check_3
```

### Code to print out offal data before it was grouped

```{r}
Corowa_edible_check <- volume_bone_price_calculated %>%
  filter(Abattoir == "COROWA") %>%
  mutate(Type = toupper(Type)) %>%
  filter(Type %in% c("INEDIBLE", "OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL")
Laverton_edible_check <- volume_bone_price_calculated %>%
  filter(Abattoir == "LAVERTON") %>%
  mutate(Type = toupper(Type)) %>%
  filter(Type %in% c("INEDIBLE", "OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL")
write.csv(Corowa_edible_check, "Corowa_edible_check.csv", row.names = FALSE)
write.csv(Laverton_edible_check, "Laverton_edible_check.csv", row.names = FALSE)
```

### Check volume_commodity_corowa = 400000 + 400028 (The differences must be 0)

```{r}
total_combined <- sum(volume_commodity_corowa$`Total Weight`, na.rm = TRUE)
total_400000   <- sum(volume_commodity_corowa_400000$`Total Weight`, na.rm = TRUE)
total_400028   <- sum(volume_commodity_corowa_400028$`Total Weight`, na.rm = TRUE)
check_4 <- data.frame(
  total_combined  = total_combined,
  sum_400000_400028 = total_400000 + total_400028,
  difference      = total_combined - (total_400000 + total_400028)
)
```

### Check for negative Total Weight in volume_commodity_corowa_400000 (It must give 0 observations)

```{r}
check_5 <- volume_commodity_corowa_400000 %>%
  filter(`Total Weight` < 0)
```

### Check for item in VA procuments but not in commodity data for corowa (ideally should be 0)

```{r}
check_6 <- anti_join(
  volume_commodity_corowa_400028 %>% distinct(`Item Code`),
  volume_commodity_corowa        %>% distinct(`Item Code`),
  by = "Item Code"
)
```

### Code to check for problem related to column (should be 0)

```{r}
check_7 <- lapply(list(final_file),
       function(df) grep("\\.x$|\\.y$", names(df), value = TRUE))
```

### Check if carcass price exists for Laverton unicodes (NA means no price found for that unicode/period)

```{r}
laverton_unicodes <- c("FLAVERTON6WAY", "LAVERTON6WAY", "LAVERTONCOMMODITY", "FLAVERTONCOMMODITY",
                       "FLAVERTONSOW COMMODITY", "FLAVERTONOTHERS(SOW)", "FLAVERTONPW OPPORTUNITY - SOW")

carcass_price_laverton_check <- carcass_price_data %>%
  mutate(`Farm Unicode` = toupper(str_trim(`Farm Unicode`)), Abattoir = toupper(Abbatoir)) %>%
  filter(`Farm Unicode` %in% laverton_unicodes, Abattoir == "LAVERTON") %>%
  pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Carcass Price") %>%
  mutate(Period = as.integer(Period)) %>%
  select(`Farm Unicode`, Abattoir, Period, `Carcass Price`)

# Summary: which unicodes have prices and which are missing entirely
check_8 <- data.frame(Unicode = laverton_unicodes) %>%
  mutate(Has_Price = Unicode %in% carcass_price_laverton_check$`Farm Unicode`)
```

### Check total Value for laverton_farm_510167_10501854_calculated

```{r}
sum(volume_6way_sow_laverton %>% filter(`Customer Group` == "6 Way") %>% pull(Value), na.rm = TRUE)
```

### Check which Item has positive Total Weight but has no price input (must be 0 for both checks)

```{r}
check_9 <- volume_va_raw %>%
  filter(`Service` == "Procurement") %>%
  mutate(
    Tab            = toupper(Tab),
    Abattoir       = toupper(Abattoir),
    Month          = toupper(Month),
    Units          = as.numeric(Units),
    `Avg Weight`   = as.numeric(`Avg Weight`),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code`    = str_trim(`Item Code`),
    Period         = match(Month, toupper(month.name))
  ) %>%
  left_join(
    item_price_data,
    by = c("Item Code" = "Item Key")
  ) %>%
  filter(`Total Weight` > 0, is.na(`Current Price`) | `Current Price` == 0) %>%
  arrange(`Item Code`)

check_10 <- volume_va_raw %>%
  filter(`Service` == "VA Sales") %>%
  mutate(
    Tab            = toupper(Tab),
    Abattoir       = toupper(Abattoir),
    Month          = toupper(Month),
    Units          = as.numeric(Units),
    `Avg Weight`   = as.numeric(`Avg Weight`),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code`    = str_trim(`Item Code`),
    Period         = match(Month, toupper(month.name))
  ) %>%
  left_join(
    item_price_data,
    by = c("Item Code" = "Item Key")
  ) %>%
  filter(`Total Weight` > 0, is.na(`Price`) | `Price` == 0) %>%
  arrange(`Item Code`)
```

### Code to check which item does not have packaging price for meat sales

```{r}
check_11 <- volume_expense_VA_sales_packaging_calculated %>%
  filter(`Total Weight` > 0, is.na(Price) | Price == 0) %>%
  group_by(`Item Code`, `Item Description`, Price) %>%
  summarise(`Total Weight` = sum(`Total Weight`, na.rm = TRUE), .groups = "drop") %>%
  arrange(`Item Code`)
```

### Code to check which item does not have packaging and Pallet price

```{r}
check_12 <- laverton_edible_offal_volume_data %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PACKAGING) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  filter(`Total Weight` > 0, is.na(PACKAGING) | PACKAGING == 0) %>%
  group_by(`Item Code`, `Item Description`, PACKAGING) %>%
  summarise(`Total Weight` = sum(`Total Weight`, na.rm = TRUE), .groups = "drop") %>%
  arrange(`Item Code`)

check_13 <- laverton_edible_offal_volume_data %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PALLETS) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  filter(`Total Weight` > 0, is.na(PALLETS) | PALLETS == 0) %>%
  group_by(`Item Code`, `Item Description`, PALLETS) %>%
  summarise(`Total Weight` = sum(`Total Weight`, na.rm = TRUE), .groups = "drop") %>%
  arrange(`Item Code`)
```

```{r}
sum(volume_offal_laverton$Value, na.rm = TRUE)
sum(corowa_edible_offal_freight_ocean_500609_10001816_calculated$Value, na.rm = TRUE)
sum(meat_trade_storage_data_calculated$Value, na.rm = TRUE)

sum(corowa_volume_6way_freight$`Total Weight`, na.rm = TRUE)
sum(corowa_volume_commodity_freight$`Total Weight`, na.rm = TRUE)
sum(corowa_volume_meat_trade_freight$`Total Weight`, na.rm = TRUE)

sum(all_expense_packaging_pallet_calculated$`Total Weight`, na.rm = TRUE)
sum(laverton_export_packaging_650301_10201854_calculated$Value, na.rm = TRUE)

```

```{r}
4989739+4939573+444003.3
```

### Code to check which item does not have packaging price for laverton 6way, sow, and commodity

```{r}
check_14 <- laverton_volume_6way_data %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PACKAGING) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  filter(`Total Weight` > 0, is.na(PACKAGING) | PACKAGING == 0) %>%
  group_by(`Item Code`, `Item Description`, PACKAGING) %>%
  summarise(`Total Weight` = sum(`Total Weight`, na.rm = TRUE), .groups = "drop") %>%
  arrange(`Item Code`)

check_15 <- laverton_volume_sow_data %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PACKAGING) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  filter(`Total Weight` > 0, is.na(PACKAGING) | PACKAGING == 0) %>%
  group_by(`Item Code`, `Item Description`, PACKAGING) %>%
  summarise(`Total Weight` = sum(`Total Weight`, na.rm = TRUE), .groups = "drop") %>%
  arrange(`Item Code`)

check_16 <- laverton_volume_commodity_data %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PACKAGING) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  filter(`Total Weight` > 0, is.na(PACKAGING) | PACKAGING == 0) %>%
  group_by(`Item Code`, `Item Description`, PACKAGING) %>%
  summarise(`Total Weight` = sum(`Total Weight`, na.rm = TRUE), .groups = "drop") %>%
  arrange(`Item Code`)

write.csv(check_15, "Sow missing packaging price.csv", row.names = FALSE)
write.csv(check_16, "Commodity missing packaging price.csv", row.names = FALSE)
```
