---
title: "Automating Financial Account Creation"
subtitle: "An R Pipeline for SOP-to-Database Reporting"
author: "Andy Tran"
date: "25 May 2026"
format:
  revealjs:
    theme: simple
    slide-number: true
    transition: fade
    fig-align: center
    smaller: true
    margin: 0.03
    width: 1500
    logo: jbs_logo.png
    include-in-header:
      text: |
        <style>
          .mermaid .nodeLabel,
          .mermaid .nodeLabel p,
          .mermaid foreignObject div {
            text-align: center !important;
            width: 100%;
          }
          .reveal .slides section {
            padding-left: 20px;
            padding-right: 20px;
          }
          .reveal .slide-logo {
            position: fixed;
            top: 10px;
            right: 10px;
            bottom: auto;
            max-height: 60px;
            max-width: 150px;
          }
          /* Slide title gold underline */
          .reveal h2 {
            color: #1a3a5c;
            border-bottom: 3px solid #f39c12;
            padding-bottom: 0.15em;
            margin-bottom: 0.3em;
          }
          /* Dark slide overrides - applied automatically by RevealJS */
          .reveal .has-dark-background h2 {
            color: #ffffff !important;
            border-bottom-color: #f39c12 !important;
          }
          .reveal .has-dark-background p,
          .reveal .has-dark-background li {
            color: #e8f4fd !important;
          }
          .reveal .has-dark-background strong {
            color: #f8c471 !important;
          }
          .reveal .has-dark-background code {
            background: rgba(255,255,255,0.15) !important;
            color: #f0f8ff !important;
          }
          /* Blockquote */
          .reveal blockquote {
            background: #eaf4fc;
            border-left: 4px solid #2980b9;
            border-radius: 0 8px 8px 0;
            padding: 0.5em 1em;
            color: #1a3a5c;
            font-style: normal;
            width: 100%;
            box-shadow: none;
          }
          .reveal .has-dark-background blockquote {
            background: rgba(255,255,255,0.1) !important;
            border-left-color: #f39c12 !important;
            color: #e8f4fd !important;
          }
          /* Tables */
          .reveal table {
            font-size: 0.82em;
            border-collapse: collapse;
            width: 100%;
          }
          .reveal table thead th {
            background: #1a3a5c !important;
            color: white !important;
            padding: 0.4em 0.8em;
            text-align: left;
          }
          .reveal table tbody tr:nth-child(even) td {
            background: #f0f6fc;
          }
          .reveal table tbody td {
            padding: 0.3em 0.8em;
            border-bottom: 1px solid #d6eaf8;
          }
          /* Dark-background coverage matrix table */
          .dark-table {
            border-collapse: separate !important;
            border-spacing: 0 6px !important;
            font-size: 0.68em !important;
          }
          .dark-table thead th {
            background: #0d2137 !important;
            color: #aed6f1 !important;
            font-weight: 700 !important;
            text-transform: uppercase !important;
            letter-spacing: 0.07em !important;
            border-bottom: none !important;
            text-align: center !important;
            padding: 0.55em 0.9em !important;
          }
          .dark-table thead th:first-child { border-radius: 6px 0 0 6px !important; text-align: left !important; }
          .dark-table thead th:last-child  { border-radius: 0 6px 6px 0 !important; }
          .dark-table tbody td {
            border-bottom: none !important;
            padding: 0.5em 0.9em !important;
            vertical-align: middle !important;
            text-align: center !important;
          }
          .dark-table tbody td:first-child { text-align: left !important; border-radius: 6px 0 0 6px !important; }
          .dark-table tbody td:last-child  { border-radius: 0 6px 6px 0 !important; }
          .dark-table tbody tr:nth-child(odd)  td { background: rgba(255,255,255,0.08) !important; }
          .dark-table tbody tr:nth-child(even) td { background: rgba(255,255,255,0.05) !important; }
          .gl-badge, .gl-badge-blue {
            display: inline-block;
            background: rgba(174,214,241,0.15);
            color: #aed6f1;
            border: 1px solid rgba(174,214,241,0.35);
            border-radius: 5px;
            padding: 0.15em 0.55em;
          }
          .cell-sub { display: block; color: #ffffff; font-size: 0.82em; margin-top: 2px; }
          .row-sub  { color: #ffffff; font-size: 0.85em; font-weight: 400; }
          .cell-empty { color: #3a5570; font-size: 1.1em; }
        </style>
execute:
  echo: false
  warning: false
  message: false
---

## Context & Motivation {background-color="#f0f6fc"}

::: {style="display:grid; grid-template-columns:1fr 50px 1fr; row-gap:0.75em; align-items:center; font-size:0.82em; margin-top:0.3em;"}

::: {style="text-align:center; font-weight:700; color:#c0392b; text-transform:uppercase; letter-spacing:0.07em; padding-bottom:0.2em;"}
❌ Excel Pipeline
:::
::: {}
:::
::: {style="text-align:center; font-weight:700; color:#27ae60; text-transform:uppercase; letter-spacing:0.07em; padding-bottom:0.2em;"}
✅ R Pipeline
:::

::: {style="background:#fdecea; border-left:4px solid #c0392b; border-radius:0 8px 8px 0; padding:0.55em 0.9em;"}
📋 **Requires manual adjustment every period**
:::
::: {style="text-align:center; font-size:1.6em; color:#95a5a6;"}
→
:::
::: {style="background:#eafaf1; border-left:4px solid #27ae60; border-radius:0 8px 8px 0; padding:0.55em 0.9em;"}
⚡ **One condition tweak refreshes everything**
:::

::: {style="background:#fdecea; border-left:4px solid #c0392b; border-radius:0 8px 8px 0; padding:0.55em 0.9em;"}
🐛 **Hard-coded, error-prone & inflexible**
:::
::: {style="text-align:center; font-size:1.6em; color:#95a5a6;"}
→
:::
::: {style="background:#eafaf1; border-left:4px solid #27ae60; border-radius:0 8px 8px 0; padding:0.55em 0.9em;"}
🔧 **Modular, flexible & easy to fix**
:::

::: {style="background:#fdecea; border-left:4px solid #c0392b; border-radius:0 8px 8px 0; padding:0.55em 0.9em;"}
📊 **20+ sheets - chaotic, impossible to follow**
:::
::: {style="text-align:center; font-size:1.6em; color:#95a5a6;"}
→
:::
::: {style="background:#eafaf1; border-left:4px solid #27ae60; border-radius:0 8px 8px 0; padding:0.55em 0.9em;"}
📖 **Clean, readable, traceable logic**
:::

:::

------------------------------------------------------------------------

## Input Data Sources

| File | Contents | Role in Pipeline |
|------------------------|------------------------|------------------------|
| `SOP Volumes.xlsx` | Weekly volumes by Farm / Bone / VA tabs | Primary volume source |
| `Prices.xlsb` | Carcass price, Kill fee, Bone fee, Item prices | Value calculation |
| `Master Data.xlsx` | GL accounts, Cost centre keys, Customer list | Account structure |
| `Trade Allowance.xlsx` | Trade discount rates per customer | Expense accounts |
| `Rates & Allocation.xlsx` | VA brand allocations, freight & storage rates | Expense accounts |

> All files are read directly from a shared OneDrive folder so the pipeline always uses the latest version.

------------------------------------------------------------------------

## Pipeline Structure {background-color="#f8fafd"}

::: {.r-stretch}
```{mermaid}
%%{init: {'flowchart': {'nodeSpacing': 40, 'rankSpacing': 60}}}%%
flowchart TD
    subgraph ext ["Other Teams"]
        A["SOP Volumes.xlsx<br/>S&OP Team"]
        B["Prices.xlsb<br/>Sales Team"]
        C["Trade Allow.xlsx<br/>BP Manager"]
        D["Rates & Alloc.xlsx<br/>BP Manager"]
    end

    subgraph fin ["Finance Team"]
        M["Master Data.xlsx<br/>NAM & Comm. Finance"]
    end

    subgraph dev ["Development & QA"]
        DC["Debug Code (Development Checks)"]
        DC --> G["Gap_Check.R (QA Tool)"]
    end

    A  --> FV["Financial Values (Volume × Price)"]
    B  --> FV
    B  --> ED

    M  --> RA["Revenue Accounts"]
    M  --> EA["Expense Accounts"]

    FV --> RD["Revenue Data"]
    RA --> RD

    FV --> ED["Expense Data"]
    EA --> ED
    C  --> ED
    D  --> ED

    RD --> DB[("Financial Database")]
    ED --> DB

    DB <--> G

    classDef extNode fill:#fad7a0,stroke:#ca6f1e,color:#1a5276,font-size:12px
    classDef finNode fill:#a9dfbf,stroke:#1e8449,color:#1a5276,font-size:12px
    classDef devNode fill:#d7bde2,stroke:#7d3c98,color:#1a5276,font-size:12px
    classDef pipeNode fill:#d6eaf8,stroke:#2980b9,color:#1a5276,font-size:12px

    class A,B,C,D extNode
    class M finNode
    class DC,G devNode
    class FV,RA,EA,RD,ED,DB pipeNode

    style ext fill:#fef9e7,stroke:#ca6f1e,color:#ca6f1e,font-size:13px
    style fin fill:#d5f5e3,stroke:#1e8449,color:#1e8449,font-size:13px
    style dev fill:#f4ecf7,stroke:#7d3c98,color:#7d3c98,font-size:13px
```
:::

------------------------------------------------------------------------

## Revenue Accounts - Core Logic

Three steps are applied to **every** Business Unit:

::::: columns
::: {.column width="48%"}
::: {style="background: #f0f6fc; border-top: 3px solid #1a3a5c; border-radius: 0 0 8px 8px; padding: 0.5em 0.8em; margin-bottom: 0.3em;"}
::: {style="font-size: 0.7em; font-weight: 700; color: #1a3a5c; text-transform: uppercase; letter-spacing: 0.06em; margin-bottom: 0.2em;"}
Step 1 - Build account skeleton
:::

``` r
# Pull all relevant customers from Master Data
# and attach the correct GL + Cost Centre key
account_rows <- customer_data %>%
  filter(BU == "1.Farming Operations") %>%
  left_join(gl_cc_data, by = "BU") %>%
  crossing(Period = 1:12)  # one row per month
```
:::

::: {style="background: #f0f6fc; border-top: 3px solid #2980b9; border-radius: 0 0 8px 8px; padding: 0.5em 0.8em;"}
::: {style="font-size: 0.7em; font-weight: 700; color: #2980b9; text-transform: uppercase; letter-spacing: 0.06em; margin-bottom: 0.2em;"}
Step 2 - Join SOP volume
:::

``` r
# Match on SOP Unicode + Abattoir + Month + Tab
account_rows %>%
  left_join(volume_farm_raw,
            by = c("SOP Unicode" = "Unicode",
                   "Abattoir", "Month", "Tab"))
```
:::
:::

::: {.column width="48%"}
::: {style="background: #f0f6fc; border-top: 3px solid #f39c12; border-radius: 0 0 8px 8px; padding: 0.5em 0.8em; margin-bottom: 0.3em;"}
::: {style="font-size: 0.7em; font-weight: 700; color: #e67e22; text-transform: uppercase; letter-spacing: 0.06em; margin-bottom: 0.2em;"}
Step 3 - Calculate value
:::

``` r
# Different formula per tab type
mutate(Value = case_when(
  Tab == "FARM" ~ Total_Weight * Carcass_Price,
  Tab == "KILL" ~ Units * Kill_Fee,
  Tab == "BONE" ~ Units * Bone_Fee
))
```
:::

::: {style="background: #f8f9fa; border: 1px solid #d6eaf8; border-radius: 8px; padding: 0.5em 0.8em;"}
::: {style="font-size: 0.7em; font-weight: 700; color: #1a3a5c; text-transform: uppercase; letter-spacing: 0.06em; margin-bottom: 0.2em;"}
Mock result after all three steps
:::

```{r}
library(dplyr)
library(knitr)

tibble(
  Tab        = c("FARM", "KILL", "BONE"),
  Units      = c(120L,   120L,   85L),
  `Weight (kg)` = c(18500, 18500, 12000),
  `Price`    = c("$3.25/kg", "$45.50/hd", "$28.00/hd"),
  `Value ($)` = c(60125, 5460, 2380)
) |> kable("simple")
```
:::
:::
:::::

------------------------------------------------------------------------

## Revenue Account Coverage {background-color="#1a3a5c"}

<div style="display:flex; width:100%; margin-bottom:0.7em; font-size:0.82em;">
<span style="background:rgba(41,128,185,0.3); border:1px solid #2980b9; border-radius:6px; padding:0.25em 0.8em; color:#aed6f1;"><strong>General Ledger (GL) 400000</strong> - External customers</span>
<span style="margin-left:auto; background:rgba(243,156,18,0.2); border:1px solid #f39c12; border-radius:6px; padding:0.25em 0.8em; color:#f8c471;"><strong>General Ledger (GL) 400028</strong> - Intercompany (JBS sites)</span>
</div>

<div style="display:grid; grid-template-columns:1fr 1fr; gap:0.6em; font-size:0.78em;">

<div style="background:rgba(255,255,255,0.07); border:1px solid rgba(41,128,185,0.45); border-radius:10px; padding:0.6em 0.9em;">
<div style="font-weight:700; text-transform:uppercase; letter-spacing:0.07em; color:#aed6f1; margin-bottom:0.55em; font-size:0.85em;">📍 Corowa</div>
<div style="display:flex; flex-direction:column; gap:0.7em;">
<div style="display:flex; flex-wrap:nowrap; gap:0.4em;">
<span style="background:rgba(41,128,185,0.25); border:1px solid rgba(41,128,185,0.5); border-radius:20px; padding:0.2em 0.65em; color:#d6eaf8; white-space:nowrap;">🌾 Farming Operations</span>
<span style="background:rgba(41,128,185,0.25); border:1px solid rgba(41,128,185,0.5); border-radius:20px; padding:0.2em 0.65em; color:#d6eaf8; white-space:nowrap;">🔪 Kill Floor</span>
<span style="background:rgba(41,128,185,0.25); border:1px solid rgba(41,128,185,0.5); border-radius:20px; padding:0.2em 0.65em; color:#d6eaf8; white-space:nowrap;">🦴 Boning Room</span>
</div>
<div style="display:flex; flex-wrap:nowrap; gap:0.4em;">
<span style="background:rgba(41,128,185,0.25); border:1px solid rgba(41,128,185,0.5); border-radius:20px; padding:0.2em 0.65em; color:#d6eaf8; white-space:nowrap;">📦 Boxed Meat</span>
<span style="background:rgba(41,128,185,0.25); border:1px solid rgba(41,128,185,0.5); border-radius:20px; padding:0.2em 0.65em; color:#d6eaf8; white-space:nowrap;">🫀 Offal (Edible & Inedible)</span>
</div>
<div style="display:flex; flex-wrap:nowrap; gap:0.4em;">
<span style="background:rgba(41,128,185,0.25); border:1px solid rgba(41,128,185,0.5); border-radius:20px; padding:0.2em 0.65em; color:#d6eaf8; white-space:nowrap;">🐷 Commodity Bone</span>
<span style="background:rgba(41,128,185,0.25); border:1px solid rgba(41,128,185,0.5); border-radius:20px; padding:0.2em 0.65em; color:#d6eaf8; white-space:nowrap;">🤝 Meat Trade</span>
</div>
</div>
</div>

<div style="display:flex; flex-direction:column; gap:0.5em;">
<div style="background:rgba(255,255,255,0.07); border:1px solid rgba(39,174,96,0.4); border-radius:10px; padding:0.6em 0.9em;">
<div style="font-weight:700; text-transform:uppercase; letter-spacing:0.07em; color:#a9dfbf; margin-bottom:0.55em; font-size:0.85em;">📍 Laverton</div>
<div style="display:flex; flex-direction:column; gap:0.7em;">
<div style="display:flex; flex-wrap:nowrap; gap:0.4em;">
<span style="background:rgba(39,174,96,0.2); border:1px solid rgba(39,174,96,0.45); border-radius:20px; padding:0.2em 0.65em; color:#a9dfbf; white-space:nowrap;">🏭 Laverton Processing</span>
<span style="background:rgba(39,174,96,0.2); border:1px solid rgba(39,174,96,0.45); border-radius:20px; padding:0.2em 0.65em; color:#a9dfbf; white-space:nowrap;">🔪 Kill Floor</span>
<span style="background:rgba(39,174,96,0.2); border:1px solid rgba(39,174,96,0.45); border-radius:20px; padding:0.2em 0.65em; color:#a9dfbf; white-space:nowrap;">🦴 Boning Room</span>
</div>
<div style="display:flex; flex-wrap:nowrap; gap:0.4em;">
<span style="background:rgba(39,174,96,0.2); border:1px solid rgba(39,174,96,0.45); border-radius:20px; padding:0.2em 0.65em; color:#a9dfbf; white-space:nowrap;">📦 Boxed Meat</span>
<span style="background:rgba(39,174,96,0.2); border:1px solid rgba(39,174,96,0.45); border-radius:20px; padding:0.2em 0.65em; color:#a9dfbf; white-space:nowrap;">🫀 Offal (Edible → Corowa)</span>
</div>
<div style="display:flex; flex-wrap:nowrap; gap:0.4em;">
<span style="background:rgba(39,174,96,0.2); border:1px solid rgba(39,174,96,0.45); border-radius:20px; padding:0.2em 0.65em; color:#a9dfbf; white-space:nowrap;">🐷 Commodity Chilled & Frozen</span>
<span style="background:rgba(39,174,96,0.2); border:1px solid rgba(39,174,96,0.45); border-radius:20px; padding:0.2em 0.65em; color:#a9dfbf; white-space:nowrap;">🐖 Sow Bone</span>
</div>
</div>
</div>

<div style="background:rgba(243,156,18,0.12); border:1px solid rgba(243,156,18,0.4); border-radius:10px; padding:0.55em 0.9em;">
<div style="font-weight:700; text-transform:uppercase; letter-spacing:0.07em; color:#f8c471; margin-bottom:0.45em; font-size:0.85em;">🔗 Cross-Site</div>
<div style="display:flex; flex-wrap:wrap; gap:0.4em;">
<span style="background:rgba(243,156,18,0.2); border:1px solid rgba(243,156,18,0.45); border-radius:20px; padding:0.2em 0.65em; color:#fdebd0; white-space:nowrap;">💎 VA / Meat Sales </span>
</div>
</div>
</div>

</div>

------------------------------------------------------------------------

## Expense Accounts - Core Logic

Same skeleton approach as revenue - account rows built from Master Data, then rates joined from external files.

::::: columns
::: {.column width="50%"}
::: {style="background: #f0f6fc; border-top: 3px solid #1a3a5c; border-radius: 0 0 8px 8px; padding: 0.5em 0.8em; margin-bottom: 0.3em;"}
::: {style="font-size: 0.7em; font-weight: 700; color: #1a3a5c; text-transform: uppercase; letter-spacing: 0.06em; margin-bottom: 0.2em;"}
Rate sources per category
:::

```{r}
tibble(
  Category      = c("Packaging & Pallet", "Trade Allowance", "Storage", "Freight"),
  `Rate Source` = c("Prices.xlsb - Packaging VA sheet",
                    "Trade Allowance.xlsx",
                    "Rates & Allocation.xlsx",
                    "Rates & Allocation.xlsx")
) |> kable("simple")
```
:::

::: {style="background: #f0f6fc; border-top: 3px solid #2980b9; border-radius: 0 0 8px 8px; padding: 0.5em 0.8em;"}
::: {style="font-size: 0.7em; font-weight: 700; color: #2980b9; text-transform: uppercase; letter-spacing: 0.06em; margin-bottom: 0.2em;"}
Value formula
:::

``` r
# Expense value = total weight × rate
mutate(Value = `Total Weight` * Rate)
```
:::
:::

::: {.column width="46%"}
::: {style="background: #f8f9fa; border: 1px solid #d6eaf8; border-radius: 8px; padding: 0.5em 0.8em;"}
::: {style="font-size: 0.7em; font-weight: 700; color: #1a3a5c; text-transform: uppercase; letter-spacing: 0.06em; margin-bottom: 0.2em;"}
Mock result after rate join
:::

```{r}
tibble(
  Category     = c("Packaging", "Trade Allow.", "Storage", "Freight"),
  `Weight (kg)`= c(18500, 18500, 18500, 18500),
  `Rate ($/kg)` = c(0.12, 0.05, 0.08, 0.15),
  `Value ($)`  = c(2220, 925, 1480, 2775)
) |> kable("simple")
```
:::
:::
:::::

------------------------------------------------------------------------

## Expense Account Coverage {background-color="#1a3a5c"}

```{=html}
<table class="dark-table" style="width:100%; margin-top:0.5em;">
  <thead>
    <tr>
      <th>Location / Category</th>
      <th>Packaging &amp; Pallet</th>
      <th>Trade Allowance</th>
      <th>Storage</th>
      <th>Freight</th>
    </tr>
  </thead>
  <tbody>
    <tr>
      <td style="color:#e8f4fd; font-weight:600;">Corowa</td>
      <td><span class="gl-badge">GL 650301</span></td>
      <td><span class="cell-empty">-</span></td>
      <td><span class="gl-badge">GL 730010</span></td>
      <td>
        <span class="gl-badge">500192</span>
        <span class="gl-badge" style="margin-left:4px;">500609</span>
        <span class="cell-sub">Domestic + Export</span>
      </td>
    </tr>
    <tr>
      <td style="color:#e8f4fd; font-weight:600;">Laverton</td>
      <td><span class="gl-badge">GL 650301</span></td>
      <td><span class="gl-badge-blue">GL 450050</span></td>
      <td><span class="gl-badge">GL 730010</span></td>
      <td>
        <span class="gl-badge">500192</span>
        <span class="cell-sub">Domestic</span>
      </td>
    </tr>
    <tr>
      <td style="color:#e8f4fd; font-weight:600;">
        Meat Sales / VA
        <span class="row-sub"><br/>VA Products</span>
      </td>
      <td><span class="gl-badge">GL 650301</span></td>
      <td><span class="gl-badge-blue">GL 450050</span></td>
      <td><span class="gl-badge">GL 730010</span></td>
      <td>
        <span class="gl-badge">500192</span>
        <span class="cell-sub">Domestic</span>
      </td>
    </tr>
    <tr>
      <td style="color:#e8f4fd; font-weight:600;">
        Special Contracts
        <span class="row-sub"><br/>Woolworths · DRJ</span>
      </td>
      <td>
        <span class="gl-badge">GL 650311</span>
        <span class="cell-sub">Margin account</span>
      </td>
      <td><span class="cell-empty">-</span></td>
      <td><span class="cell-empty">-</span></td>
      <td><span class="cell-empty">-</span></td>
    </tr>
  </tbody>
</table>
```

------------------------------------------------------------------------

## Key Challenges {background-color="#1a2840"}

::: {.r-stretch}
```{mermaid}
%%{init: {'flowchart': {'nodeSpacing': 22, 'rankSpacing': 110}, 'theme': 'base', 'themeVariables': {'background': '#1a2840', 'mainBkg': '#1a2840', 'lineColor': '#5d7a8a', 'edgeLabelBackground': '#1a2840'}}}%%
flowchart LR

    subgraph ch["⚠️  CHALLENGE"]
        C1["<span style='font-size:1.15em;font-weight:bold;'>Unstable Source Data</span><br/><br/>Spelling mistakes &amp;<br/>inconsistent naming<br/>in SOP Volumes"]
        C2["<span style='font-size:1.15em;font-weight:bold;'>Incomplete Price Data</span><br/><br/>Prices.xlsb missing<br/>item codes &amp;<br/>packaging rates"]
        C3["<span style='font-size:1.15em;font-weight:bold;'>Complex Contracts</span><br/><br/>Individual discounts<br/>&amp; pricing negotiated<br/>per customer"]
    end

    subgraph co["⚡  CONSEQUENCE"]
        I1["<span style='font-size:1.15em;font-weight:bold;'>Joins break silently</span><br/><br/>Volume rows lost<br/>with no error raised"]
        I2["<span style='font-size:1.15em;font-weight:bold;'>NA revenue values</span><br/><br/>Expense rows<br/>fail silently"]
        I3["<span style='font-size:1.15em;font-weight:bold;'>Separate GL accounts</span><br/><br/>Conditional logic<br/>multiplies per contract"]
    end

    subgraph so["✅  SOLUTION"]
        S1["<span style='font-size:1.15em;font-weight:bold;'>str_trim · toupper</span><br/><br/>Typo corrections<br/>applied at load time"]
        S2["<span style='font-size:1.15em;font-weight:bold;'>Gap Check built</span><br/><br/>Surfaces every missing<br/>price row after each run"]
        S3["<span style='font-size:1.15em;font-weight:bold;'>Conditional branches</span><br/><br/>Pipeline logic split<br/>per contract type"]
    end

    C1 --> I1 --> S1
    C2 --> I2 --> S2
    C3 --> I3 --> S3

    classDef chBlue   fill:#1a3a5c,stroke:#2980b9,stroke-width:3px,color:#e8f4fd
    classDef impBlue  fill:#0d2137,stroke:#2980b9,stroke-width:1px,color:#aed6f1
    classDef solBlue  fill:#1e4976,stroke:#5dade2,stroke-width:2px,color:#aed6f1

    classDef chAmber  fill:#4a2c00,stroke:#f39c12,stroke-width:3px,color:#fef9e7
    classDef impAmber fill:#2d1a00,stroke:#f39c12,stroke-width:1px,color:#f8c471
    classDef solAmber fill:#5d3800,stroke:#f5b041,stroke-width:2px,color:#f8c471

    classDef chPurp   fill:#3d1a5c,stroke:#a569bd,stroke-width:3px,color:#f5eef8
    classDef impPurp  fill:#2d1040,stroke:#a569bd,stroke-width:1px,color:#d7bde2
    classDef solPurp  fill:#4a2070,stroke:#c39bd3,stroke-width:2px,color:#d7bde2

    class C1 chBlue
    class I1 impBlue
    class S1 solBlue
    class C2 chAmber
    class I2 impAmber
    class S2 solAmber
    class C3 chPurp
    class I3 impPurp
    class S3 solPurp

    style ch fill:#0d1a2e,stroke:#2980b9,stroke-width:1px,color:#aed6f1
    style co fill:#0d1a2e,stroke:#f39c12,stroke-width:1px,color:#f8c471
    style so fill:#0d1a2e,stroke:#a569bd,stroke-width:1px,color:#d7bde2
```
:::

------------------------------------------------------------------------

## Quality Assurance - Gap Check

::: {style="background: #eaf4fc; border-left: 4px solid #2980b9; border-radius: 0 8px 8px 0; padding: 0.4em 0.9em; color: #1a3a5c; margin-bottom: 0.3em;"}
Built from real failure points during development - each check represents a problem that once caused **silent data loss**. Unlike manual Excel review, R pinpoints the exact item, month and site instantly.
:::

```{=html}
<p style="font-size:0.76em; color:#1a3a5c; margin:0.2em 0 0.55em 0;">
  <b>Sheet 1</b> reconciles SOP raw weight vs database across 12 categories - a <code>GAP</code> flag pinpoints exactly which segment lost data.
  <b>Sheet 2</b> catches 8 failure types, grouped below:
</p>

<div style="display:grid; grid-template-columns:1fr 1fr; gap:0.65em; font-size:0.72em;">

  <!-- Naming Issues -->
  <div style="background:#eaf4fc; border-top:3px solid #2980b9; border-radius:0 0 8px 8px; padding:0.6em 0.9em;">
    <div style="font-weight:700; color:#1a5276; text-transform:uppercase; letter-spacing:0.07em; margin-bottom:0.45em;">🏷️ Naming Issues</div>
    <div style="margin-bottom:0.35em;">
      <div style="font-weight:600; color:#2980b9;">Item cannot be matched to a product category</div>
      <div style="color:#5d6d7e;">→ Incorrectly named value in source data</div>
    </div>
    <div>
      <div style="font-weight:600; color:#2980b9;">Item missing storage type classification</div>
      <div style="color:#5d6d7e;">→ Missing essential label in source data</div>
    </div>
  </div>

  <!-- Missing Prices -->
  <div style="background:#fef5e7; border-top:3px solid #e67e22; border-radius:0 0 8px 8px; padding:0.6em 0.9em;">
    <div style="font-weight:700; color:#7d4e00; text-transform:uppercase; letter-spacing:0.07em; margin-bottom:0.45em;">💰 Missing Prices</div>
    <div style="margin-bottom:0.35em;">
      <div style="font-weight:600; color:#e67e22;">Item has no revenue price assigned</div>
      <div style="color:#5d6d7e;">→ New product not yet in price reference file</div>
    </div>
    <div>
      <div style="font-weight:600; color:#e67e22;">Item sold at zero or missing price</div>
      <div style="color:#5d6d7e;">→ Sale record with blank or zero price</div>
    </div>
  </div>

  <!-- Missing Fees -->
  <div style="background:#eafaf1; border-top:3px solid #27ae60; border-radius:0 0 8px 8px; padding:0.6em 0.9em;">
    <div style="font-weight:700; color:#1e5631; text-transform:uppercase; letter-spacing:0.07em; margin-bottom:0.45em;">📋 Missing Fees</div>
    <div style="margin-bottom:0.35em;">
      <div style="font-weight:600; color:#27ae60;">Volume has no Carcass Price</div>
      <div style="color:#5d6d7e;">→ Customer volume with no matching carcass price</div>
    </div>
    <div style="margin-bottom:0.35em;">
      <div style="font-weight:600; color:#27ae60;">Volume has no Bone Processing Fee</div>
      <div style="color:#5d6d7e;">→ Customer volume with no matching bone fee</div>
    </div>
    <div>
      <div style="font-weight:600; color:#27ae60;">Volume has no Kill Fee</div>
      <div style="color:#5d6d7e;">→ Customer volume with no matching kill fee</div>
    </div>
  </div>

  <!-- Inconsistency -->
  <div style="background:#f5eef8; border-top:3px solid #8e44ad; border-radius:0 0 8px 8px; padding:0.6em 0.9em;">
    <div style="font-weight:700; color:#4a235a; text-transform:uppercase; letter-spacing:0.07em; margin-bottom:0.45em;">⚖️ Inconsistency </div>
    <div>
      <div style="font-weight:600; color:#8e44ad;">Mismatch item in volume data</div>
      <div style="color:#5d6d7e;">→ Produce n item A but no item A found in storage</div>
    </div>
  </div>

</div>
```

------------------------------------------------------------------------

## Summary - Excel vs R {background-color="#f0f6fc"}

```{=html}
<div style="display:flex; flex-direction:column; gap:0.42em; font-size:0.73em; margin-top:0.3em;">

  <!-- Header row -->
  <div style="display:grid; grid-template-columns:21% 37% 4% 37%; align-items:center; gap:0.4em;">
    <div></div>
    <div style="text-align:center; font-weight:700; color:#922b21; text-transform:uppercase; letter-spacing:0.07em;">❌ Excel (Before)</div>
    <div></div>
    <div style="text-align:center; font-weight:700; color:#1e5631; text-transform:uppercase; letter-spacing:0.07em;">✅ R Pipeline (Now)</div>
  </div>

  <!-- Row 1 -->
  <div style="display:grid; grid-template-columns:21% 37% 4% 37%; align-items:center; gap:0.4em;">
    <div style="font-weight:600; color:#1a3a5c;">⏱️ Time to build</div>
    <div style="background:#fdecea; border:1px solid #e74c3c; border-radius:8px; padding:0.3em 0.7em; color:#7b241c;">Manual work required every period</div>
    <div style="text-align:center; color:#95a5a6; font-size:1.3em;">→</div>
    <div style="background:#eafaf1; border:1px solid #27ae60; border-radius:8px; padding:0.3em 0.7em; color:#1e5631;">One-click · under 10 minutes</div>
  </div>

  <!-- Row 2 -->
  <div style="display:grid; grid-template-columns:21% 37% 4% 37%; align-items:center; gap:0.4em;">
    <div style="font-weight:600; color:#1a3a5c;">🏢 Adding a Business Unit</div>
    <div style="background:#fdecea; border:1px solid #e74c3c; border-radius:8px; padding:0.3em 0.7em; color:#7b241c;">Copy, paste &amp; reformat an entire sheet</div>
    <div style="text-align:center; color:#95a5a6; font-size:1.3em;">→</div>
    <div style="background:#eafaf1; border:1px solid #27ae60; border-radius:8px; padding:0.3em 0.7em; color:#1e5631;">Add a filter condition + a join · minutes</div>
  </div>

  <!-- Row 3 -->
  <div style="display:grid; grid-template-columns:21% 37% 4% 37%; align-items:center; gap:0.4em;">
    <div style="font-weight:600; color:#1a3a5c;">🔄 Rule or contract change</div>
    <div style="background:#fdecea; border:1px solid #e74c3c; border-radius:8px; padding:0.3em 0.7em; color:#7b241c;">Manually update every affected cell</div>
    <div style="text-align:center; color:#95a5a6; font-size:1.3em;">→</div>
    <div style="background:#eafaf1; border:1px solid #27ae60; border-radius:8px; padding:0.3em 0.7em; color:#1e5631;">Change one line of code · re-run</div>
  </div>

  <!-- Row 4 -->
  <div style="display:grid; grid-template-columns:21% 37% 4% 37%; align-items:center; gap:0.4em;">
    <div style="font-weight:600; color:#1a3a5c;">🔍 Data error tracing</div>
    <div style="background:#fdecea; border:1px solid #e74c3c; border-radius:8px; padding:0.3em 0.7em; color:#7b241c;">Manually scan rows · easy to miss</div>
    <div style="text-align:center; color:#95a5a6; font-size:1.3em;">→</div>
    <div style="background:#eafaf1; border:1px solid #27ae60; border-radius:8px; padding:0.3em 0.7em; color:#1e5631;">Gap Check pinpoints exact item, month &amp; site</div>
  </div>

  <!-- Row 5 -->
  <div style="display:grid; grid-template-columns:21% 37% 4% 37%; align-items:center; gap:0.4em;">
    <div style="font-weight:600; color:#1a3a5c;">⚠️ Risk of human error</div>
    <div style="background:#fdecea; border:1px solid #e74c3c; border-radius:8px; padding:0.3em 0.7em; color:#7b241c;">High · copy-paste mistakes go unnoticed</div>
    <div style="text-align:center; color:#95a5a6; font-size:1.3em;">→</div>
    <div style="background:#eafaf1; border:1px solid #27ae60; border-radius:8px; padding:0.3em 0.7em; color:#1e5631;">Low · same logic applied consistently every run</div>
  </div>

  <!-- Row 6 -->
  <div style="display:grid; grid-template-columns:21% 37% 4% 37%; align-items:center; gap:0.4em;">
    <div style="font-weight:600; color:#1a3a5c;">📋 Advanced calculation</div>
    <div style="background:#fdecea; border:1px solid #e74c3c; border-radius:8px; padding:0.3em 0.7em; color:#7b241c;">Very tedious to set up complicated formula · imprecise &amp; incorrect</div>
    <div style="text-align:center; color:#95a5a6; font-size:1.3em;">→</div>
    <div style="background:#eafaf1; border:1px solid #27ae60; border-radius:8px; padding:0.3em 0.7em; color:#1e5631;">Fast and easy!!!</div>
  </div>

  <!-- Row 7 -->
  <div style="display:grid; grid-template-columns:21% 37% 4% 37%; align-items:center; gap:0.4em;">
    <div style="font-weight:600; color:#1a3a5c;">🛡️ Quality assurance</div>
    <div style="background:#fdecea; border:1px solid #e74c3c; border-radius:8px; padding:0.3em 0.7em; color:#7b241c;">Manual spot-check only</div>
    <div style="text-align:center; color:#95a5a6; font-size:1.3em;">→</div>
    <div style="background:#eafaf1; border:1px solid #27ae60; border-radius:8px; padding:0.3em 0.7em; color:#1e5631;">Automated Gap Check runs after every build</div>
  </div>

</div>
```

------------------------------------------------------------------------

## {background-color="#1a3a5c"}

<div style="display: flex; flex-direction: column; align-items: center; justify-content: center; height: 75vh; text-align: center; gap: 0.35em;">

<div style="font-size: 2.8em; font-weight: 700; color: #ffffff; letter-spacing: 0.04em; line-height: 1.1;">
Thank You
</div>


<div style="font-size: 1.1em; color: #aed6f1; font-style: italic; max-width: 700px; line-height: 1.4;">
Questions &amp; Discussion
</div>

<div style="margin-top: 0.6em; display: flex; gap: 2em; justify-content: center; flex-wrap: wrap;">

<div style="background: rgba(255,255,255,0.1); border: 1px solid rgba(255,255,255,0.25); border-radius: 10px; padding: 0.5em 1.1em; color: #ffffff;">
<div style="font-size: 0.7em; color: #aed6f1; text-transform: uppercase; letter-spacing: 0.08em; margin-bottom: 0.2em;">Presenter</div>
<div style="font-size: 0.95em; font-weight: 600;">Andy Tran</div>
</div>

<div style="background: rgba(255,255,255,0.1); border: 1px solid rgba(255,255,255,0.25); border-radius: 10px; padding: 0.5em 1.1em; color: #ffffff;">
<div style="font-size: 0.7em; color: #aed6f1; text-transform: uppercase; letter-spacing: 0.08em; margin-bottom: 0.2em;">Date</div>
<div style="font-size: 0.95em; font-weight: 600;">25 May 2026</div>
</div>

<div style="background: rgba(255,255,255,0.1); border: 1px solid rgba(255,255,255,0.25); border-radius: 10px; padding: 0.5em 1.1em; color: #ffffff;">
<div style="font-size: 0.7em; color: #aed6f1; text-transform: uppercase; letter-spacing: 0.08em; margin-bottom: 0.2em;">Unit</div>
<div style="font-size: 0.95em; font-weight: 600;">ETC5543</div>
</div>

</div>

<div style="margin-top: 0.6em; font-size: 0.75em; color: #7fb3d3;">
<em>Automating Financial Account Creation - An R Pipeline for SOP-to-Database Reporting</em>
</div>

</div>



