---
title: "Automating Financial Account Creation"
subtitle: "An R Pipeline for SOP-to-Database Reporting"
author: "Andy Tran"
date: "13 May 2026"
format:
  revealjs:
    theme: simple
    slide-number: true
    transition: fade
    fig-align: center
    smaller: true
    margin: 0.05
    width: 1500
    logo: jbs_logo.png
    include-in-header:
      text: |
        <style>
          .mermaid .nodeLabel,
          .mermaid .nodeLabel p,
          .mermaid foreignObject div {
            text-align: center !important;
            width: 100%;
          }
          .reveal .slides section {
            padding-left: 20px;
            padding-right: 20px;
          }
          .reveal .slide-logo {
            position: fixed;
            top: 10px;
            right: 10px;
            bottom: auto;
            max-height: 60px;
            max-width: 150px;
          }
        </style>
execute:
  echo: false
  warning: false
  message: false
---

## Context & Motivation

::::: columns
::: {.column width="50%"}
**The challenge**

-   Financial accounts for two processing sites (Corowa & Laverton) were built manually each reporting period
-   Data lives across multiple spreadsheets with different structures
-   Manual process is time-consuming and error-prone
-   Any missed row = wrong account value
:::

::: {.column width="50%"}
**The goal**

-   Build an automated R pipeline that reads raw SOP data and price files
-   Produces structured financial database entries covering every Business Unit
-   Includes a built-in quality check so errors can be caught before submission
:::
:::::

------------------------------------------------------------------------

## Input Data Sources

| File | Contents | Role in Pipeline |
|------------------------|------------------------|------------------------|
| `SOP Volumes.xlsx` | Weekly volumes by Farm / Bone / VA tabs | Primary volume source |
| `Prices.xlsb` | Carcass price, Kill fee, Bone fee, Item prices | Value calculation |
| `Master Data.xlsx` | GL accounts, Cost centre keys, Customer list | Account structure |
| `Trade Allowance.xlsx` | Trade discount rates per customer | Expense accounts |
| `Rates & Allocation.xlsx` | VA brand allocations, freight & storage rates | Expense accounts |

> All files are read directly from a shared OneDrive folder so the pipeline always uses the latest version.

------------------------------------------------------------------------

## Pipeline Architecture

::: {.r-stretch}
```{mermaid}
%%{init: {'flowchart': {'nodeSpacing': 40, 'rankSpacing': 60}}}%%
flowchart TD
    subgraph ext ["Other Teams"]
        A["SOP Volumes.xlsx<br/>S&OP Team"]
        B["Prices.xlsb<br/>Sales Team"]
        C["Trade Allow.xlsx<br/>BP Manager"]
        D["Rates & Alloc.xlsx<br/>BP Manager"]
    end

    subgraph fin ["Finance Team"]
        M["Master Data.xlsx<br/>NAM & Comm. Finance"]
    end

    subgraph dev ["Development & QA"]
        DC["Debug Code (Development Checks)"]
        DC --> G["Gap_Check.R (QA Tool)"]
    end

    A  --> FV["Financial Values (Volume × Price)"]
    B  --> FV
    B  --> ED

    M  --> RA["Revenue Accounts"]
    M  --> EA["Expense Accounts"]

    FV --> RD["Revenue Data"]
    RA --> RD

    FV --> ED["Expense Data"]
    EA --> ED
    C  --> ED
    D  --> ED

    RD --> DB[("Financial Database")]
    ED --> DB

    DB <--> G

    classDef extNode fill:#fad7a0,stroke:#ca6f1e,color:#1a5276,font-size:12px
    classDef finNode fill:#a9dfbf,stroke:#1e8449,color:#1a5276,font-size:12px
    classDef devNode fill:#d7bde2,stroke:#7d3c98,color:#1a5276,font-size:12px
    classDef pipeNode fill:#d6eaf8,stroke:#2980b9,color:#1a5276,font-size:12px

    class A,B,C,D extNode
    class M finNode
    class DC,G devNode
    class FV,RA,EA,RD,ED,DB pipeNode

    style ext fill:#fef9e7,stroke:#ca6f1e,color:#ca6f1e,font-size:13px
    style fin fill:#d5f5e3,stroke:#1e8449,color:#1e8449,font-size:13px
    style dev fill:#f4ecf7,stroke:#7d3c98,color:#7d3c98,font-size:13px
```
:::

------------------------------------------------------------------------

## Revenue Accounts - Core Logic

Three steps are applied to **every** Business Unit:

::::: columns
::: {.column width="48%"}
**Step 1 - Build account skeleton**

``` r
# Pull all relevant customers from Master Data
# and attach the correct GL + Cost Centre key
account_rows <- customer_data %>%
  filter(BU == "1.Farming Operations") %>%
  left_join(gl_cc_data, by = "BU") %>%
  crossing(Period = 1:12)  # one row per month
```

**Step 2 - Join SOP volume**

``` r
# Match on SOP Unicode + Abattoir + Month + Tab
account_rows %>%
  left_join(volume_farm_raw,
            by = c("SOP Unicode" = "Unicode",
                   "Abattoir", "Month", "Tab"))
```
:::

::: {.column width="48%"}
**Step 3 - Calculate value**

``` r
# Different formula per tab type
mutate(Value = case_when(
  Tab == "FARM" ~ Total_Weight * Carcass_Price,
  Tab == "KILL" ~ Units * Kill_Fee,
  Tab == "BONE" ~ Units * Bone_Fee
))
```

**Mock result after all three steps:**

```{r}
library(dplyr)
library(knitr)

tibble(
  Tab        = c("FARM", "KILL", "BONE"),
  Units      = c(120L,   120L,   85L),
  `Weight (kg)` = c(18500, 18500, 12000),
  `Price`    = c("$3.25/kg", "$45.50/hd", "$28.00/hd"),
  `Value ($)` = c(60125, 5460, 2380)
) |> kable("simple")
```
:::
:::::

------------------------------------------------------------------------

## Revenue Account Coverage

> **GL 400000** = Sales to external customers  \|  **GL 400028** = Intercompany sales between JBS sites

::::: columns
::: {.column width="50%"}
**Corowa**

-   1\. Farming Operations
-   2\. Meat Processing
    -   Kill Floor, Boning Room, Boxed Meat
    -   Each sub-section has both 400000 & 400028
-   Offal - Edible & Inedible
-   Commodity Bone
-   Meat Trade *(receives Laverton volume under Corowa account)*
:::

::: {.column width="50%"}
**Laverton**

-   6\. Laverton Processing
    -   Kill Floor, Boning Room, Boxed Meat
-   Offal *(Edible shipped to Corowa via Lineage cold store)*
-   Commodity Chilled & Frozen
-   Sow Bone

**Cross-site**

-   3\. Meat Sales (VA / Value-Add)
:::
:::::

------------------------------------------------------------------------

## Expense Accounts - Core Logic

Same skeleton approach as revenue - account rows built from Master Data, then rates joined from external files.

::::: columns
::: {.column width="50%"}
**Rate sources per category**

```{r}
tibble(
  Category      = c("Packaging & Pallet", "Trade Allowance", "Storage", "Freight"),
  `Rate Source` = c("Prices.xlsb - Packaging VA sheet",
                    "Trade Allowance.xlsx",
                    "Rates & Allocation.xlsx",
                    "Rates & Allocation.xlsx")
) |> kable("simple")
```

``` r
# Expense value = total weight × rate
mutate(Value = `Total Weight` * Rate)
```
:::

::: {.column width="46%"}
**Mock result after rate join**

```{r}
tibble(
  Category     = c("Packaging", "Trade Allow.", "Storage", "Freight"),
  `Weight (kg)`= c(18500, 18500, 18500, 18500),
  `Rate ($/kg)` = c(0.12, 0.05, 0.08, 0.15),
  `Value ($)`  = c(2220, 925, 1480, 2775)
) |> kable("simple")
```
:::
:::::

------------------------------------------------------------------------

## Expense Account Coverage

::::: columns
::: {.column width="50%"}
**Packaging & Pallet** *(GL 650301 / 650303 / 650311)*

-   Corowa: Offal, 6 Way, Commodity
-   Laverton: Offal, 6 Way, Commodity, Sow, Export
-   Meat Sales (VA products)
-   Special contracts (Woolworths, DRJ) use separate margin account GL 650311

**Trade Allowance** *(GL 450050)*

-   Meat Sales (VA)
-   Laverton Processing
:::

::: {.column width="50%"}
**Storage** *(GL 730010)*

-   Corowa: Offal, Commodity, 6 Way, Meat Trade, Stock on Hand
-   Laverton: Sow, Stock on Hand
-   Meat Sales

**Freight** *(GL 500192 / 500609)*

-   500192 = Domestic freight
-   500609 = Ocean / Export freight
-   Covers: Offal, 6 Way, Commodity, Meat Trade, Meat Sales
:::
:::::

------------------------------------------------------------------------

## Key Challenges

:::::: columns
::: {.column width="33%"}
**Unstable source data**

-   SOP Volumes contains spelling mistakes and inconsistent naming that silently break joins
-   Master Data missing customer or GL entries means volume rows match no account and are lost
-   Required ongoing fixes during development (e.g. `str_trim`, `toupper`, typo corrections)
:::

::: {.column width="33%"}
**Incomplete price data**

-   `Prices.xlsb` frequently missing item codes - revenue rows for those items produce NA values
-   Packaging rates also missing for newer items - expense rows fail silently
-   Gap Check was built specifically to surface these missing-price rows after each run
:::

::: {.column width="33%"}
**Complex customer contracts**

-   JBS negotiates individual discounts and special pricing per customer
-   Customers like Woolworths and DRJ require separate GL accounts and additional conditional calculation steps
-   Every new contract adds conditional logic, making the pipeline progressively harder to maintain
:::
::::::

------------------------------------------------------------------------

## Quality Assurance - Gap Check

Built from real failure points during development - each check represents a problem that once caused silent data loss. Unlike manual Excel review, R pinpoints the exact item, month and site instantly.

**Sheet 1** reconciles SOP raw weight vs database across 12 categories - a `GAP` status flags exactly which segment lost data. **Sheet 2** lists every row that failed to enter the database:

```{r}
tibble(
  Check = c(
    "Item has no revenue price assigned",
    "Item cannot be matched to a product category",
    "Item missing storage type classification",
    "Volume has no Carcass Price",
    "Volume has no Bone Processing Fee",
    "Volume has no Kill Fee",
    "Item sold at zero or missing price",
    "Internal vs external volume split does not reconcile"
  ),
  `What it catches` = c(
    "New product not yet added to the price reference file",
    "Incorrectly named value in the source data",
    "Missing Chilled / Frozen label in source data",
    "Customer volume with no matching carcass price",
    "Customer volume with no matching bone fee",
    "Customer volume with no matching kill fee",
    "Sale record with blank or zero price",
    "Splitting logic error - totals don't add up"
  )
) |> kable("simple")
```

------------------------------------------------------------------------

## Summary - Excel vs R

```{r}
tibble(
  ` ` = c(
    "Time to build each month",
    "Adding a new Business Unit",
    "Handling a rule change or new contract",
    "Data error tracing",
    "Risk of human error",
    "Complex freight cost allocation",
    "Quality assurance"
  ),
  `Excel (Before)` = c(
    "A lot of time for manual work per period",
    "Copy, paste and reformat an entire sheet",
    "Manually update every affected cell",
    "Manually scan rows - easy to miss",
    "High - copy-paste mistakes go unnoticed",
    "Averaged cost across all export types manually - imprecise and considered incorrect",
    "Manual spot-check only"
  ),
  `R Pipeline (Now)` = c(
    "One-click once - under 10 minutes",
    "Add a filter condition and a join - minutes",
    "Change one line of code, re-run",
    "Gap Check pinpoints exact item, month, site",
    "Low - same logic applied consistently every run",
    "Many-to-many join assigns the correct rate to each specific export type automatically",
    "Automated Gap Check runs after every build"
  )
) |> kable("simple")
```
