---
title: "Finance Calculating"
format: html
editor: visual
---

# Prepare Data

## Library Loading

```{r}
library(readxl)
library(readr)
library(dplyr)
library(openxlsx)
library(tidyr)
library(lubridate)
library(openxlsx2)
library(stringr)
```

## Data Input

```{r, warning=FALSE}
# Read everything as text with no headers
volume_raw <- read_excel(
  "C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/SOP Volumes.xlsx",
  sheet = "Sheet1",
  col_names = FALSE,
  col_types = "text"
)
# The reason for loading data directly from OneDrive is that the data will be update frequency by putting it inside a shared folder
carcass_price_data <- wb_to_df("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Prices.xlsb", sheet = "Carcass Price")
bone_fee_data <- wb_to_df("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Prices.xlsb", sheet = "Bone Fee")
kill_fee_data <- wb_to_df("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Prices.xlsb", sheet = "Kill Fee")
item_price_data <- wb_to_df("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Prices.xlsb", sheet = "BM PRice")
gl_cc_data <- read_excel("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Master Data..xlsx", sheet = "GL & CC")
customer_data <- read_excel("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Master Data..xlsx", sheet = "Customer")
```

## Data Processing

```{r}
# Remove extra spaces in BU naming (e.g. "1. Farming" → "1.Farming")
gl_cc_data <- gl_cc_data %>%
  mutate(BU = str_replace_all(BU, "(\\d+\\.)\\s+", "\\1"))

# Split volume_raw into three data types based on col 2 identifier
volume_farm_raw <- volume_raw %>%
  filter(`...2` %in% c("Farm", "Kill", "Bone")) %>%
  select(1:23)

volume_bone_raw <- volume_raw %>%
  filter(`...2` %in% c("2.Meat Processing", "6.Laverton Processing")) %>%
  select(1:23)

volume_va_raw <- volume_raw %>%
  filter(`...2` == "3.Meat Sales") %>%
  select(1:23)

# Assign names for each separate data
colnames(volume_farm_raw) <- c("Unicode", "Tab", "Week", "Month", "Year", "Abattoir", "Service", "Int/Ext", "Vendor Type", "Customer Code", "Customer name", "Item type", "Item Code", "Item Description", "Run", "Storage", "Type", "Group", "Primal", "Units", "Avg Weight", "Total Weight", "Production check")

colnames(volume_bone_raw) <- c("Unicode", "Tab", "Week", "Month", "Year", "Abattoir", "Service", "Int/Ext", "Vendor Type", "Customer Code", "Customer name", "Item type", "Item Code", "Item Description", "Run", "Storage", "Type", "Group", "Primal", "Units", "Avg Weight", "Total Weight", "Production check")

colnames(volume_va_raw)   <- c("Unicode", "Tab", "Week", "Month", "Year", "Abattoir", "Service", "Int/Ext", "Vendor Type", "Customer Code", "Customer name", "Item type", "Item Code", "Item Description", "Run", "Storage", "Type", "Group", "Primal", "Units", "Avg Weight", "Total Weight", "Production check")

# Remove duplicated Item to prevent potential error in the future
item_price_data <- item_price_data %>%
  select(-`Item Description`) %>%
  mutate(`Item Key` = str_trim(`Item Key`)) %>%
  group_by(`Item Key`) %>%
  slice(1) %>%
  ungroup()
```

# Revenue Data

## Farm Section

#### 1.Farming Operations Sales (400000-10001812)

```{r}
# Sales — external customers
farm_sales_400000_10001812 <- customer_data %>% 
  filter(`BU` == "1.Farming Operations") %>% 
  filter(!`SOP Unicode` %in% c(
    # These are Intercompany customer which was provided by the company so i filter these customer out
    "FLAVERTON6WAY",
    "FCOROWA6Way",
    "FLAVERTONCommodity",
    "FCOROWACommodity",
    "FOtherX",
    "FLAVERTONSow Commodity"
  )) 
farm_sales_400000_10001812_new <- farm_sales_400000_10001812 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10001812),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 1.Farming Operations Intercompany Sales (400028-10001812)

```{r}
# Intercompany Sales — internal transfers 
farm_sales_400028_10001812 <- customer_data %>% 
  filter(`BU` == "1.Farming Operations") %>% 
  filter(`SOP Unicode` %in% c(
    # These are Intercompany customer which was provided by the company so i filter them in
    "FLAVERTON6WAY",
    "FCOROWA6Way",
    "FLAVERTONCommodity",
    "FCOROWACommodity",
    "FOtherX",
    "FLAVERTONSow Commodity"
  )) 
farm_sales_400028_10001812_new <- farm_sales_400028_10001812 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10001812),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Corowa Meat Processing

### Kill Floor

#### 2.Meat Processing Sales Kill Floor (400000-10201816)

```{r}
# Sales — external customers
meat_sales_kill_400000_10201816 <- customer_data %>%
  filter(`BU` == "2.Meat Processing") %>%
  filter(Tab == "Kill") %>%
  filter(!`Customer Group` %in% c("Edible Offal", "Inedible Offal")) %>%  # exclude offal — captured separately
  filter(!`SOP Unicode` %in% c(
    # These are Intercompany customers so filter them out
    "COROWA6Way",
    "COROWACommodity"
  ))
meat_sales_kill_400000_10201816_new <- meat_sales_kill_400000_10201816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10201816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 2.Meat Processing Sales Intercompany Kill Floor (400028-10201816)

```{r}
# Intercompany Sales — internal transfers
meat_sales_kill_400028_10201816 <- customer_data %>%
  filter(`BU` == "2.Meat Processing") %>%
  filter(Tab == "Kill") %>%
  filter(!`Customer Group` %in% c("Edible Offal", "Inedible Offal")) %>%  # exclude offal — captured separately
  filter(`SOP Unicode` %in% c(
    # These are Intercompany customers so filter them in
    "COROWA6Way",
    "COROWACommodity"
  ))
meat_sales_kill_400028_10201816_new <- meat_sales_kill_400028_10201816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10201816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Boning Room

#### 2.Meat Processing Sales Boning Room (400000-11901816)

```{r}
# Sales — external customers
meat_sales_boning_400000_11901816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab == "Bone") %>% 
  filter(`Floor` == "Bone") %>% 
  filter(!`SOP Unicode` %in% c(
    # These are Intercompany customers so filter them out
    "COROWA6Way",
    "COROWACommodity"
  )) 
meat_sales_boning_400000_11901816_new <- meat_sales_boning_400000_11901816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 11901816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 2.Meat Processing Sales Intercompany Boning Room (400028-11901816)

```{r}
# Intercompany Sales — internal transfers
meat_sales_boning_400028_11901816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab == "Bone") %>% 
  filter(`Floor` == "Bone") %>% 
  filter(`SOP Unicode` %in% c(
    # These are Intercompany customers so filter them in
    "COROWA6Way",
    "COROWACommodity"
  )) 
meat_sales_boning_400028_11901816_new <- meat_sales_boning_400028_11901816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 11901816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Meat Boxed

#### 2.Meat Processing Sale Boxed Meat (400000-10501816)

```{r}
# Sales — external customers
meat_sales_boxed_meat_400000_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab %in% c("Boxed Meat", "Meat Trade")) %>%
  filter(`Floor` %in% c("Boxed Meat", "Meat Trade")) %>% 
  filter(!`SOP Unicode` %in% c(
    # This is an Intercompany customer so filter it out
    "CommodityChilInternalVA"
  )) 
meat_sales_boxed_meat_400000_10501816_new <- meat_sales_boxed_meat_400000_10501816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 2.Meat Processing Sale Intercompany Boxed Meat (400028-10501816)

```{r}
# Intercompany Sales — internal transfers
meat_sales_boxed_meat_400028_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab %in% c("Boxed Meat", "Meat Trade")) %>%
  filter(`Floor` %in% c("Boxed Meat", "Meat Trade")) %>% 
  filter(`SOP Unicode` %in% c(
    # This is an Intercompany customer so filter it in
    "CommodityChilInternalVA"
  )) 
meat_sales_boxed_meat_400028_10501816_new <- meat_sales_boxed_meat_400028_10501816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Meat Sales

#### 3.Meat Sales (400000-10001814)

```{r}
# Sales — external customers, no intercompany filtering needed for this BU
meat_sales_400000_10001814 <- customer_data %>% 
  filter(`BU` == "3.Meat Sales") %>% 
  filter(Tab == "VA") 
meat_sales_400000_10001814_new <- meat_sales_400000_10001814 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10001814),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Laverton Processing

### Kill Floor

#### 6. Laverton Processing Sales Kill Floor (400000-10201854)

```{r}
# Sales — external customers
laverton_sales_kill_400000_10201854 <- customer_data %>%
  filter(`BU` == "6.Laverton Processing") %>%
  filter(Tab == "Kill") %>%
  filter(`Floor` == "Kill") %>%
  filter(!`Customer Group` %in% c("Edible Offal", "Inedible Offal")) %>%  # exclude offal — captured separately
  filter(!`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them out
  "Laverton6Way",
  "LavertonCommodity",
  "LAVERTONEdibleOffal",
  "LAVERTONLaverton - Purchase",
  "LAVERTONPW Opportunity - Sow",
  "LavertonSow",
  "LAVERTONSow Commodity"
  ))
laverton_sales_kill_400000_10201854_new <- laverton_sales_kill_400000_10201854 %>% 
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10201854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 6. Laverton Processing Sales Intercompany Kill Floor (400028-10201854)

```{r}
# Intercompany Sales — internal transfers
laverton_sales_kill_400028_10201854 <- customer_data %>%
  filter(`BU` == "6.Laverton Processing") %>%
  filter(Tab == "Kill") %>%
  filter(`Floor` == "Kill") %>%
  filter(!`Customer Group` %in% c("Edible Offal", "Inedible Offal")) %>%  # exclude offal — captured separately
  filter(`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them in
  "Laverton6Way",
  "LavertonCommodity",
  "LAVERTONEdibleOffal",
  "LAVERTONLaverton - Purchase",
  "LAVERTONPW Opportunity - Sow",
  "LavertonSow",
  "LAVERTONSow Commodity"
  ))
laverton_sales_kill_400028_10201854_new <- laverton_sales_kill_400028_10201854 %>% 
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10201854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Boning Room

#### 6. Laverton Processing Sales Boning Room (400000-11901854)

```{r}
# Sales — external customers
laverton_sales_boning_400000_11901854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Bone") %>%
  filter(`Floor` == "Bone") %>% 
  filter(!`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them out
  "Laverton6Way",
  "LavertonCommodity",
  "LAVERTONLaverton - Purchase",
  "LAVERTONPW Opportunity - Sow",
  "LAVERTONSow Commodity"
  )) 
laverton_sales_boning_400000_11901854_new <- laverton_sales_boning_400000_11901854 %>% 
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 11901854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 6. Laverton Processing Sales Intercompany Boning Room (400028-11901854)

```{r}
# Intercompany Sales — internal transfers
laverton_sales_boning_400028_11901854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Bone") %>% 
  filter(`Floor` == "Bone") %>% 
  filter(`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them in
  "Laverton6Way",
  "LavertonCommodity",
  "LAVERTONLaverton - Purchase",
  "LAVERTONPW Opportunity - Sow",
  "LAVERTONSow Commodity"
  )) 
laverton_sales_boning_400028_11901854_new <- laverton_sales_boning_400028_11901854 %>% 
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 11901854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Boxed Meat

#### 6. Laverton Processing Sales Boxed Meat (400000-10501854)

```{r}
# Sales — external customers
laverton_sales_boxed_meat_400000_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Bone") %>%
  filter(`Floor` == "Boxed Meat") %>% 
  filter(!`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them out
  "LavertonSow",
  "LavertonCommodity",
  "Laverton6Way"
  )) 
laverton_sales_boxed_meat_400000_10501854_new <- laverton_sales_boxed_meat_400000_10501854 %>% 
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 6. Laverton Processing Sales Intercompany Boxed Meat (400028-10501854)

```{r}
# Intercompany Sales — internal transfers
laverton_sales_boxed_meat_400028_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Bone") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them in
  "LavertonSow",
  "LavertonCommodity",
  "Laverton6Way"
  )) 
laverton_sales_boxed_meat_400028_10501854_new <- laverton_sales_boxed_meat_400028_10501854 %>% 
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

# Offal (Edible and Inedible Data)

## Corowa Offal Data

### Edible Offal Sales (400000-10001816)

```{r}
# Sales — external customers
edible_offal_sales_400000_10001816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab == "Kill") %>% 
  filter(`Floor` == "Kill") %>% 
  filter(`Customer Group` == "Edible Offal")

edible_offal_sales_400000_10001816_new <- edible_offal_sales_400000_10001816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10001816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Inedible Offal Sales (400000-10801816)

```{r}
# Sales — external customers
inedible_offal_sales_400000_10801816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab == "Kill") %>% 
  filter(`Floor` == "Kill") %>% 
  filter(`Customer Group` == "Inedible Offal")

inedible_offal_sales_400000_10801816_new <- inedible_offal_sales_400000_10801816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10801816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Laverton Offal Data

### Intercompany Edible Offal Sales (400028-10001854)

```{r}
# Sales — intercompany, this happen because Laverton consolidate its Edible Offal with Corowa under Corowa name to sell to the customer
edible_offal_sales_400028_10001854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Kill") %>% 
  filter(`Floor` == "Kill") %>% 
  filter(`Customer Group` == "Edible Offal")

edible_offal_sales_400028_10001854_new <- edible_offal_sales_400028_10001854 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10001854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Inedible Offal Sales (400000-10801854)

```{r}
# Sales — external customers
inedible_offal_sales_400000_10801854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Kill") %>% 
  filter(`Floor` == "Kill") %>% 
  filter(`Customer Group` == "Inedible Offal")

inedible_offal_sales_400000_10801854_new <- inedible_offal_sales_400000_10801854 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10801854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

# Commodity Data (Boxed Meat Floor)

## Commodity Data Corowa

### Corowa 6Way Data Frozen (400000-10501816)

```{r}
# Sales — external customers for corowa 6way frozen products
corowa_6way_frz_400000_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "6 Way") %>% 
  filter(`Sales Type` == "FRZ")

corowa_6way_frz_400000_10501816_new <- corowa_6way_frz_400000_10501816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Corowa Commodity Data Frozen (400000-10501816)

```{r}
# Sales — external customers for corowa 6way frozen products
corowa_commodity_frz_400000_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Commodity") %>% 
  filter(`Sales Type` == "FRZ")

corowa_commodity_frz_400000_10501816_new <- corowa_commodity_frz_400000_10501816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Corowa Commodity Data Frozen (400028-10501816) (equivalent to VA sales)

```{r}
# Sales — Intercompany as those products are transfering to VA 
corowa_commodity_frz_400028_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Commodity") %>% 
  filter(`Sales Type` == "FRZ")

corowa_commodity_frz_400028_10501816_new <- corowa_commodity_frz_400028_10501816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Commodity Data Laverton

### Laverton 6Way Data Frozen (400028-10501854)

```{r}
# Sales — Intercompany as those products are transfering to corowa 
laverton_6way_frz_400028_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "6 Way") %>% 
  filter(`Sales Type` == "FRZ")

laverton_6way_frz_400028_10501854_new <- laverton_6way_frz_400028_10501854 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Laverton Sow Data Frozen (400000-10501854)

```{r}
# Sales — external customers for corowa 6way frozen products - Only Laverton has Sow account
laverton_6way_frz_400000_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Sow") %>% 
  filter(`Sales Type` == "FRZ")

laverton_6way_frz_400000_10501854_new <- laverton_6way_frz_400000_10501854 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Laverton Commodity Data Frozen (400028-10501854)

```{r}
# Sales — Intercompany since the product will be frozen before moving to Corowa
laverton_commodity_frz_400028_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Commodity") %>% 
  filter(`Sales Type` == "FRZ")

laverton_commodity_frz_400028_10501854_new <- laverton_commodity_frz_400028_10501854 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Laverton Commodity Data Chilled (400000-10501854)

```{r}
# Sales — external customers for laverton commodity chilled products
laverton_commodity_chil_400000_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Commodity") %>% 
  filter(`Sales Type` == "Chil")

laverton_commodity_chil_400000_10501854_new <- laverton_commodity_chil_400000_10501854 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

# Final Stage: Join data, apply calculation and apply special condition for each specific data

## Farm Data

### Join all prepared data together to create the main data

```{r}
all_revenue_farm <- bind_rows(
  farm_sales_400000_10001812_new,
  farm_sales_400028_10001812_new,
  meat_sales_kill_400000_10201816_new,
  meat_sales_kill_400028_10201816_new,
  meat_sales_boning_400000_11901816_new,
  meat_sales_boning_400028_11901816_new,
  meat_sales_boxed_meat_400000_10501816_new,
  meat_sales_boxed_meat_400028_10501816_new,
  meat_sales_400000_10001814_new,
  laverton_sales_kill_400000_10201854_new,
  laverton_sales_kill_400028_10201854_new,
  laverton_sales_boning_400000_11901854_new,
  laverton_sales_boning_400028_11901854_new,
  laverton_sales_boxed_meat_400000_10501854_new,
  laverton_sales_boxed_meat_400028_10501854_new
  )
```

### Some changes to the main data based on guidance

```{r}
# Here are some special conditions, filtering that i applied due to guidance from my manager, some are only tempotarily, some are because of the way data was recorded (unwanted data get in the way so those data need to be filter out)
all_revenue_farm <- all_revenue_farm %>%
  mutate(Abattoir = if_else(is.na(Abattoir) | Abattoir == "", "EXTERNAL", Abattoir)) %>%  # fill blank Abattoir and also when its External because external mean the process did not happen within the company so there is no need to include this result
  mutate(`Customer name` = if_else(
    BU == "2.Meat Processing" & Tab %in% c("Boxed Meat", "Meat Trade") & `SOP Unicode` == "CommodityChilInternalVA",
    "Commodity to VA",
    `Customer name`
    # Change name for some customer based on guidance
  )) %>%
  mutate(Month = month.name[Period]) %>%
  mutate(`Customer Group` = if_else(`Customer Group` == "Wangarrata", "Wangaratta", `Customer Group`)) %>%  # fix typo
filter(!(toupper(Abattoir) == "LAVERTON" & Tab == "Kill" & str_detect(toupper(`Customer name`), "6WAY|COMMODITY"))) # Temporarily special condition
```

### Join Volume and Weight to the Main Data

```{r}
# Pre-standardise keys once
all_revenue_farm_std <- all_revenue_farm %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(Month),
    Tab           = toupper(Tab)
  )

# Join volume_farm_raw on SOP Unicode + Abattoir + Month + Tab
all_revenue_farm_new <- all_revenue_farm_std %>%
  left_join(
    volume_farm_raw %>%
      filter(!(`Int/Ext` %in% "External" & Tab == "Farm")) %>%
      filter(!(Service == "live" & Tab %in% c("Kill", "Bone"))) %>%
      mutate(
        Unicode        = toupper(Unicode),
        Abattoir       = toupper(Abattoir),
        Month          = toupper(Month),
        Tab            = toupper(Tab),
        Units          = as.numeric(Units),
        `Avg Weight`   = as.numeric(`Avg Weight`),
        `Total Weight` = as.numeric(`Total Weight`)
      ) %>%
      group_by(Unicode, Abattoir, Month, Tab) %>%
      summarise(
        `Item Code`    = first(`Item Code`),
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("SOP Unicode" = "Unicode", "Abattoir", "Month", "Tab")
  )
```

### Join Price to the Main Data

```{r}
# Split by Tab to apply the correct price source for each type
all_revenue_farm_final <- bind_rows(
  # Join Farm Tab to Carcass Price, add condition: FCOROWAWoolworths inherits price from FEXTERNALBig River Pork - Coles
  all_revenue_farm_new %>%
    mutate(`SOP Unicode` = str_trim(`SOP Unicode`)) %>%
    filter(Tab == "FARM") %>%
    left_join(
      carcass_price_data %>%
        mutate(`Farm Unicode` = toupper(str_trim(`Farm Unicode`)), Abattoir = toupper(Abbatoir)) %>%
        pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Carcass Price") %>%
        mutate(Period = as.integer(Period)) %>%
        select(`Farm Unicode`, Abattoir, Period, `Carcass Price`) %>%
        bind_rows(
          filter(., `Farm Unicode` == toupper(str_trim("FEXTERNALBig River Pork - Coles"))) %>%
            mutate(`Farm Unicode` = toupper(str_trim("FCOROWAWoolworths")))
        ),
      by = c("SOP Unicode" = "Farm Unicode", "Abattoir", "Period")
    ),
  # Join Bone Tab to Fee Data
  all_revenue_farm_new %>%
    mutate(`SOP Unicode` = str_trim(`SOP Unicode`)) %>%
    filter(Tab == "BONE") %>%
    left_join(
      bone_fee_data %>%
        mutate(`SOP Unicode` = toupper(str_trim(`SOP Unicode`)), Abattoir = toupper(Abbatoir)) %>%
        pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Fee") %>%
        mutate(Period = as.integer(Period)) %>%
        select(`SOP Unicode`, Abattoir, Period, Fee),
      by = c("SOP Unicode", "Abattoir", "Period")
    ),
  # join Kill tab to Fee Data 
  all_revenue_farm_new %>%
    mutate(`SOP Unicode` = str_trim(`SOP Unicode`)) %>%
    filter(Tab == "KILL") %>%
    left_join(
      kill_fee_data %>%
        mutate(`SOP Unicode` = toupper(str_trim(`SOP Unicode`)), Abattoir = toupper(Abbatoir)) %>%
        pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Fee") %>%
        mutate(Period = as.integer(Period)) %>%
        select(`SOP Unicode`, Abattoir, Period, Fee),
      by = c("SOP Unicode", "Abattoir", "Period")
    ),
  # All other Tab types — no price applied
  all_revenue_farm_new %>%
    filter(is.na(Tab) | !Tab %in% c("FARM", "BONE", "KILL"))
)
```

### Calculation for Value by Weight x Carcass Price

```{r}
# Farm: Total Weight x Carcass Price | Bone/Kill: Units x Fee
all_revenue_farm_calculated <- all_revenue_farm_final %>%
  mutate(Value = case_when(
    Tab == "FARM" ~ `Total Weight` * `Carcass Price`,
    Tab %in% c("BONE", "KILL") ~ Units * Fee,
    TRUE ~ NA_real_))
```

## Join Price Data to Volume Data for Bone Data in order to calculate the value for each item

```{r}
# Join volume_bone_raw with item_price_data on Item Code, calculate Value per item, then aggregate by BU/Abattoir/Month
volume_bone_price_calculated <- volume_bone_raw %>%
  mutate(
    Tab         = toupper(Tab),
    Abattoir    = toupper(Abattoir),
    Month       = toupper(Month),
    Units       = as.numeric(Units),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code` = str_trim(`Item Code`)
  ) %>%
  left_join(
    item_price_data,
    by = c("Item Code" = "Item Key")
  ) %>%
  mutate(Value = `Total Weight` * `Current Price`)
```

## Offal Data from Bone Data

### Join all data to create main data

```{r}
all_revenue_offal_data <- bind_rows(
  edible_offal_sales_400000_10001816_new,
  inedible_offal_sales_400000_10801816_new,
  edible_offal_sales_400028_10001854_new,
  inedible_offal_sales_400000_10801854_new
  )
# Pre-standardise keys once
all_revenue_offal_data_std <- all_revenue_offal_data %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  )
```

### Filter calculated bone data for offal data

```{r}
# Group value for Corowa and filter out unrelevant data for Offal Data
volume_offal_corowa <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(Type %in% c("INEDIBLE", "OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = case_when(
      Type == "INEDIBLE"    ~ "Inedible Offal",
      Type == "OFFALS"      ~ "Edible Offal",
      Type == "BACON CUTS"  ~ "Edible Offal",
      TRUE ~ NA_character_
    )
  ) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  )

# Group value for Corowa and filter out unrelevant data for Offal Data and apply special discount for Laverton since this site ship the offal to Lineage whom charge a special discount which is also the reason why Corowa and Laverton was splitted
volume_offal_laverton <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(Type %in% c("INEDIBLE", "OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = case_when(
      Type == "INEDIBLE"    ~ "Inedible Offal",
      Type == "OFFALS"      ~ "Edible Offal",
      Type == "BACON CUTS"  ~ "Edible Offal",
      TRUE ~ NA_character_
    )
  ) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Value = if_else(`Customer Group` == "Edible Offal", Value - 0.51 * `Total Weight`, Value))

# Combine Laverton and Corowa 
volume_offal_combined <- bind_rows(volume_offal_corowa, volume_offal_laverton)

# Join item-level volume + value into the bone revenue data on BU + Abattoir + Month
all_revenue_offal_data_calculated <- all_revenue_offal_data_std %>%
  left_join(
    volume_offal_combined,
    by = c("BU" = "Tab", "Abattoir", "Month", "Customer Group")
  )
```

## 6Way and Sow Data from Bone Data

### Join all data to create main data

```{r}
all_revenue_6way_sow_data <- bind_rows(
  corowa_6way_frz_400000_10501816_new,
  laverton_6way_frz_400028_10501854_new,
  laverton_6way_frz_400000_10501854_new
  )

# Pre-standardise keys once
all_revenue_6way_sow_data_std <- all_revenue_6way_sow_data %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  )
```

### Filter calculated bone data for 6 way and sow data

```{r}
# Group value for Corowa and filter out unrelevant data for commodity Data 
volume_6way_sow_corowa <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(toupper(Run) == "6 WAY") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = "6 Way"
    ) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  )

# Group value for Laverton and filter out unrelevant data for commodity Data 
volume_6way_sow_laverton <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(toupper(Run) %in% c("6 WAY", "SOW BONE")) %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group` = case_when(
    toupper(Run) == "6 WAY" ~ "6 Way",
    toupper(Run) == "SOW B"   ~ "Sow",
    TRUE ~ NA_character_
    )) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Value = if_else(`Customer Group` == "6 Way", Value - 0.51 * `Total Weight`, Value))

# Combine Corowa and Laverton
volume_6way_sow_combined <- bind_rows(volume_6way_sow_corowa, volume_6way_sow_laverton)

# Join item-level volume + value into the bone revenue data on BU + Abattoir + Month
all_revenue_6way_sow_data_calculated <- all_revenue_6way_sow_data_std %>%
  left_join(
    volume_6way_sow_combined,
    by = c("BU" = "Tab", "Abattoir", "Month", "Customer Group")
  )
```

## Commodity Data from Bone Data (special)

### Join all data to create main data

```{r}
all_revenue_commodity_data <- bind_rows(
  corowa_commodity_frz_400000_10501816_new,
  corowa_commodity_frz_400028_10501816_new,
  laverton_commodity_frz_400028_10501854_new,
  laverton_commodity_chil_400000_10501854_new
  )

# Pre-standardise keys once
all_revenue_commodity_data_std <- all_revenue_commodity_data %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  )
```

### Separate value of 400000 and 400028 for Corowa from 3.Meat Sales

```{r}
# Get internal VA sales which is equivalent to 400028 volume from 3.Meat Sales as the volume source for Corowa commodity bone
volume_commodity_corowa_400028 <- volume_va_raw %>%
  filter(`Vendor Type` == "Internal") %>%
  filter(`Service` == "Procurement") %>%
  mutate(
    `Item Code`    = str_trim(`Item Code`),
    Month          = toupper(Month),
    Abattoir       = toupper(Abattoir),
    `Total Weight` = as.numeric(`Total Weight`),
    `Customer Group` = "Commodity"
  )

# Filter for Corowa commodity bone and assign Customer Group - covers both 400000 and 400028
volume_commodity_corowa <- volume_bone_raw %>%
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(toupper(Run) == "COMMODITY BONE") %>%
  mutate(
    Unicode          = toupper(Unicode),
    Abattoir         = toupper(Abattoir),
    Month            = toupper(Month),
    Tab              = toupper(Tab),
    Units            = NA_real_,
    `Avg Weight`     = NA_real_,
    `Total Weight`   = as.numeric(`Total Weight`),
    `Customer Group` = "Commodity"
  ) 

# 400000 = total (volume_commodity_corowa) minus 400028 (internal), matched by Item Code + Week
volume_commodity_corowa_400000 <- volume_commodity_corowa %>%
  left_join(
    volume_commodity_corowa_400028 %>%
      rename(Weight_400028 = `Total Weight`),
    by = c("Item Code", "Week")
  ) %>%
  mutate(`Total Weight` = `Total Weight` - coalesce(Weight_400028, 0)) %>%
  select(-Weight_400028)
```

### Calculate Value for 400000 and 400028 of Corowa from 3.Meat Sales

```{r}
volume_commodity_corowa_400028_calculated <- volume_commodity_corowa_400028 %>%
  mutate(
    Tab         = toupper(Tab),
    Abattoir    = toupper(Abattoir),
    Month       = toupper(Month),
    Units       = as.numeric(Units),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code` = str_trim(`Item Code`)
  ) %>%
  left_join(
    item_price_data,
    by = c("Item Code" = "Item Key")
  ) %>%
  mutate(Value = `Total Weight` * `Current Price`)
  

volume_commodity_corowa_400000_calculated <- volume_commodity_corowa_400000 %>%
  mutate(
    Tab         = toupper(Tab),
    Abattoir    = toupper(Abattoir),
    Month       = toupper(Month),
    Units       = as.numeric(Units),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code` = str_trim(`Item Code`)
  ) %>%
  left_join(
    item_price_data,
    by = c("Item Code" = "Item Key")
  ) %>%
  mutate(Value = `Total Weight` * `Current Price`)
```

### Filter calculated bone data for commodity data

```{r}
# Group value for Corowa and filter out unrelevant data for commodity Data 
volume_6way_sow_corowa <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(toupper(Run) == "6 WAY") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = "6 Way"
    ) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  )
```

## Rejoin all calculated data together before writing it down

```{r}
final_file <- bind_rows(all_revenue_offal_data_calculated, all_revenue_farm_calculated, all_revenue_6way_sow_data_calculated, all_revenue_commodity_corowa_calculated)
```

# Write down the file

```{r}
write.csv(final_file, "GL_DB Template.csv", row.names = FALSE)
```

# Extra Debugging Code

### Check whether Unit x Avg Weight = Total Weight for every Unicode (result should only return TRUE and NA for check column)

```{r}
check_1 <- all_revenue_farm_new %>%
  mutate(check = round(Units * `Avg Weight`, 2) == round(`Total Weight`, 2)) 
check_1
```

### Check whether the same item has different Item Code (must return 0)

```{r}
check_2 <- volume_farm_raw %>%
  mutate(
    Unicode = toupper(Unicode),
    Abattoir = toupper(Abattoir),
    Month = toupper(Month),
    Tab = toupper(Tab)
  ) %>%
  group_by(Unicode, Abattoir, Month, Tab) %>%
  summarise(n_item_codes = n_distinct(`Item Code`), .groups = "drop") %>%
  filter(n_item_codes > 1)
check_2
```

### Checking Unmatched Customers (the result should ideally return 0)

```{r}
all_captured <- bind_rows(
  farm_sales_400000_10001812,
  farm_sales_400028_10001812,
  meat_sales_kill_400000_10201816,
  meat_sales_kill_400028_10201816,
  meat_sales_boning_400000_11901816,
  meat_sales_boning_400028_11901816,
  meat_sales_boxed_meat_400000_10501816,
  meat_sales_boxed_meat_400028_10501816,
  meat_sales_400000_10001814,
  laverton_sales_kill_400000_10201854,
  laverton_sales_kill_400028_10201854,
  laverton_sales_boning_400000_11901854,
  laverton_sales_boning_400028_11901854,
  laverton_sales_boxed_meat_400000_10501854,
  laverton_sales_boxed_meat_400028_10501854,
  edible_offal_sales_400000_10001816_new,
  inedible_offal_sales_400000_10801816_new,
  edible_offal_sales_400028_10001854_new,
  inedible_offal_sales_400000_10801854_new
)
check_3 <- customer_data %>%
  anti_join(all_captured, by = names(customer_data))
check_3
```

### Code to print out offal data before it was grouped

```{r}
Corowa_edible_check <- volume_bone_price_calculated %>%
  filter(Abattoir == "COROWA") %>%
  mutate(Type = toupper(Type)) %>%
  filter(Type %in% c("INEDIBLE", "OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL")
Laverton_edible_check <- volume_bone_price_calculated %>%
  filter(Abattoir == "LAVERTON") %>%
  mutate(Type = toupper(Type)) %>%
  filter(Type %in% c("INEDIBLE", "OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL")
write.csv(Corowa_edible_check, "Corowa_edible_check.csv", row.names = FALSE)
write.csv(Laverton_edible_check, "Laverton_edible_check.csv", row.names = FALSE)
```

### Check volume_commodity_corowa = 400000 + 400028 (The differences must be 0)

```{r}
total_combined <- sum(volume_commodity_corowa$`Total Weight`, na.rm = TRUE)
total_400000   <- sum(volume_commodity_corowa_400000$`Total Weight`, na.rm = TRUE)
total_400028   <- sum(volume_commodity_corowa_400028$`Total Weight`, na.rm = TRUE)
check_4 <- data.frame(
  total_combined  = total_combined,
  sum_400000_400028 = total_400000 + total_400028,
  difference      = total_combined - (total_400000 + total_400028)
)
```

### Check for negative Total Weight in volume_commodity_corowa_400000 (It must give 0 observations)

```{r}
check_5 <- volume_commodity_corowa_400000 %>%
  filter(`Total Weight` < 0)
```

Check for item in VA procuments but not in 3.Meat Sales

```{r}
anti_join(
  volume_commodity_corowa_400028 %>% distinct(`Item Code`),
  volume_commodity_corowa        %>% distinct(`Item Code`),
  by = "Item Code"
)
```
