---
title: "Finance Calculating"
format: html
editor: visual
---

# Prepare Data

## Library Loading

```{r}
library(readxl)
library(readr)
library(dplyr)
library(openxlsx)
library(tidyr)
library(lubridate)
library(openxlsx2)
library(stringr)
```

## Data Input

```{r, warning=FALSE}
# Read everything as text with no headers
volume_raw <- read_excel(
  "C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/SOP Volumes.xlsx",
  sheet = "Sheet1",
  col_names = FALSE,
  col_types = "text"
)
carcass_price_data <- wb_to_df("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Prices.xlsb", sheet = "Carcass Price")
bone_fee_data <- wb_to_df("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Prices.xlsb", sheet = "Bone Fee")
kill_fee_data <- wb_to_df("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Prices.xlsb", sheet = "Kill Fee")
gl_cc_data <- read_excel("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Master Data..xlsx", sheet = "GL & CC")
customer_data <- read_excel("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Master Data..xlsx", sheet = "Customer")
```

## Data Processing

```{r}
# Remove extra spaces in BU naming (e.g. "1. Farming" → "1.Farming")
gl_cc_data <- gl_cc_data %>%
  mutate(BU = str_replace_all(BU, "(\\d+\\.)\\s+", "\\1"))

# Split volume_raw into three data types based on col 2 identifier
volume_farm_raw <- volume_raw %>%
  filter(`...2` %in% c("Farm", "Kill", "Bone")) %>%
  select(where(~ !all(is.na(.))))

volume_bone_raw <- volume_raw %>%
  filter(`...2` %in% c("2.Meat Processing", "6.Laverton Processing")) %>%
  select(where(~ !all(is.na(.))))

volume_va_raw <- volume_raw %>%
  filter(`...2` == "3.Meat Sales") %>%
  select(where(~ !all(is.na(.))))

colnames(volume_farm_raw) <- c("Unicode", "Tab", "Week", "Month", "Year", "Abattoir", "Service", "Int/Ext", "Vendor Type", "Customer Code", "Customer name", "Item type", "Item Code", "Item Description", "Run", "Storage", "Type", "Group", "Primal", "Units", "Avg Weight", "Total Weight")

# Placeholder names since bone and VA not yet used
colnames(volume_bone_raw) <- paste0("col", seq_along(volume_bone_raw))
colnames(volume_va_raw)   <- paste0("col", seq_along(volume_va_raw))

```

# Revenue Data

## Farm Section

#### 1.Farming Operations Sales (400000-10001812)

```{r}
# Sales — external customers
farm_sales_400000_10001812 <- customer_data %>% 
  filter(`BU` == "1.Farming Operations") %>% 
  filter(!`SOP Unicode` %in% c(
    # These are Intercompany customer which was provided by the company so i filter these customer out
    "FLAVERTON6WAY",
    "FCOROWA6Way",
    "FLAVERTONCommodity",
    "FCOROWACommodity",
    "FOtherX",
    "FLAVERTONSow Commodity"
  )) 
farm_sales_400000_10001812_new <- farm_sales_400000_10001812 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 1.Farming Operations Intercompany Sales (400028-10001812)

```{r}
# Intercompany Sales — internal transfers 
farm_sales_400028_10001812 <- customer_data %>% 
  filter(`BU` == "1.Farming Operations") %>% 
  filter(`SOP Unicode` %in% c(
    # These are Intercompany customer which was provided by the company so i filter them in
    "FLAVERTON6WAY",
    "FCOROWA6Way",
    "FLAVERTONCommodity",
    "FCOROWACommodity",
    "FOtherX",
    "FLAVERTONSow Commodity"
  )) 
farm_sales_400028_10001812_new <- farm_sales_400028_10001812 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Corowa Meat Processing

### Kill Floor

#### 2.Meat Processing Sales Kill Floor (400000-10201816)

```{r}
# Sales — external customers
meat_sales_kill_400000_10201816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab == "Kill") %>% 
  filter(!`SOP Unicode` %in% c(
    # These are Intercompany customers so filter them out
    "COROWA6Way",
    "COROWACommodity"
  )) 
meat_sales_kill_400000_10201816_new <- meat_sales_kill_400000_10201816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10201816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 2.Meat Processing Sales Intercompany Kill Floor (400028-10201816)

```{r}
# Intercompany Sales — internal transfers
meat_sales_kill_400028_10201816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab == "Kill") %>% 
  filter(`SOP Unicode` %in% c(
    # These are Intercompany customers so filter them in
    "COROWA6Way",
    "COROWACommodity"
  )) 
meat_sales_kill_400028_10201816_new <- meat_sales_kill_400028_10201816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10201816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Boning Room

#### 2.Meat Processing Sales Boning Room (400000-11901816)

```{r}
# Sales — external customers
meat_sales_boning_400000_11901816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab == "Bone") %>% 
  filter(`Floor` == "Bone") %>% 
  filter(!`SOP Unicode` %in% c(
    # These are Intercompany customers so filter them out
    "COROWA6Way",
    "COROWACommodity"
  )) 
meat_sales_boning_400000_11901816_new <- meat_sales_boning_400000_11901816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 11901816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 2.Meat Processing Sales Intercompany Boning Room (400028-11901816)

```{r}
# Intercompany Sales — internal transfers
meat_sales_boning_400028_11901816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab == "Bone") %>% 
  filter(`Floor` == "Bone") %>% 
  filter(`SOP Unicode` %in% c(
    # These are Intercompany customers so filter them in
    "COROWA6Way",
    "COROWACommodity"
  )) 
meat_sales_boning_400028_11901816_new <- meat_sales_boning_400028_11901816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 11901816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Meat Boxed

#### 2.Meat Processing Sale Boxed Meat (400000-10501816)

```{r}
# Sales — external customers
meat_sales_boxed_meat_400000_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab %in% c("Boxed Meat", "Meat Trade")) %>%
  filter(`Floor` %in% c("Boxed Meat", "Meat Trade")) %>% 
  filter(!`SOP Unicode` %in% c(
    # This is an Intercompany customer so filter it out
    "CommodityChilInternalVA"
  )) 
meat_sales_boxed_meat_400000_10501816_new <- meat_sales_boxed_meat_400000_10501816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 2.Meat Processing Sale Intercompany Boxed Meat (400028-10501816)

```{r}
# Intercompany Sales — internal transfers
meat_sales_boxed_meat_400028_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab %in% c("Boxed Meat", "Meat Trade")) %>%
  filter(`Floor` %in% c("Boxed Meat", "Meat Trade")) %>% 
  filter(`SOP Unicode` %in% c(
    # This is an Intercompany customer so filter it in
    "CommodityChilInternalVA"
  )) 
meat_sales_boxed_meat_400028_10501816_new <- meat_sales_boxed_meat_400028_10501816 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Meat Sales

#### 3.Meat Sales (400000-10001814)

```{r}
# Sales — external customers, no intercompany filtering needed for this BU
meat_sales_400000_10001814 <- customer_data %>% 
  filter(`BU` == "3.Meat Sales") %>% 
  filter(Tab == "VA") 
meat_sales_400000_10001814_new <- meat_sales_400000_10001814 %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10001814),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Laverton Processing

### Kill Floor

#### 6. Laverton Processing Sales Kill Floor (400000-10201854)

```{r}
# Sales — external customers
laverton_sales_kill_400000_10201854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Kill") %>% 
  filter(`Floor` == "Kill") %>% 
  filter(!`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them out
  "Laverton6Way",
  "LavertonCommodity",
  "LAVERTONEdibleOffal",
  "LAVERTONLaverton - Purchase",
  "LAVERTONPW Opportunity - Sow",
  "LavertonSow",
  "LAVERTONSow Commodity"
  )) 
laverton_sales_kill_400000_10201854_new <- laverton_sales_kill_400000_10201854 %>% 
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10201854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 6. Laverton Processing Sales Intercompany Kill Floor (400028-10201854)

```{r}
# Intercompany Sales — internal transfers
laverton_sales_kill_400028_10201854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Kill") %>% 
  filter(`Floor` == "Kill") %>% 
  filter(`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them in
  "Laverton6Way",
  "LavertonCommodity",
  "LAVERTONEdibleOffal",
  "LAVERTONLaverton - Purchase",
  "LAVERTONPW Opportunity - Sow",
  "LavertonSow",
  "LAVERTONSow Commodity"
  )) 
laverton_sales_kill_400028_10201854_new <- laverton_sales_kill_400028_10201854 %>% 
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10201854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Boning Room

#### 6. Laverton Processing Sales Boning Room (400000-11901854)

```{r}
# Sales — external customers
laverton_sales_boning_400000_11901854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Bone") %>%
  filter(`Floor` == "Bone") %>% 
  filter(!`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them out
  "Laverton6Way",
  "LavertonCommodity",
  "LAVERTONLaverton - Purchase",
  "LAVERTONPW Opportunity - Sow",
  "LAVERTONSow Commodity"
  )) 
laverton_sales_boning_400000_11901854_new <- laverton_sales_boning_400000_11901854 %>% 
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 11901854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 6. Laverton Processing Sales Intercompany Boning Room (400028-11901854)

```{r}
# Intercompany Sales — internal transfers
laverton_sales_boning_400028_11901854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Bone") %>% 
  filter(`Floor` == "Bone") %>% 
  filter(`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them in
  "Laverton6Way",
  "LavertonCommodity",
  "LAVERTONLaverton - Purchase",
  "LAVERTONPW Opportunity - Sow",
  "LAVERTONSow Commodity"
  )) 
laverton_sales_boning_400028_11901854_new <- laverton_sales_boning_400028_11901854 %>% 
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 11901854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Boxed Meat

#### 6. Laverton Processing Sales Boxed Meat (400000-10501854)

```{r}
# Sales — external customers
laverton_sales_boxed_meat_400000_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Bone") %>%
  filter(`Floor` == "Boxed Meat") %>% 
  filter(!`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them out
  "LavertonSow",
  "LavertonCommodity",
  "Laverton6Way"
  )) 
laverton_sales_boxed_meat_400000_10501854_new <- laverton_sales_boxed_meat_400000_10501854 %>% 
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 6. Laverton Processing Sales Intercompany Boxed Meat (400028-10501854)

```{r}
# Intercompany Sales — internal transfers
laverton_sales_boxed_meat_400028_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Bone") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them in
  "LavertonSow",
  "LavertonCommodity",
  "Laverton6Way"
  )) 
laverton_sales_boxed_meat_400028_10501854_new <- laverton_sales_boxed_meat_400028_10501854 %>% 
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

# Final Stage

## Join all prepared data together to create the main data

```{r}
all_revenue <- bind_rows(
  farm_sales_400000_10001812_new,
  farm_sales_400028_10001812_new,
  meat_sales_kill_400000_10201816_new,
  meat_sales_kill_400028_10201816_new,
  meat_sales_boning_400000_11901816_new,
  meat_sales_boning_400028_11901816_new,
  meat_sales_boxed_meat_400000_10501816_new,
  meat_sales_boxed_meat_400028_10501816_new,
  meat_sales_400000_10001814_new,
  laverton_sales_kill_400000_10201854_new,
  laverton_sales_kill_400028_10201854_new,
  laverton_sales_boning_400000_11901854_new,
  laverton_sales_boning_400028_11901854_new,
  laverton_sales_boxed_meat_400000_10501854_new,
  laverton_sales_boxed_meat_400028_10501854_new
  )
```

## Some changes to the main data based on guidance

```{r}
# Here are some special conditions, filtering that i applied due to guidance from my manager, some are only tempotarily, some are because of the way data was recorded (unwanted data get in the way so need to be filter out)
all_revenue <- all_revenue %>%
  mutate(Abattoir = if_else(is.na(Abattoir) | Abattoir == "", "EXTERNAL", Abattoir)) %>%  # fill blank Abattoir and also when its External because external mean the process did not happen within the company so there is no need to include this result
  mutate(`Customer name` = if_else(
    BU == "2.Meat Processing" & Tab %in% c("Boxed Meat", "Meat Trade") & `SOP Unicode` == "CommodityChilInternalVA",
    "Commodity to VA",
    `Customer name`
    # Change name for some customer based on guidance
  )) %>%
  mutate(Month = month.name[Period]) %>%
  mutate(`Customer Group` = if_else(`Customer Group` == "Wangarrata", "Wangaratta", `Customer Group`)) %>%  # fix typo
  filter(!(toupper(Abattoir) == "LAVERTON" & Tab == "Kill" & str_detect(`Customer name`, "6Way|Commodity")))  # remove intercompany rows already captured elsewhere
```

## Join Volume and Weight to the Main Data

```{r}
all_revenue_new <- all_revenue %>%
  # Standardise key columns to uppercase before joining
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    Abattoir = toupper(Abattoir),
    Month = toupper(Month),
    Tab = toupper(Tab)
  ) %>%
  left_join(
    volume_farm_raw %>%
      filter(!(`Int/Ext` %in% "External" & Tab == "Farm")) %>%   # exclude external Farm rows
      filter(!(Service == "live" & Tab %in% c("Kill", "Bone"))) %>%  # exclude live service rows
      mutate(
        Unicode = toupper(Unicode),
        Abattoir = toupper(Abattoir),
        Month = toupper(Month),
        Tab = toupper(Tab),
        Units = as.numeric(Units),
        `Avg Weight` = as.numeric(`Avg Weight`),
        `Total Weight` = as.numeric(`Total Weight`)
      ) %>%
      # Aggregate to one row per key to avoid row duplication on join
      group_by(Unicode, Abattoir, Month, Tab) %>%
      summarise(
        `Item Code` = first(`Item Code`),
        Units = sum(Units, na.rm = TRUE),
        `Avg Weight` = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("SOP Unicode" = "Unicode", "Abattoir" = "Abattoir", "Month" = "Month", "Tab" = "Tab")
  )
```

## Join Price to the Main Data

```{r}
# Split by Tab to apply the correct price source for each type
all_revenue_final <- bind_rows(
  # Join Farm Tab to Carcass Price, add condition: FCOROWAWoolworths inherits price from FEXTERNALBig River Pork - Coles
  all_revenue_new %>%
    mutate(`SOP Unicode` = str_trim(`SOP Unicode`)) %>%
    filter(Tab == "FARM") %>%
    left_join(
      carcass_price_data %>%
        mutate(`Farm Unicode` = toupper(str_trim(`Farm Unicode`)), Abattoir = toupper(Abbatoir)) %>%
        pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Carcass Price") %>%
        mutate(Period = as.integer(Period)) %>%
        select(`Farm Unicode`, Abattoir, Period, `Carcass Price`) %>%
        bind_rows(
          filter(., `Farm Unicode` == toupper(str_trim("FEXTERNALBig River Pork - Coles"))) %>%
            mutate(`Farm Unicode` = toupper(str_trim("FCOROWAWoolworths")))
        ),
      by = c("SOP Unicode" = "Farm Unicode", "Abattoir", "Period")
    ),
  # Join Bone Tab to Fee Data
  all_revenue_new %>%
    mutate(`SOP Unicode` = str_trim(`SOP Unicode`)) %>%
    filter(Tab == "BONE") %>%
    left_join(
      bone_fee_data %>%
        mutate(`SOP Unicode` = toupper(str_trim(`SOP Unicode`)), Abattoir = toupper(Abbatoir)) %>%
        pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Fee") %>%
        mutate(Period = as.integer(Period)) %>%
        select(`SOP Unicode`, Abattoir, Period, Fee),
      by = c("SOP Unicode", "Abattoir", "Period")
    ),
  # join Kill tab to Fee Data 
  all_revenue_new %>%
    mutate(`SOP Unicode` = str_trim(`SOP Unicode`)) %>%
    filter(Tab == "KILL") %>%
    left_join(
      kill_fee_data %>%
        mutate(`SOP Unicode` = toupper(str_trim(`SOP Unicode`)), Abattoir = toupper(Abbatoir)) %>%
        pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Fee") %>%
        mutate(Period = as.integer(Period)) %>%
        select(`SOP Unicode`, Abattoir, Period, Fee),
      by = c("SOP Unicode", "Abattoir", "Period")
    ),
  # All other Tab types — no price applied
  all_revenue_new %>%
    filter(is.na(Tab) | !Tab %in% c("FARM", "BONE", "KILL"))
)
```

## Calculation for Value by Weight x Carcass Price

```{r}
# Farm: Total Weight x Carcass Price | Bone/Kill: Units x Fee
all_revenue_calculated <- all_revenue_final %>%
  mutate(Value = case_when(
    Tab == "FARM" ~ `Total Weight` * `Carcass Price`,
    Tab %in% c("BONE", "KILL") ~ Units * Fee,
    TRUE ~ NA_real_))
```

## Write down the file

```{r}
write.csv(all_revenue_calculated, "GL_DB Template.csv", row.names = FALSE)
```

# Extra Debugging Code

### Check whether Unit x Avg Weight = Total Weight for every Unicode (result should only return TRUE and NA for check column)

```{r}
check_1 <- all_revenue_new %>%
  mutate(check = round(Units * `Avg Weight`, 2) == round(`Total Weight`, 2)) 
check_1
```

### Check whether the same item has different Item Code (must return 0)

```{r}
check_2 <- volume_farm_raw %>%
  mutate(
    Unicode = toupper(Unicode),
    Abattoir = toupper(Abattoir),
    Month = toupper(Month),
    Tab = toupper(Tab)
  ) %>%
  group_by(Unicode, Abattoir, Month, Tab) %>%
  summarise(n_item_codes = n_distinct(`Item Code`), .groups = "drop") %>%
  filter(n_item_codes > 1)
check_2
```

### Checking Unmatched Customers (the result should ideally return 0)

```{r}
all_captured <- bind_rows(
  farm_sales_400000_10001812,
  farm_sales_400028_10001812,
  meat_sales_kill_400000_10201816,
  meat_sales_kill_400028_10201816,
  meat_sales_boning_400000_11901816,
  meat_sales_boning_400028_11901816,
  meat_sales_boxed_meat_400000_10501816,
  meat_sales_boxed_meat_400028_10501816,
  meat_sales_400000_10001814,
  laverton_sales_kill_400000_10201854,
  laverton_sales_kill_400028_10201854,
  laverton_sales_boning_400000_11901854,
  laverton_sales_boning_400028_11901854,
  laverton_sales_boxed_meat_400000_10501854,
  laverton_sales_boxed_meat_400028_10501854
)
check_3 <- customer_data %>%
  anti_join(all_captured, by = names(customer_data))
check_3
```
