---
title: "Finance Calculating"
format: html
editor: visual
---

# Prepare Data

## Library Loading

```{r}
library(readxl)
library(readr)
library(dplyr)
library(openxlsx)
library(tidyr)
library(lubridate)
library(openxlsx2)
library(stringr)
```

## Data Input

```{r, warning=FALSE}
# Read everything as text with no headers
volume_raw <- read_excel(
  "C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/SOP Volumes.xlsx",
  sheet = "Sheet1",
  col_names = FALSE,
  col_types = "text"
)
# The reason for loading data directly from OneDrive is that the data will be update frequency by putting it inside a shared folder
carcass_price_data <- wb_to_df("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Prices.xlsb", sheet = "Carcass Price")
bone_fee_data <- wb_to_df("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Prices.xlsb", sheet = "Bone Fee")
kill_fee_data <- wb_to_df("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Prices.xlsb", sheet = "Kill Fee")
item_price_data <- wb_to_df("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Prices.xlsb", sheet = "BM PRice")
packaging_price_data <- wb_to_df("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Prices.xlsb", sheet = "Packaging VA")
gl_cc_data <- read_excel("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Master Data..xlsx", sheet = "GL & CC")
customer_data <- read_excel("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Master Data..xlsx", sheet = "Customer")
VA_brand_data <- read_excel("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Master Data..xlsx", sheet = "VA")
trade_allowance_data <- read_excel("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Trade Allowance.xlsx", sheet = "Sheet1")
rates_and_allocation_data <- read_excel("C:/Users/ATran2/OneDrive - JBS/Forecast Project - Documents/Rates and Allocation.xlsx", sheet = "Sheet1") 
```

## Data Processing

```{r}
# Remove extra spaces in BU naming (e.g. "1. Farming" → "1.Farming")
gl_cc_data <- gl_cc_data %>%
  mutate(BU = str_replace_all(BU, "(\\d+\\.)\\s+", "\\1"))

# Process rate and allocation data for it to combatible 
rates_and_allocation_data <- rates_and_allocation_data %>%
  filter(!is.na(Brand)) %>%
  mutate(`%` = `%` / sum(`%`), .by = Brand)


# Split volume_raw into three data types based on col 2 identifier
volume_farm_raw <- volume_raw %>%
  filter(`...2` %in% c("Farm", "Kill", "Bone")) %>%
  select(1:23)

volume_bone_raw <- volume_raw %>%
  filter(`...2` %in% c("2.Meat Processing", "6.Laverton Processing")) %>%
  select(1:23)

volume_va_raw <- volume_raw %>%
  filter(`...2` == "3.Meat Sales") %>%
  select(1:23)

# Assign names for each separate data
colnames(volume_farm_raw) <- c("Unicode", "Tab", "Week", "Month", "Year", "Abattoir", "Service", "Int/Ext", "Vendor Type", "Customer Code", "Customer name", "Item type", "Item Code", "Item Description", "Run", "Storage", "Type", "Group", "Primal", "Units", "Avg Weight", "Total Weight", "Price")

colnames(volume_bone_raw) <- c("Unicode", "Tab", "Week", "Month", "Year", "Abattoir", "Service", "Int/Ext", "Vendor Type", "Customer Code", "Customer name", "Item type", "Item Code", "Item Description", "Run", "Storage", "Type", "Group", "Primal", "Units", "Avg Weight", "Total Weight", "Price")

colnames(volume_va_raw)   <- c("Unicode", "Tab", "Week", "Month", "Year", "Abattoir", "Service", "Int/Ext", "Vendor Type", "Customer Code", "Customer name", "Item type", "Item Code", "Item Description", "Run", "Storage", "Type", "Group", "Primal", "Units", "Avg Weight", "Total Weight", "Price")

# Remove duplicated Item to prevent potential error in the future
item_price_data <- item_price_data %>%
  select(-`Item Description`) %>%
  mutate(`Item Key` = str_trim(`Item Key`)) %>%
  group_by(`Item Key`) %>%
  slice(1) %>%
  ungroup()
```

# Revenue Account Creation

## Farm Section

#### 1.Farming Operations Sales (400000-10001812)

```{r}
# Sales — external customers
farm_sales_400000_10001812 <- customer_data %>% 
  filter(`BU` == "1.Farming Operations") %>% 
  filter(!`SOP Unicode` %in% c(
    # These are Intercompany customer which was provided by the company so i filter these customer out
    "FLAVERTON6WAY",
    "FCOROWA6Way",
    "FLAVERTONCommodity",
    "FCOROWACommodity",
    "FOtherX",
    "FLAVERTONSow Commodity"
  )) 
farm_sales_400000_10001812_new <- farm_sales_400000_10001812 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10001812),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 1.Farming Operations Intercompany Sales (400028-10001812)

```{r}
# Intercompany Sales — internal transfers 
farm_sales_400028_10001812 <- customer_data %>% 
  filter(`BU` == "1.Farming Operations") %>% 
  filter(`SOP Unicode` %in% c(
    # These are Intercompany customer which was provided by the company so i filter them in
    "FLAVERTON6WAY",
    "FCOROWA6Way",
    "FLAVERTONCommodity",
    "FCOROWACommodity",
    "FOtherX",
    "FLAVERTONSow Commodity"
  )) 
farm_sales_400028_10001812_new <- farm_sales_400028_10001812 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10001812),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Corowa Meat Processing

### Kill Floor

#### 2.Meat Processing Sales Kill Floor (400000-10201816)

```{r}
# Sales — external customers
meat_sales_kill_400000_10201816 <- customer_data %>%
  filter(`BU` == "2.Meat Processing") %>%
  filter(Tab == "Kill") %>%
  filter(!`Customer Group` %in% c("Edible Offal", "Inedible Offal")) %>%  # exclude offal — captured separately
  filter(!`SOP Unicode` %in% c(
    # These are Intercompany customers so filter them out
    "COROWA6Way",
    "COROWACommodity"
  ))
meat_sales_kill_400000_10201816_new <- meat_sales_kill_400000_10201816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10201816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 2.Meat Processing Sales Intercompany Kill Floor (400028-10201816)

```{r}
# Intercompany Sales — internal transfers
meat_sales_kill_400028_10201816 <- customer_data %>%
  filter(`BU` == "2.Meat Processing") %>%
  filter(Tab == "Kill") %>%
  filter(!`Customer Group` %in% c("Edible Offal", "Inedible Offal")) %>%  # exclude offal — captured separately
  filter(`SOP Unicode` %in% c(
    # These are Intercompany customers so filter them in
    "COROWA6Way",
    "COROWACommodity"
  ))
meat_sales_kill_400028_10201816_new <- meat_sales_kill_400028_10201816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10201816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Boning Room

#### 2.Meat Processing Sales Boning Room (400000-11901816)

```{r}
# Sales — external customers
meat_sales_boning_400000_11901816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab == "Bone") %>% 
  filter(`Floor` == "Bone") %>% 
  filter(!`SOP Unicode` %in% c(
    # These are Intercompany customers so filter them out
    "COROWA6Way",
    "COROWACommodity"
  )) 
meat_sales_boning_400000_11901816_new <- meat_sales_boning_400000_11901816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 11901816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 2.Meat Processing Sales Intercompany Boning Room (400028-11901816)

```{r}
# Intercompany Sales — internal transfers
meat_sales_boning_400028_11901816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab == "Bone") %>% 
  filter(`Floor` == "Bone") %>% 
  filter(`SOP Unicode` %in% c(
    # These are Intercompany customers so filter them in
    "COROWA6Way",
    "COROWACommodity"
  )) 
meat_sales_boning_400028_11901816_new <- meat_sales_boning_400028_11901816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 11901816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Meat Boxed

#### 2.Meat Processing Sale Boxed Meat (400000-10501816)

```{r}
# Sales — external customers
meat_sales_boxed_meat_400000_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab %in% c("Boxed Meat", "Meat Trade")) %>%
  filter(`Floor` %in% c("Boxed Meat", "Meat Trade")) %>% 
  filter(!`SOP Unicode` %in% c(
    # This is an Intercompany customer so filter it out
    "CommodityChilInternalVA"
  )) 
meat_sales_boxed_meat_400000_10501816_new <- meat_sales_boxed_meat_400000_10501816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 2.Meat Processing Sale Intercompany Boxed Meat (400028-10501816)

```{r}
# Intercompany Sales — internal transfers
meat_sales_boxed_meat_400028_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab %in% c("Boxed Meat", "Meat Trade")) %>%
  filter(`Floor` %in% c("Boxed Meat", "Meat Trade")) %>% 
  filter(`SOP Unicode` %in% c(
    # This is an Intercompany customer so filter it in
    "CommodityChilInternalVA"
  )) 
meat_sales_boxed_meat_400028_10501816_new <- meat_sales_boxed_meat_400028_10501816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Meat Sales

#### 3.Meat Sales (400000-10001814)

```{r}
# Sales — external customers, no intercompany filtering needed for this BU
meat_sales_400000_10001814 <- customer_data %>% 
  filter(`BU` == "3.Meat Sales") %>% 
  filter(Tab == "VA") 
meat_sales_400000_10001814_new <- meat_sales_400000_10001814 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10001814),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Laverton Processing

### Kill Floor

#### 6. Laverton Processing Sales Kill Floor (400000-10201854)

```{r}
# Sales — external customers
laverton_sales_kill_400000_10201854 <- customer_data %>%
  filter(`BU` == "6.Laverton Processing") %>%
  filter(Tab == "Kill") %>%
  filter(`Floor` == "Kill") %>%
  filter(!`Customer Group` %in% c("Edible Offal", "Inedible Offal")) %>%  # exclude offal — captured separately
  filter(!`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them out
  "Laverton6Way",
  "LavertonCommodity",
  "LAVERTONEdibleOffal",
  "LAVERTONLaverton - Purchase",
  "LAVERTONPW Opportunity - Sow",
  "LavertonSow",
  "LAVERTONSow Commodity"
  ))
laverton_sales_kill_400000_10201854_new <- laverton_sales_kill_400000_10201854 %>% 
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10201854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 6. Laverton Processing Sales Intercompany Kill Floor (400028-10201854)

```{r}
# Intercompany Sales — internal transfers
laverton_sales_kill_400028_10201854 <- customer_data %>%
  filter(`BU` == "6.Laverton Processing") %>%
  filter(Tab == "Kill") %>%
  filter(`Floor` == "Kill") %>%
  filter(!`Customer Group` %in% c("Edible Offal", "Inedible Offal")) %>%  # exclude offal — captured separately
  filter(`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them in
  "Laverton6Way",
  "LavertonCommodity",
  "LAVERTONEdibleOffal",
  "LAVERTONLaverton - Purchase",
  "LAVERTONPW Opportunity - Sow",
  "LavertonSow",
  "LAVERTONSow Commodity"
  ))
laverton_sales_kill_400028_10201854_new <- laverton_sales_kill_400028_10201854 %>% 
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10201854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Boning Room

#### 6. Laverton Processing Sales Boning Room (400000-11901854)

```{r}
# Sales — external customers
laverton_sales_boning_400000_11901854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Bone") %>%
  filter(`Floor` == "Bone") %>% 
  filter(!`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them out
  "Laverton6Way",
  "LavertonCommodity",
  "LAVERTONLaverton - Purchase",
  "LAVERTONPW Opportunity - Sow",
  "LAVERTONSow Commodity"
  )) 
laverton_sales_boning_400000_11901854_new <- laverton_sales_boning_400000_11901854 %>% 
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 11901854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 6. Laverton Processing Sales Intercompany Boning Room (400028-11901854)

```{r}
# Intercompany Sales — internal transfers
laverton_sales_boning_400028_11901854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Bone") %>% 
  filter(`Floor` == "Bone") %>% 
  filter(`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them in
  "Laverton6Way",
  "LavertonCommodity",
  "LAVERTONLaverton - Purchase",
  "LAVERTONPW Opportunity - Sow",
  "LAVERTONSow Commodity"
  )) 
laverton_sales_boning_400028_11901854_new <- laverton_sales_boning_400028_11901854 %>% 
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 11901854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Boxed Meat

#### 6. Laverton Processing Sales Boxed Meat (400000-10501854)

```{r}
# Sales — external customers
laverton_sales_boxed_meat_400000_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Bone") %>%
  filter(`Floor` == "Boxed Meat") %>% 
  filter(!`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them out
  "LavertonSow",
  "LavertonCommodity",
  "Laverton6Way"
  )) 
laverton_sales_boxed_meat_400000_10501854_new <- laverton_sales_boxed_meat_400000_10501854 %>% 
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

#### 6. Laverton Processing Sales Intercompany Boxed Meat (400028-10501854)

```{r}
# Intercompany Sales — internal transfers
laverton_sales_boxed_meat_400028_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Bone") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`SOP Unicode` %in% c(
  # These are Intercompany customers so filter them in
  "LavertonSow",
  "LavertonCommodity",
  "Laverton6Way"
  )) 
laverton_sales_boxed_meat_400028_10501854_new <- laverton_sales_boxed_meat_400028_10501854 %>% 
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

# Offal (Edible and Inedible Data)

## Corowa Offal Data

### Edible Offal Sales (400000-10001816)

```{r}
# Sales — external customers
edible_offal_sales_400000_10001816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab == "Kill") %>% 
  filter(`Floor` == "Kill") %>% 
  filter(`Customer Group` == "Edible Offal")

edible_offal_sales_400000_10001816_new <- edible_offal_sales_400000_10001816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10001816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Inedible Offal Sales (400000-10801816)

```{r}
# Sales — external customers
inedible_offal_sales_400000_10801816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab == "Kill") %>% 
  filter(`Floor` == "Kill") %>% 
  filter(`Customer Group` == "Inedible Offal")

inedible_offal_sales_400000_10801816_new <- inedible_offal_sales_400000_10801816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10801816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Laverton Offal Data

### Intercompany Edible Offal Sales (400028-10001854)

```{r}
# Sales — intercompany, this happen because Laverton consolidate its Edible Offal with Corowa under Corowa name to sell to the customer
edible_offal_sales_400028_10001854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Kill") %>% 
  filter(`Floor` == "Kill") %>% 
  filter(`Customer Group` == "Edible Offal")

edible_offal_sales_400028_10001854_new <- edible_offal_sales_400028_10001854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10001854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Inedible Offal Sales (400000-10801854)

```{r}
# Sales — external customers
inedible_offal_sales_400000_10801854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(Tab == "Kill") %>% 
  filter(`Floor` == "Kill") %>% 
  filter(`Customer Group` == "Inedible Offal")

inedible_offal_sales_400000_10801854_new <- inedible_offal_sales_400000_10801854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10801854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

# Commodity Data (Boxed Meat Floor)

## Commodity Data Corowa

### Corowa 6Way Data Frozen (400000-10501816)

```{r}
# Sales — external customers for corowa 6way frozen products
corowa_6way_frz_400000_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "6 Way") %>% 
  filter(`Sales Type` == "FRZ")

corowa_6way_frz_400000_10501816_new <- corowa_6way_frz_400000_10501816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Corowa Commodity Data Frozen (400000-10501816)

```{r}
# Sales — external customers for corowa 6way frozen products
corowa_commodity_frz_400000_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Commodity") %>% 
  filter(`Sales Type` == "FRZ")

corowa_commodity_frz_400000_10501816_new <- corowa_commodity_frz_400000_10501816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Corowa Commodity Data Frozen (400028-10501816) (equivalent to VA sales)

```{r}
# Sales — Intercompany as those products are transfering to VA 
corowa_commodity_frz_400028_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Commodity") %>% 
  filter(`Sales Type` == "FRZ")

corowa_commodity_frz_400028_10501816_new <- corowa_commodity_frz_400028_10501816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Laverton 6Way Data Frozen (400028-10501854)

```{r}
# Sales — Intercompany as those products are transfering to corowa 
laverton_6way_frz_400028_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "6 Way") %>% 
  filter(`Sales Type` == "FRZ")

laverton_6way_frz_400028_10501854_new <- laverton_6way_frz_400028_10501854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Laverton Sow Data Frozen (400000-10501854)

```{r}
# Sales — external customers for corowa 6way frozen products - Only Laverton has Sow account
laverton_sow_frz_400000_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Sow") %>% 
  filter(`Sales Type` == "FRZ")

laverton_sow_frz_400000_10501854_new <- laverton_sow_frz_400000_10501854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Laverton Commodity Data Frozen (400028-10501854)

```{r}
# Sales — Intercompany since the product will be frozen before moving to Corowa
laverton_commodity_frz_400028_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Commodity") %>% 
  filter(`Sales Type` == "FRZ")

laverton_commodity_frz_400028_10501854_new <- laverton_commodity_frz_400028_10501854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400028, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Laverton Commodity Data Chilled (400000-10501854)

```{r}
# Sales — external customers for laverton commodity chilled products
laverton_commodity_chil_400000_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Commodity") %>% 
  filter(`Sales Type` == "Chil")

laverton_commodity_chil_400000_10501854_new <- laverton_commodity_chil_400000_10501854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Meat Trade Data Laverton -\> Corowa

```{r}
# Sales - a special type of data transfering from Laverton 6Way, Commodity and Edible in Intercompany Sales to Corowa and count as Meat Trade product

meat_trade_data <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Floor` == "Meat Trade") %>% 
  filter(`Service` %in% c("6 Way", "Commodity", "Edible Offal"))


meat_trade_data_new <- meat_trade_data %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400000, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

# Final Stage: Join data, apply calculation and apply special condition for each specific data

## Farm Data

### Join all prepared data together to create the main data

```{r}
all_revenue_farm <- bind_rows(
  farm_sales_400000_10001812_new,
  farm_sales_400028_10001812_new,
  meat_sales_kill_400000_10201816_new,
  meat_sales_kill_400028_10201816_new,
  meat_sales_boning_400000_11901816_new,
  meat_sales_boning_400028_11901816_new,
  meat_sales_boxed_meat_400000_10501816_new,
  meat_sales_boxed_meat_400028_10501816_new,
  meat_sales_400000_10001814_new,
  laverton_sales_kill_400000_10201854_new,
  laverton_sales_kill_400028_10201854_new,
  laverton_sales_boning_400000_11901854_new,
  laverton_sales_boning_400028_11901854_new,
  laverton_sales_boxed_meat_400000_10501854_new,
  laverton_sales_boxed_meat_400028_10501854_new
  )
```

### Some changes to the main data based on guidance

```{r}
# Here are some special conditions, filtering that i applied due to guidance from my manager, some are only tempotarily, some are because of the way data was recorded (unwanted data get in the way so those data need to be filter out)
all_revenue_farm <- all_revenue_farm %>%
  mutate(Abattoir = if_else(is.na(Abattoir) | Abattoir == "", "EXTERNAL", Abattoir)) %>%  # fill blank Abattoir and also when its External because external mean the process did not happen within the company so there is no need to include this result
  mutate(`Customer name` = if_else(
    BU == "2.Meat Processing" & Tab %in% c("Boxed Meat", "Meat Trade") & `SOP Unicode` == "CommodityChilInternalVA",
    "Commodity to VA",
    `Customer name`
    # Change name for some customer based on guidance
  )) %>%
  mutate(Month = month.name[Period]) %>%
  mutate(`Customer Group` = if_else(`Customer Group` == "Wangarrata", "Wangaratta", `Customer Group`)) %>%  # fix typo
filter(!(toupper(Abattoir) == "LAVERTON" & Tab == "Kill" & str_detect(toupper(`Customer name`), "6WAY|COMMODITY"))) # Temporarily special condition
```

### Join Volume and Weight to the Main Data

```{r}
# Pre-standardise keys once
all_revenue_farm_std <- all_revenue_farm %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(Month),
    Tab           = toupper(Tab)
  )

# Join volume_farm_raw on SOP Unicode + Abattoir + Month + Tab
all_revenue_farm_new <- all_revenue_farm_std %>%
  left_join(
    volume_farm_raw %>%
      filter(!(`Int/Ext` %in% "External" & Tab == "Farm")) %>%
      filter(!(Service == "live" & Tab %in% c("Kill", "Bone"))) %>%
      mutate(
        Unicode        = toupper(Unicode),
        Abattoir       = toupper(Abattoir),
        Month          = toupper(Month),
        Tab            = toupper(Tab),
        Units          = as.numeric(Units),
        `Avg Weight`   = as.numeric(`Avg Weight`),
        `Total Weight` = as.numeric(`Total Weight`)
      ) %>%
      group_by(Unicode, Abattoir, Month, Tab) %>%
      summarise(
        `Item Code`    = first(`Item Code`),
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("SOP Unicode" = "Unicode", "Abattoir", "Month", "Tab")
  )
```

### Join Price to the Main Data

```{r}
# Split by Tab to apply the correct price source for each type
all_revenue_farm_final <- bind_rows(
  # Join Farm Tab to Carcass Price, add condition: FCOROWAWoolworths inherits price from FEXTERNALBig River Pork - Coles
  all_revenue_farm_new %>%
    mutate(`SOP Unicode` = str_trim(`SOP Unicode`)) %>%
    filter(Tab == "FARM") %>%
    left_join(
      carcass_price_data %>%
        mutate(`Farm Unicode` = toupper(str_trim(`Farm Unicode`)), Abattoir = toupper(Abbatoir)) %>%
        pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Carcass Price") %>%
        mutate(Period = as.integer(Period)) %>%
        select(`Farm Unicode`, Abattoir, Period, `Carcass Price`) %>%
        bind_rows(
          filter(., `Farm Unicode` == toupper(str_trim("FEXTERNALBig River Pork - Coles"))) %>%
            mutate(`Farm Unicode` = toupper(str_trim("FCOROWAWoolworths")))
        ),
      by = c("SOP Unicode" = "Farm Unicode", "Abattoir", "Period")
    ),
  # Join Bone Tab to Fee Data
  all_revenue_farm_new %>%
    mutate(`SOP Unicode` = str_trim(`SOP Unicode`)) %>%
    filter(Tab == "BONE") %>%
    left_join(
      bone_fee_data %>%
        mutate(`SOP Unicode` = toupper(str_trim(`SOP Unicode`)), Abattoir = toupper(Abbatoir)) %>%
        pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Fee") %>%
        mutate(Period = as.integer(Period)) %>%
        select(`SOP Unicode`, Abattoir, Period, Fee),
      by = c("SOP Unicode", "Abattoir", "Period")
    ),
  # join Kill tab to Fee Data 
  all_revenue_farm_new %>%
    mutate(`SOP Unicode` = str_trim(`SOP Unicode`)) %>%
    filter(Tab == "KILL") %>%
    left_join(
      kill_fee_data %>%
        mutate(`SOP Unicode` = toupper(str_trim(`SOP Unicode`)), Abattoir = toupper(Abbatoir)) %>%
        pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Fee") %>%
        mutate(Period = as.integer(Period)) %>%
        select(`SOP Unicode`, Abattoir, Period, Fee),
      by = c("SOP Unicode", "Abattoir", "Period")
    ),
  # All other Tab types — no price applied
  all_revenue_farm_new %>%
    filter(is.na(Tab) | !Tab %in% c("FARM", "BONE", "KILL"))
)
```

### Calculation for Value by Weight x Carcass Price

```{r}
# Farm: Total Weight x Carcass Price | Bone/Kill: Units x Fee
all_revenue_farm_calculated <- all_revenue_farm_final %>%
  mutate(Value = case_when(
    Tab == "FARM" ~ `Total Weight` * `Carcass Price`,
    Tab %in% c("BONE", "KILL") ~ Units * Fee,
    TRUE ~ NA_real_))
```

## Join Price Data to Volume Data for Bone Data in order to calculate the value for each item

```{r}
# Join volume_bone_raw with item_price_data on Item Code, calculate Value per item, then aggregate by BU/Abattoir/Month
volume_bone_price_calculated <- volume_bone_raw %>%
  mutate(
    Tab         = toupper(Tab),
    Abattoir    = toupper(Abattoir),
    Month       = toupper(Month),
    Units       = as.numeric(Units),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code` = str_trim(`Item Code`)
  ) %>%
  left_join(
    item_price_data,
    by = c("Item Code" = "Item Key")
  ) %>%
  mutate(Value = `Total Weight` * `Current Price`)
```

## Offal Data from Bone Data

### Join all data to create main data

```{r}
all_revenue_offal_data <- bind_rows(
  edible_offal_sales_400000_10001816_new,
  inedible_offal_sales_400000_10801816_new,
  edible_offal_sales_400028_10001854_new,
  inedible_offal_sales_400000_10801854_new
  )
# Pre-standardise keys once
all_revenue_offal_data_std <- all_revenue_offal_data %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  )
```

### Filter calculated bone data for offal data

```{r}
# Group value for Corowa and filter out unrelevant data for Offal Data
volume_offal_corowa <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(Type %in% c("INEDIBLE", "OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = case_when(
      Type == "INEDIBLE"    ~ "Inedible Offal",
      Type == "OFFALS"      ~ "Edible Offal",
      Type == "BACON CUTS"  ~ "Edible Offal",
      TRUE ~ NA_character_
    )
  ) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  )

# Group value for Corowa and filter out unrelevant data for Offal Data and apply special discount for Laverton since this site ship the offal to Lineage whom charge a special discount which is also the reason why Corowa and Laverton was splitted
volume_offal_laverton <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(Type %in% c("INEDIBLE", "OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = case_when(
      Type == "INEDIBLE"    ~ "Inedible Offal",
      Type == "OFFALS"      ~ "Edible Offal",
      Type == "BACON CUTS"  ~ "Edible Offal",
      TRUE ~ NA_character_
    )
  ) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Value = if_else(`Customer Group` == "Edible Offal", Value - 0.51 * `Total Weight`, Value))

# Combine Laverton and Corowa 
volume_offal_combined <- bind_rows(volume_offal_corowa, volume_offal_laverton)

# Join item-level volume + value into the bone revenue data on BU + Abattoir + Month
all_revenue_offal_data_calculated <- all_revenue_offal_data_std %>%
  left_join(
    volume_offal_combined %>% select(-`Customer name`),
    by = c("BU" = "Tab", "Abattoir", "Month", "Customer Group")
  )
```

## 6Way and Sow Data from Bone Data

### Join all data to create main data

```{r}
all_revenue_6way_sow_data <- bind_rows(
  corowa_6way_frz_400000_10501816_new,
  laverton_6way_frz_400028_10501854_new,
  laverton_sow_frz_400000_10501854_new
  )

# Pre-standardise keys once
all_revenue_6way_sow_data_std <- all_revenue_6way_sow_data %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  )
```

### Filter calculated bone data for 6 way and sow data

```{r}
# Group value for Corowa and filter out unrelevant data for commodity Data 
volume_6way_sow_corowa <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(toupper(Run) == "6 WAY") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = "6 Way"
    ) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  )

# Group value for Laverton and filter out unrelevant data for commodity Data 
volume_6way_sow_laverton <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(toupper(Run) %in% c("6 WAY", "SOW BONE")) %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group` = case_when(
    toupper(Run) == "6 WAY" ~ "6 Way",
    toupper(Run) == "SOW BONE"   ~ "Sow",
    TRUE ~ NA_character_
    )) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Value = if_else(`Customer Group` == "6 Way", Value - 0.51 * `Total Weight`, Value))

# Combine Corowa and Laverton
volume_6way_sow_combined <- bind_rows(volume_6way_sow_corowa, volume_6way_sow_laverton)

# Join item-level volume + value into the bone revenue data on BU + Abattoir + Month
all_revenue_6way_sow_data_calculated <- all_revenue_6way_sow_data_std %>%
  left_join(
    volume_6way_sow_combined %>% select(-`Customer name`),
    by = c("BU" = "Tab", "Abattoir", "Month", "Customer Group")
  )
```

## Commodity Data from Bone Data for Corowa (special)

### Join all data to create main data

```{r}
all_revenue_commodity_data <- bind_rows(
  corowa_commodity_frz_400000_10501816_new,
  corowa_commodity_frz_400028_10501816_new,
  laverton_commodity_frz_400028_10501854_new,
  laverton_commodity_chil_400000_10501854_new
  )

# Pre-standardise keys once
all_revenue_commodity_data_std <- all_revenue_commodity_data %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  )
```

### Separate value of 400000 and 400028 for Corowa from 3.Meat Sales

```{r}
# Get internal VA sales which is equivalent to 400028 volume from 3.Meat Sales as the volume source for Corowa commodity bone
volume_commodity_corowa_400028 <- volume_va_raw %>%
  filter(`Vendor Type` == "Internal") %>%
  filter(`Service` == "Procurement") %>%
  mutate(
    `Item Code`    = str_trim(`Item Code`),
    Month          = toupper(Month),
    Abattoir       = toupper(Abattoir),
    `Total Weight` = as.numeric(`Total Weight`),
    `Customer Group` = "Commodity"
  )

# Filter for Corowa commodity bone and assign Customer Group - covers both 400000 and 400028
volume_commodity_corowa <- volume_bone_raw %>%
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(toupper(Run) == "COMMODITY BONE") %>%
  mutate(
    Unicode          = toupper(Unicode),
    Abattoir         = toupper(Abattoir),
    Month            = toupper(Month),
    Tab              = toupper(Tab),
    Units            = NA_real_,
    `Avg Weight`     = NA_real_,
    `Total Weight`   = as.numeric(`Total Weight`),
    `Customer Group` = "Commodity"
  ) 

# 400000 = total (volume_commodity_corowa) minus 400028 (internal), matched by Item Code + Week
volume_commodity_corowa_400000 <- volume_commodity_corowa %>%
  left_join(
    volume_commodity_corowa_400028 %>%
      select(`Item Code`, Week, Weight_400028 = `Total Weight`),
    by = c("Item Code", "Week")
  ) %>%
  mutate(`Total Weight` = `Total Weight` - coalesce(Weight_400028, 0)) %>%
  select(-Weight_400028)
```

### Calculate Value for 400000 and 400028 of Corowa from 3.Meat Sales

```{r}
volume_commodity_corowa_400028_calculated <- volume_commodity_corowa_400028 %>%
  mutate(
    Tab         = toupper(Tab),
    Abattoir    = toupper(Abattoir),
    Month       = toupper(Month),
    Units       = as.numeric(Units),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code` = str_trim(`Item Code`)
  ) %>%
  left_join(
    item_price_data,
    by = c("Item Code" = "Item Key")
  ) %>%
  mutate(Value = `Total Weight` * `Current Price`)
  

volume_commodity_corowa_400000_calculated <- volume_commodity_corowa_400000 %>%
  mutate(
    Tab         = toupper(Tab),
    Abattoir    = toupper(Abattoir),
    Month       = toupper(Month),
    Units       = as.numeric(Units),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code` = str_trim(`Item Code`)
  ) %>%
  left_join(
    item_price_data,
    by = c("Item Code" = "Item Key")
  ) %>%
  mutate(Value = `Total Weight` * `Current Price`)
```

### Group calculated bone data for commodity data - 400000 and 400028 of Corowa from 3.Meat Sales

```{r}
# Group 400028 volume by Abattoir + Month, then derive Period from Month name
volume_commodity_corowa_400028_grouped <- volume_commodity_corowa_400028_calculated %>%
  mutate(
    Abattoir         = "COROWA",
    Month            = toupper(Month),
    `Customer Group` = "Commodity"
  ) %>%
  group_by(Abattoir, Month, `Customer Group`) %>%
  summarise(
    Units          = sum(as.numeric(Units), na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Period = match(Month, toupper(month.name)))

# Join 400028 volume to its GL account rows in the revenue data
all_revenue_commodity_corowa_400028 <- all_revenue_commodity_data_std %>%
  filter(`GL Account` == 400028, `Abattoir` == "COROWA") %>%
  left_join(
    volume_commodity_corowa_400028_grouped,
    by = c("Abattoir", "Month", "Customer Group", "Period")
  )

# Group 400000 volume by Abattoir + Month, then derive Period from Month name
volume_commodity_corowa_400000_grouped <- volume_commodity_corowa_400000_calculated %>%
  mutate(
    Abattoir         = toupper(Abattoir),
    Month            = toupper(Month),
    `Customer Group` = "Commodity"
  ) %>%
  group_by(Abattoir, Month, `Customer Group`) %>%
  summarise(
    Units          = sum(as.numeric(Units), na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Period = match(Month, toupper(month.name)))

# Join 400000 volume to its GL account rows in the revenue data
all_revenue_commodity_corowa_400000 <- all_revenue_commodity_data_std %>%
  filter(`GL Account` == 400000, `Abattoir` == "COROWA") %>%
  left_join(
    volume_commodity_corowa_400000_grouped,
    by = c("Abattoir", "Month", "Customer Group", "Period")
  )

# Combine both accounts into final commodity Corowa result
all_revenue_commodity_corowa_calculated <- bind_rows(
  all_revenue_commodity_corowa_400028,
  all_revenue_commodity_corowa_400000
)
```

## Commodity Data from Bone Data for Laverton

```{r}
# CHIL storage → matches laverton_commodity_chil_400000_10501854 (GL 400000)
volume_commodity_laverton_chil <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(toupper(Run) == "COMMODITY BONE") %>%
  filter(toupper(Storage) == "CHILLED") %>%
  mutate(
    Unicode          = toupper(Unicode),
    Abattoir         = toupper(Abattoir),
    Month            = toupper(Month),
    Tab              = toupper(Tab),
    Units            = as.numeric(Units),
    `Avg Weight`     = as.numeric(`Avg Weight`),
    `Total Weight`   = as.numeric(`Total Weight`),
    `Customer Group` = "Commodity"
  ) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Period = match(Month, toupper(month.name)))

# FRZ storage → matches laverton_commodity_frz_400028_10501854 (GL 400028)
volume_commodity_laverton_frz <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(toupper(Run) == "COMMODITY BONE") %>%
  filter(toupper(Storage) == "FROZEN") %>%
  mutate(
    Unicode          = toupper(Unicode),
    Abattoir         = toupper(Abattoir),
    Month            = toupper(Month),
    Tab              = toupper(Tab),
    Units            = as.numeric(Units),
    `Avg Weight`     = as.numeric(`Avg Weight`),
    `Total Weight`   = as.numeric(`Total Weight`),
    `Customer Group` = "Commodity"
  ) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Period = match(Month, toupper(month.name))) %>%
  mutate(Value = Value - 0.51 * `Total Weight`)

# Join each to their respective GL account rows, then combine
all_revenue_commodity_laverton_chil <- all_revenue_commodity_data_std %>%
  filter(`GL Account` == 400000, toupper(Abattoir) == "LAVERTON") %>%
  left_join(
    volume_commodity_laverton_chil %>% select(-`Customer name`),
    by = c("BU" = "Tab", "Abattoir", "Month", "Customer Group", "Period")
  )

all_revenue_commodity_laverton_frz <- all_revenue_commodity_data_std %>%
  filter(`GL Account` == 400028, toupper(Abattoir) == "LAVERTON") %>%
  left_join(
    volume_commodity_laverton_frz %>% select(-`Customer name`),
    by = c("BU" = "Tab", "Abattoir", "Month", "Customer Group", "Period")
  )

all_revenue_commodity_laverton_calculated <- bind_rows(
  all_revenue_commodity_laverton_chil,
  all_revenue_commodity_laverton_frz
)
```

## Meat Trade Data

### Standardize the Data

```{r}
# Pre-standardise keys once
all_revenue_meat_trade_data_std <- meat_trade_data_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  )
```

### Match 6Way from Laverton to Corowa Meat Trade

```{r}
volume_meat_trade_6way <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(toupper(Run) %in% c("6 WAY")) %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group` = "Meat Trade",
    `Customer name`  = "Meat Trade") %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  mutate(Period = match(Month, toupper(month.name))) %>% 
  mutate(Service = "6 Way")
```

### Match Commodity Data from Laverton (FRZ) to Corowa Meat Trade

```{r}
volume_meat_trade_commodity <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(toupper(Run) == "COMMODITY BONE") %>%
  filter(toupper(Storage) == "FROZEN") %>%
  mutate(
    Unicode          = toupper(Unicode),
    Abattoir         = toupper(Abattoir),
    Month            = toupper(Month),
    Tab              = toupper(Tab),
    Units            = as.numeric(Units),
    `Avg Weight`     = as.numeric(`Avg Weight`),
    `Total Weight`   = as.numeric(`Total Weight`),
    `Customer Group` = "Meat Trade",
    `Customer name`  = "Meat Trade") %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Period = match(Month, toupper(month.name))) %>% 
  mutate(Service = "Commodity")
```

### Match Edible Data from Laverton to Corowa Meat Trade

```{r}
volume_meat_trade_edible_offal <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(Type %in% c("OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group` = "Meat Trade",
    `Customer name`  = "Meat Trade") %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Period = match(Month, toupper(month.name))) %>% 
  mutate(Service = "Edible Offal")
```

### Group all meat trade data and join them with customer account

```{r}
# Combine Corowa and Laverton
volume_meat_trade_combined <- bind_rows(volume_meat_trade_6way, volume_meat_trade_commodity, volume_meat_trade_edible_offal) %>% 
  mutate(Abattoir = "COROWA") %>% # remap Laverton → Corowa
  mutate(Tab = "2.MEAT PROCESSING")
# Join item-level volume + value into the bone revenue data on BU + Abattoir + Month
all_revenue_meat_trade_data_calculated <- all_revenue_meat_trade_data_std %>%
  left_join(
    volume_meat_trade_combined %>% select(-`Customer name`),
    by = c("BU" = "Tab", "Abattoir", "Month", "Customer Group", "Service", "Period")
  )
```

## Meat Sales Data

### Prepare the calculated data from VA raw

```{r}
# Pre-standardise keys once
all_revenue_meat_sales_data_std <- meat_sales_400000_10001814_new %>%
  mutate(
    Abattoir = "VALUE ADD",
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

volume_VA_price_calculated <- volume_va_raw %>%
  filter(`Service` == "VA Sales") %>%
  mutate(
    Tab         = toupper(Tab),
    Abattoir    = toupper(Abattoir),
    Month       = toupper(Month),
    Units          = as.numeric(Units),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code`    = str_trim(`Item Code`),
    Price          = as.numeric(Price)
  ) %>%
  mutate(Value = `Total Weight` * Price) 


all_revenue_meat_sales <- volume_VA_price_calculated %>%
  left_join(
    VA_brand_data %>% select(`Item Code`, Brand),
    by = "Item Code"
  ) %>%
  mutate(
    `Customer name`  = if_else(!is.na(Brand), Brand, `Customer name`)
  ) %>%
  select(-Brand) %>%
  group_by(Tab, Abattoir, Month, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Period = match(Month, toupper(month.name))) %>% 
  mutate(`Customer Group` = `Customer name`)
```

```{r}
# Join each to their respective GL account rows, then combine
all_revenue_meat_sales_data_calculated <- all_revenue_meat_sales_data_std %>%
  left_join(
    all_revenue_meat_sales %>% select(-`Customer name`),
    by = c("BU" = "Tab", "Abattoir", "Month", "Customer Group", "Period")
  )
```

# Expense Account Creation

## Farm Sell and Buy Back from V&V

### Gross Sales Account (400350-10001812)

```{r}
# Sales for expense account
farm_sales_400350_10001812 <- customer_data %>% 
  filter(`BU` == "1.Farming Operations") %>% 
  filter(`SOP Unicode` %in% c(
    "FLAVERTONNew Team"
  ))
farm_sales_400350_10001812_new <- farm_sales_400350_10001812 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 400350, `Cc Key` == 10001812),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Cost of Sales Account (510157-10001812)

```{r}
# Cost of Sales for expense account
farm_costs_510157_10001812 <- customer_data %>% 
  filter(`BU` == "1.Farming Operations") %>% 
  filter(`SOP Unicode` %in% c(
    "FLAVERTONNew Team"
  ))
farm_costs_510157_10001812_new <- farm_costs_510157_10001812 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 510157, `Cc Key` == 10001812),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Inter-company Sales from Farm to Corowa and Laverton

### Corowa Expense for pig from Farm Account (510167-10501816)

Warning: There is a mismatch in information between customer data and gl&cc account

```{r}
# Expense account for corowa from farm pig
corowa_farm_510167_10501816 <- customer_data %>% 
  filter(`BU` == "1.Farming Operations") %>% 
  filter(`Customer Group` %in% c(
    "Other Transactions")) %>% 
  mutate(`Abattoir` = "Corowa",
         `BU` = "2.Meat Processing")
  
corowa_farm_510167_10501816_new <- corowa_farm_510167_10501816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 510167, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Laverton Expense for pig from Farm Account (510167-10501854)

```{r}
# Expense account for laverton from farm pig
laverton_farm_510167_10501854 <- customer_data %>% 
  filter(`BU` == "1.Farming Operations") %>% 
  filter(`Customer Group` %in% c(
    "Other Transactions"
  )) %>% 
  mutate(`Abattoir` = "Laverton",
         `BU` = "6.Laverton Processing")
  
laverton_farm_510167_10501854_new <- laverton_farm_510167_10501854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 510167, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Inter-company Cost of Sales for Meat Trades from Laverton to Corowa (510167-10501816)

```{r}
# Expense account for corowa meat trade coming from meat trasfering from corowa to laverton
meat_trade_510167_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Customer Group` %in% c(
    "Meat Trade"
  )) 
  
meat_trade_510167_10501816_new <- meat_trade_510167_10501816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 510167, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 3.Meat Sales Cost of Sales from procurement internal transactions (510167-10001814)

```{r}
# Expense account for buying meat from internal 
meat_sales_internal_510167_10001814 <- customer_data %>% 
  filter(`BU` == "3.Meat Sales") %>% 
  filter(`Customer Group` == "Meat Purchase")

meat_sales_internal_510167_10001814_new <- meat_sales_internal_510167_10001814 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 510167, `Cc Key` == 10001814),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 3.Meat Sales Cost of Sales from procurement external transactions (500031-1001814)

```{r}
# Expense account for buying meat from external
meat_sales_external_500031_10001814 <- customer_data %>% 
  filter(`BU` == "3.Meat Sales") %>% 
  filter(`Customer Group` == "Meat Purchase")

meat_sales_external_500031_10001814_new <- meat_sales_external_500031_10001814 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 500031, `Cc Key` == 10001814),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Packaging and Pallet expense account for 3. Meat Sales

### 3. Meat Sales Packaging Account (650311-10001814)

```{r}
# Expense account for packaging from Value Add product
meat_sales_packaging_650311_10001814 <- customer_data %>% 
  filter(`BU` == "3.Meat Sales") 

meat_sales_packaging_650311_10001814_new <- meat_sales_packaging_650311_10001814 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650311, `Cc Key` == 10001814),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 3. Meat Sales Pallet Account (650303-10001814)

```{r}
# Expense account for packaging from Value Add product
meat_sales_pallet_650303_10001814 <- customer_data %>% 
  filter(`BU` == "3.Meat Sales") 

meat_sales_pallet_650303_10001814_new <- meat_sales_pallet_650303_10001814 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650303, `Cc Key` == 10001814),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Packaging and Pallet expense account for 2.Meat Processing

### 2.Meat Processing Edible Offal packaging account (650301-10001816)

```{r}
# Expense account for packaging from Edible Offal in Corowa
offal_corowa_packaging_650301_10001816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Customer Group` == "Edible Offal")

offal_corowa_packaging_650301_10001816_new <- offal_corowa_packaging_650301_10001816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650301, `Cc Key` == 10001816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 2.Meat Processing Edible Offal Pallet account (650303-10001816)

```{r}
# Expense account for pallet from Edible Offal in Corowa
offal_corowa_pallet_650303_10001816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Customer Group` == "Edible Offal")

offal_corowa_pallet_650303_10001816_new <- offal_corowa_pallet_650303_10001816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650303, `Cc Key` == 10001816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 2.Meat Processing 6 Way packaging account (650301-10501816)

```{r}
# Packaging Expense account for corowa 6way frozen products
corowa_6way_packaging_frz_650301_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "6 Way") %>% 
  filter(`Sales Type` == "FRZ")

corowa_6way_packaging_frz_650301_10501816_new <- corowa_6way_packaging_frz_650301_10501816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650301, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 2.Meat Processing 6 Way pallet account (650303-10501816)

```{r}
# Pallet Expense account for corowa 6way frozen products
corowa_6way_pallet_frz_650303_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "6 Way") %>% 
  filter(`Sales Type` == "FRZ")

corowa_6way_pallet_frz_650303_10501816_new <- corowa_6way_pallet_frz_650303_10501816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650303, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 2.Meat Processing Commodity packaging account (650301-10501816)

```{r}
# Packaging Expense account for corowa 6way frozen products
corowa_commodity_packaging_frz_650301_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Commodity") %>% 
  filter(`Sales Type` == "FRZ")

corowa_commodity_packaging_frz_650301_10501816_new <- corowa_commodity_packaging_frz_650301_10501816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650301, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 2.Meat Processing Commodity pallet account (650303-10501816)

```{r}
# Pallet Expense account for corowa 6way frozen products
corowa_commodity_pallet_frz_650303_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Commodity") %>% 
  filter(`Sales Type` == "FRZ")

corowa_commodity_pallet_frz_650303_10501816_new <- corowa_commodity_pallet_frz_650303_10501816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650303, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Packaging and margin expense account for 2.Meat Processing (Special Contracts)

### 2.Meat Processing Woolworth packaging account (650301-11901816)

```{r}
# Packaging Expense account for corowa woolworth customer (special price apply)
corowa_ww_packaging_650301_11901816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Tab` == "Bone") %>% 
  filter(`Floor` == "Bone") %>% 
  filter(`Customer Group` == "Woolworths") 

corowa_ww_packaging_650301_11901816_new <- corowa_ww_packaging_650301_11901816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650301, `Cc Key` == 11901816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 2.Meat Processing Woolworth packaging margin account (650311-11901816)

```{r}
# Pallet Expense account for corowa woolworth customer (special price apply)
corowa_ww_packaging_margin_650311_11901816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Tab` == "Bone") %>% 
  filter(`Floor` == "Bone") %>% 
  filter(`Customer Group` == "Woolworths") 

corowa_ww_packaging_margin_650311_11901816_new <- corowa_ww_packaging_margin_650311_11901816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650311, `Cc Key` == 11901816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 2.Meat Processing DRJ packaging account (650301-11901816)

```{r}
# Packaging Expense account for corowa DRJ customer (special price apply)
corowa_DRJ_packaging_650301_11901816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Tab` == "Bone") %>% 
  filter(`Floor` == "Bone") %>% 
  filter(`Customer Group` == "DRJ") 

corowa_DRJ_packaging_650301_11901816_new <- corowa_DRJ_packaging_650301_11901816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650301, `Cc Key` == 11901816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 2.Meat Processing DRJ packaging and margin account (650311-11901816)

```{r}
# Pallet Expense account for corowa DRJ customer (special price apply)
corowa_DRJ_packaging_margin_650311_11901816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Tab` == "Bone") %>% 
  filter(`Floor` == "Bone") %>% 
  filter(`Customer Group` == "DRJ") 

corowa_DRJ_packaging_margin_650311_11901816_new <- corowa_DRJ_packaging_margin_650311_11901816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650311, `Cc Key` == 11901816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Packaging and Pallet expense account for 6.Laverton Processing

### 6.Laverton Processing Edible Offal Packaging Account (650301-10001854)

```{r}
# Expense account for packaging from Edible Offal in Laverton
offal_laverton_packaging_650301_10001854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Customer Group` == "Edible Offal")

offal_laverton_packaging_650301_10001854_new <- offal_laverton_packaging_650301_10001854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650301, `Cc Key` == 10001854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 6.Laverton Processing Edible Offal Pallet Account (650303-10001854)

```{r}
# Expense account for pallet from Edible Offal in Laverton
offal_laverton_pallet_650303_10001854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Customer Group` == "Edible Offal")

offal_laverton_pallet_650303_10001854_new <- offal_laverton_pallet_650303_10001854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650303, `Cc Key` == 10001854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 6.Laverton Processing 6 Way Packaging Account (650301-10501854)

```{r}
# Packaging Expense account for laverton 6way frozen products
laverton_6way_packaging_frz_650301_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "6 Way") %>% 
  filter(`Sales Type` == "FRZ")

laverton_6way_packaging_frz_650301_10501854_new <- laverton_6way_packaging_frz_650301_10501854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650301, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 6.Laverton Processing 6 Way Pallet Account (650303-10501854)

```{r}
# Pallet Expense account for laverton 6way frozen products
laverton_6way_pallet_frz_650303_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "6 Way") %>% 
  filter(`Sales Type` == "FRZ")

laverton_6way_pallet_frz_650303_10501854_new <- laverton_6way_pallet_frz_650303_10501854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650303, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 6.Laverton Processing Commodity Packaging Account (650301-10501854)

```{r}
# Packaging Expense account for laverton commodity frozen products
laverton_commodity_packaging_frz_650301_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Commodity") %>% 
  filter(`Sales Type` == "FRZ")

laverton_commodity_packaging_frz_650301_10501854_new <- laverton_commodity_packaging_frz_650301_10501854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650301, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 6.Laverton Processing Commodity Pallet Account (650303-10501854)

```{r}
# Pallet Expense account for laverton commodity frozen products
laverton_commodity_pallet_frz_650303_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Commodity") %>% 
  filter(`Sales Type` == "FRZ")

laverton_commodity_pallet_frz_650303_10501854_new <- laverton_commodity_pallet_frz_650303_10501854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650303, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 6.Laverton Processing Sow Packaging Account (650301-10501854)

```{r}
# Packaging Expense account for laverton sow frozen products
laverton_sow_packaging_frz_650301_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Sow") %>% 
  filter(`Sales Type` == "FRZ")

laverton_sow_packaging_frz_650301_10501854_new <- laverton_sow_packaging_frz_650301_10501854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650301, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 6.Laverton Processing Sow Pallet Account (650303-10501854)

```{r}
# Pallet Expense account for laverton sow frozen products
laverton_sow_pallet_frz_650303_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Sow") %>% 
  filter(`Sales Type` == "FRZ")

laverton_sow_pallet_frz_650303_10501854_new <- laverton_sow_pallet_frz_650303_10501854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650303, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 6.Laverton Processing Export Pallet Account (650301-10201854)

```{r}
# Packaging Expense account for Laverton export to Singapore and Malaysia
laverton_export_packaging_650301_10201854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Export Carcass") %>% 
  filter(`Customer Group` == "Export") 

laverton_export_packaging_650301_10201854_new <- laverton_export_packaging_650301_10201854 %>%
  select(-any_of("Floor")) %>%
  mutate(`Customer name` = paste(`Customer name`, `Customer Group`)) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 650301, `Cc Key` == 10201854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Trade Allowance Expense Account

### 3. Meat Sales (450050-10001814)

```{r}
# Trade Allowance 
trade_allowance_meat_sales_450050_10001814 <- customer_data %>% 
  filter(`BU` == "3.Meat Sales") %>% 
  filter(Tab == "VA") 

trade_allowance_meat_sales_450050_10001814_new <- trade_allowance_meat_sales_450050_10001814 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% 
      filter(`GL Account` == 450050, `Cc Key` == 10001814) %>%
      mutate(BU = "3.Meat Sales"),
    by = c("BU" = "BU")
  ) %>% 
  crossing(Period = 1:12)
```

### 6. Laverton Processing (450050-10201854)

```{r}
laverton_trade_allowance_450050_10201854 <- customer_data %>%
  filter(`BU` == "6.Laverton Processing") %>%
  filter(Tab == "Kill") %>%
  filter(Floor == "Kill") %>% 
  filter(`Customer name` %in% c("BE Campbells Bacon", "B.E. Campbell"))
  
laverton_trade_allowance_450050_10201854_new <- laverton_trade_allowance_450050_10201854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 450050, `Cc Key` == 10201854) %>%
    mutate(BU = "6.Laverton Processing"),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

## Storage Expense Account

### Corowa Offal Storage Cost (730010-10001816)

```{r}
# Storage Cost Expense Account
edible_offal_storage_730010_10001816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(Tab == "Kill") %>% 
  filter(`Floor` == "Kill") %>% 
  filter(`Customer Group` == "Edible Offal")

edible_offal_storage_730010_10001816_new <- edible_offal_storage_730010_10001816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 730010, `Cc Key` == 10001816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Corowa Commodity Storage Cost (730010-10501816)

```{r}
# Storage Cost 
corowa_commodity_frz_storage_7300100_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Commodity") %>% 
  filter(`Sales Type` == "FRZ")

corowa_commodity_frz_storage_7300100_10501816_new <- corowa_commodity_frz_storage_7300100_10501816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 730010, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Corowa 6 Way Storage Cost (730010-10501816)

```{r}
# Storage cost — external customers for corowa 6way frozen products
corowa_6way_frz_storage_730010_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "6 Way") %>% 
  filter(`Sales Type` == "FRZ")

corowa_6way_frz_storage_730010_10501816_new <- corowa_6way_frz_storage_730010_10501816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 730010, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Corowa Meat Trade Storage Cost (730010-10501816)

```{r}
# Storage cost for this special type of data transfering from Laverton 6Way, Commodity and Edible Offal in Intercompany Sales to Corowa and count as Meat Trade product
meat_trade_storage_data <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Floor` == "Meat Trade") %>% 
  filter(`Service` %in% c("6 Way", "Commodity", "Edible Offal"))

meat_trade_storage_data_new <- meat_trade_storage_data %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 730010, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Corowa Stock On Hand Cost (730010-10501816)

```{r}
corowa_stock_on_hand_730010_10501816 <- customer_data %>% 
  filter(`BU` == "2.Meat Processing") %>% 
  filter(`Customer name` == "Corowa Stock On Hand")

corowa_stock_on_hand_730010_10501816_new <- corowa_stock_on_hand_730010_10501816 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 730010, `Cc Key` == 10501816),
    by = c("BU" = "BU")
  ) 
```

### Laverton Sow Storage Cost (730010-10501854)

```{r}
# Storage Cost — external customers for corowa 6way frozen products - Only Laverton has Sow account
laverton_sow_frz_storage_730010_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Floor` == "Boxed Meat") %>% 
  filter(`Customer Group` == "Sow") %>% 
  filter(`Sales Type` == "FRZ")

laverton_sow_frz_storage_730010_10501854_new <- laverton_sow_frz_storage_730010_10501854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 730010, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Laverton Stock On Hand Cost (730010-10501854)

```{r}
laverton_stock_on_hand_730010_10501854 <- customer_data %>% 
  filter(`BU` == "6.Laverton Processing") %>% 
  filter(`Customer name` == "Laverton Stock On Hand")

laverton_stock_on_hand_730010_10501854_new <- laverton_stock_on_hand_730010_10501854 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 730010, `Cc Key` == 10501854),
    by = c("BU" = "BU")
  ) 
```

### Value Add Storage Cost (730010-10001814)

```{r}
# Storage Cost — external customers, no intercompany filtering needed for this BU
meat_sales_storage_730010_10001814 <- customer_data %>% 
  filter(`BU` == "3.Meat Sales") %>% 
  filter(Tab == "VA") 

meat_sales_storage_730010_10001814_new <- meat_sales_storage_730010_10001814 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 730010, `Cc Key` == 10001814),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### Value Add Stock On Hand Cost (730010-10001814)

```{r}
value_add_stock_on_hand_730010_10001814 <- customer_data %>% 
  filter(`BU` == "3.Meat Sales") %>% 
  filter(`Customer name` == "Value Add Stock On Hand")

value_add_stock_on_hand_730010_10001814_new <- value_add_stock_on_hand_730010_10001814 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 730010, `Cc Key` == 10001814),
    by = c("BU" = "BU")
  ) 
```

## Freight Out Expense Account

### Come from VA (500192-10001814)

```{r}
# Storage Cost — external customers, no intercompany filtering needed for this BU
freight_out_500192_10001814 <- customer_data %>%
  filter(`BU` == "3.Meat Sales") %>%
  filter(Tab == "VA") 

freight_out_500192_10001814_new <- freight_out_500192_10001814 %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 500192, `Cc Key` == 10001814),
    by = c("BU" = "BU")
  ) %>% 
  # Add Month columns for future use
  crossing(Period = 1:12)
```

### 

# Processing Data for Expense Account

## V&V Data

### Process Farm Sell and Buy Back from V&V Data

```{r}
external_VA_price_calculated <- volume_va_raw %>%
  filter(`Vendor Type` == "External") %>%
  filter(`Service` == "Procurement") %>%
  mutate(
    Unicode        = toupper(str_trim(Unicode)),
    Month          = toupper(Month),
    Abattoir       = toupper(Abattoir),
    `Total Weight` = as.numeric(`Total Weight`),
    Period         = match(Month, toupper(month.name))
  ) %>%
  left_join(
    carcass_price_data %>%
      filter(`Customer name` == "Other Transactions") %>%
      pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Carcass Price") %>%
      mutate(Period = as.integer(Period)) %>%
      select(Period, `Carcass Price`),
    by = "Period"
  ) %>%
  mutate(Value = `Total Weight` * `Carcass Price`) %>%
  group_by(Month, Period) %>%
  summarise(
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Tab = "1.Farming Operations")
```

### Join Farm Sell and Buy Back from V&V Data with account

```{r}
# Convert Gross Sales - Other variables into negative according to account adjustment
farm_sales_400350_10001812_calculated <- farm_sales_400350_10001812_new %>%
  left_join(
    external_VA_price_calculated ,
    by = c("BU" = "Tab","Period")
  ) %>%
  mutate(Value = -Value)

# This one reflect the cost of sales for farm and positive value in opposite to Gross Sales - Other
farm_costs_510157_10001812_calculated <- farm_costs_510157_10001812_new %>%
  left_join(
    external_VA_price_calculated ,
    by = c("BU" = "Tab","Period")
  )
```

### Join gross sales and cost of sales data

```{r}
all_expense_new_team_calculated <- bind_rows(farm_sales_400350_10001812_calculated, farm_costs_510157_10001812_calculated)
```

## Corowa and Laverton Farm expense

### Buying pig, killing pig and boning them from Farm

```{r}
# Prepare separated data for Corowa and Laverton so it is easier to debug in the future
corowa_laverton_transactions <- volume_farm_raw %>%
      filter(!(`Int/Ext` %in% "External" ))

# Calculate pig fee by buying from farm
# Start from transactions to preserve real customer names (one row per customer per period)
corowa_farm_510167_10501816_buy_calculated <- corowa_laverton_transactions %>%
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(toupper(Unicode) %in% c("FCOROWA6WAY", "COROWA6WAY", "FCOROWACOMMODITY", "COROWACOMMODITY")) %>%
  mutate(
    Unicode        = toupper(Unicode),
    Abattoir       = toupper(Abattoir),
    Month          = toupper(Month),
    Units          = as.numeric(Units),
    `Avg Weight`   = as.numeric(`Avg Weight`),
    `Total Weight` = as.numeric(`Total Weight`),
    Period         = match(Month, toupper(month.name))
  ) %>%
  left_join(
    carcass_price_data %>%
      mutate(`Farm Unicode` = toupper(str_trim(`Farm Unicode`)), Abattoir = toupper(Abbatoir)) %>%
      pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Carcass Price") %>%
      mutate(Period = as.integer(Period)) %>%
      select(`Farm Unicode`, Abattoir, Period, `Carcass Price`),
    by = c("Unicode" = "Farm Unicode", "Abattoir", "Period")
  ) %>%
  mutate(Value = `Total Weight` * `Carcass Price`) %>%
  group_by(`Customer name`, Month, Period) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  left_join(
    corowa_farm_510167_10501816 %>% select(`Customer name`, `SOP Unicode`, `Customer Group`, Tab),
    by = "Customer name"
  ) %>%
  mutate(BU = "2.Meat Processing") %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 510167, `Cc Key` == 10501816),
    by = "BU"
  ) %>% 
  mutate(Tab = "Farm")

# Calculated Kill fee for the pig from farm
corowa_farm_510167_10501816_kill_calculated <- corowa_laverton_transactions %>%
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(toupper(Tab) == "KILL") %>%
  filter(toupper(Unicode) %in% c("FCOROWA6WAY", "COROWA6WAY", "FCOROWACOMMODITY", "COROWACOMMODITY")) %>%
  mutate(
    Unicode        = toupper(Unicode),
    Abattoir       = toupper(Abattoir),
    Month          = toupper(Month),
    Units          = as.numeric(Units),
    `Avg Weight`   = as.numeric(`Avg Weight`),
    `Total Weight` = as.numeric(`Total Weight`),
    Period         = match(Month, toupper(month.name))
  ) %>%
  left_join(
    kill_fee_data %>%
      mutate(`SOP Unicode` = toupper(str_trim(`SOP Unicode`)), Abattoir = toupper(Abbatoir)) %>%
      filter(`SOP Unicode` %in% c("COROWACOMMODITY", "COROWA6WAY")) %>%
      pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Fee") %>%
      mutate(Period = as.integer(Period)) %>%
      group_by(Abattoir, Period) %>%
      summarise(Fee = mean(Fee, na.rm = TRUE), .groups = "drop"),
    by = c("Abattoir", "Period")
  ) %>%
  mutate(Value = Units * Fee) %>%
  group_by(`Customer name`, Month, Period) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Fee            = mean(Fee, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  left_join(
    corowa_farm_510167_10501816 %>% select(`Customer name`, `SOP Unicode`, `Customer Group`, Tab),
    by = "Customer name"
  ) %>%
  mutate(BU = "2.Meat Processing") %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 510167, `Cc Key` == 10501816),
    by = "BU"
  ) %>% 
  mutate(Tab = "Kill")

# Calculated Bone fee for the pig from farm
corowa_farm_510167_10501816_bone_calculated <- corowa_laverton_transactions %>%
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(toupper(Tab) == "BONE") %>%
  filter(toupper(Unicode) %in% c("FCOROWA6WAY", "COROWA6WAY", "FCOROWACOMMODITY", "COROWACOMMODITY")) %>%
  mutate(
    Unicode        = toupper(Unicode),
    Abattoir       = toupper(Abattoir),
    Month          = toupper(Month),
    Units          = as.numeric(Units),
    `Avg Weight`   = as.numeric(`Avg Weight`),
    `Total Weight` = as.numeric(`Total Weight`),
    Period         = match(Month, toupper(month.name))
  ) %>%
  left_join(
    bone_fee_data %>%
      mutate(`SOP Unicode` = toupper(str_trim(`SOP Unicode`)), Abattoir = toupper(Abbatoir)) %>%
      filter(`SOP Unicode` %in% c("COROWACOMMODITY", "COROWA6WAY")) %>%
      pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Fee") %>%
      mutate(Period = as.integer(Period)) %>%
      group_by(Abattoir, Period) %>%
      summarise(Fee = mean(Fee, na.rm = TRUE), .groups = "drop"),
    by = c("Abattoir", "Period")
  ) %>%
  mutate(Value = Units * Fee) %>%
  group_by(`Customer name`, Month, Period) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Fee            = mean(Fee, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  left_join(
    corowa_farm_510167_10501816 %>% select(`Customer name`, `SOP Unicode`, `Customer Group`, Tab),
    by = "Customer name"
  ) %>%
  mutate(BU = "2.Meat Processing") %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 510167, `Cc Key` == 10501816),
    by = "BU"
  ) %>%
  mutate(Tab = "Bone")
```

### Buying pig, killing pig and boning them from Farm

```{r}
# Expense for Laverton
# Start from transactions to preserve real customer names (one row per customer per period)
laverton_farm_510167_10501854_calculated <- corowa_laverton_transactions %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(toupper(Unicode) %in% c("FLAVERTON6WAY", "LAVERTON6WAY", "LAVERTONCOMMODITY", "FLAVERTONCOMMODITY", "FLAVERTONSOW COMMODITY", "FLAVERTONOTHERS(SOW)", "FLAVERTONPW OPPORTUNITY - SOW")) %>%
  mutate(
    Unicode        = toupper(Unicode),
    Abattoir       = toupper(Abattoir),
    Month          = toupper(Month),
    Units          = as.numeric(Units),
    `Avg Weight`   = as.numeric(`Avg Weight`),
    `Total Weight` = as.numeric(`Total Weight`),
    Period         = match(Month, toupper(month.name))
  ) %>%
  left_join(
    carcass_price_data %>%
      mutate(`Farm Unicode` = toupper(str_trim(`Farm Unicode`)), Abattoir = toupper(Abbatoir)) %>%
      pivot_longer(cols = matches("^\\d+$"), names_to = "Period", values_to = "Carcass Price") %>%
      mutate(Period = as.integer(Period)) %>%
      select(`Farm Unicode`, Abattoir, Period, `Carcass Price`),
    by = c("Unicode" = "Farm Unicode", "Abattoir", "Period")
  ) %>%
  mutate(Value = `Total Weight` * `Carcass Price`) %>%
  group_by(`Customer name`, Month, Period) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  left_join(
    laverton_farm_510167_10501854 %>% select(`Customer name`, `SOP Unicode`, `Customer Group`, Tab),
    by = "Customer name"
  ) %>%
  mutate(BU = "6.Laverton Processing") %>%
  select(-any_of("Floor")) %>%
  left_join(
    gl_cc_data %>% filter(`GL Account` == 510167, `Cc Key` == 10501854),
    by = "BU"
  )
```

### Join Expense Account buying from Farm for both Corowa and Laverton

```{r}
all_expense_corowa_laverton_expense_farm <- bind_rows(corowa_farm_510167_10501816_buy_calculated,
corowa_farm_510167_10501816_kill_calculated,
corowa_farm_510167_10501816_bone_calculated,            laverton_farm_510167_10501854_calculated) %>%
  mutate(Value = -Value)
```

## Meat Sale Expense

### Transferring meat from Laverton include edible offal, 6way and commodity frozen

```{r}
# Volume for intercompany meat trade from Laverton to Corowa
volume_meat_trade_laverton_intercompany <- bind_rows(
  volume_offal_laverton %>% filter(`Customer Group` == "Edible Offal"),
  volume_6way_sow_laverton %>% filter(`Customer Group` == "6 Way"),
  volume_commodity_laverton_frz
) %>%
  mutate(Period = match(Month, toupper(month.name))) %>%
  select(-Tab, -Abattoir, -`Customer name`)

all_expense_meat_trade_laverton_corowa_calculated <- meat_trade_510167_10501816_new %>%
  left_join(
    volume_meat_trade_laverton_intercompany,
    by = c("Period", "Service" = "Customer Group")
  ) %>%
  mutate(Value = -Value)
```

### Buying meat from Internal and External Vendor with Procurement Service

```{r}
# Standardise the data
meat_sales_internal_510167_10001814_new_std <- meat_sales_internal_510167_10001814_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

# Standardise the data
meat_sales_external_500031_10001814_new_std <- meat_sales_external_500031_10001814_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

# Prepare data for expense of meat sales
volume_expense_VA_calculated <- volume_va_raw %>%
  filter(`Service` == "Procurement") %>%
  mutate(
    Tab            = toupper(Tab),
    Abattoir       = toupper(Abattoir),
    Month          = toupper(Month),
    Units          = as.numeric(Units),
    `Avg Weight`   = as.numeric(`Avg Weight`),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code`    = str_trim(`Item Code`),
    Period         = match(Month, toupper(month.name))
  ) %>%
  left_join(
    item_price_data,
    by = c("Item Code" = "Item Key")
  ) %>%
  mutate(Value = `Total Weight` * `Current Price`) %>%
  group_by(Tab, Abattoir, Month, Period, `Vendor Type`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  )

# Internal vendor → 510167-10001814
meat_sales_internal_510167_10001814_calculated <- meat_sales_internal_510167_10001814_new_std %>%
  select(-any_of("Abattoir")) %>%
  left_join(
    volume_expense_VA_calculated %>% filter(`Vendor Type` == "Internal"),
    by = c("BU" = "Tab", "Period", "Month")
  ) %>%
  mutate(Value = -Value)

# External vendor → 500031-10001814
meat_sales_external_500031_10001814_calculated <- meat_sales_external_500031_10001814_new_std %>%
  select(-any_of("Abattoir")) %>%
  left_join(
    volume_expense_VA_calculated %>% filter(`Vendor Type` == "External"),
    by = c("BU" = "Tab", "Period", "Month")
  ) %>%
  mutate(Value = -Value)

# Join both Internal and External Expense for Meat Sales
all_expense_meat_sales_internal_external_calculated <- bind_rows(
  meat_sales_internal_510167_10001814_calculated %>% select(-any_of("Vendor Type")),
  meat_sales_external_500031_10001814_calculated %>% select(-any_of("Vendor Type"))
)
```

### Packaging and Pallet for value added

```{r}
# Standardise the data
meat_sales_packaging_650311_10001814_new_std <- meat_sales_packaging_650311_10001814_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) %>% 
  mutate(Abattoir = "VALUE ADD")

# Standardise the data
meat_sales_pallet_650303_10001814_new_std <- meat_sales_pallet_650303_10001814_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) %>% 
  mutate(Abattoir = "VALUE ADD")

# Prepare data for expense of meat sales
volume_expense_VA_sales_calculated <- volume_va_raw %>%
  filter(`Service` == "VA Sales") %>%
  mutate(
    Tab            = toupper(Tab),
    Abattoir       = toupper(Abattoir),
    Month          = toupper(Month),
    Units          = as.numeric(Units),
    `Avg Weight`   = as.numeric(`Avg Weight`),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code`    = str_trim(`Item Code`),
    Period         = match(Month, toupper(month.name))
  ) %>%
  left_join(
    VA_brand_data %>% select(`Item Code`, Brand),
    by = "Item Code"
  ) %>%
  mutate(
    `Customer name` = if_else(!is.na(Brand), Brand, `Customer name`)
  ) %>%
  select(-Brand) 

# Calculate the packaging cost 
volume_expense_VA_sales_packaging_calculated <- volume_expense_VA_sales_calculated %>%
  select(-Price) %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 2) %>%
      select(BOM, PACKAGING) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  rename(Price = PACKAGING) %>%
  mutate(Value = `Total Weight` * Price)

# Calculate the pallet cost 
volume_expense_VA_sales_pallet_calculated <- volume_expense_VA_sales_calculated %>%
  select(-Price) %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 2) %>%
      select(BOM, PALLETS) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  rename(Price = PALLETS) %>%
  mutate(Value = `Total Weight` * Price)

# Join the calculated value with the account to create the final data
meat_sales_packaging_650311_10001814_calculated <- meat_sales_packaging_650311_10001814_new_std %>%
  left_join(
    volume_expense_VA_sales_packaging_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer name`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer name")
  ) %>%
  mutate(Value = -Value)

# Join the calculated value with the account to create the final data
meat_sales_pallet_650303_10001814_calculated <- meat_sales_pallet_650303_10001814_new_std %>%
  left_join(
    volume_expense_VA_sales_pallet_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer name`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer name")
  ) %>%
  mutate(Value = -Value)

all_expense_packaging_pallet_meat_sales_calculated <- bind_rows(meat_sales_packaging_650311_10001814_calculated, meat_sales_pallet_650303_10001814_calculated)
```

## Corowa Packaging and Pallet for Kill and Bone

### Edible Offal

#### Special function design to add price to those item without the price using other variant

```{r}
# Look for variant = 4 for item without price for variant = 3
join_packaging_price <- function(volume_data, price_col, variant = 3) {
  volume_data %>%
    select(-Price) %>%
    left_join(
      packaging_price_data %>%
        filter(VARIANT == variant) %>%
        select(BOM, !!sym(price_col)) %>%
        mutate(BOM = as.character(BOM)),
      by = c("Item Code" = "BOM")
    ) %>%
    rename(Price = !!sym(price_col)) %>%
    left_join(
      packaging_price_data %>%
        filter(VARIANT == 4) %>%
        select(BOM, !!sym(price_col)) %>%
        mutate(BOM = as.character(BOM)) %>%
        rename(Price_fallback = !!sym(price_col)),
      by = c("Item Code" = "BOM")
    ) %>%
    mutate(
      Price = if_else(`Total Weight` > 0 & (is.na(Price) | Price == 0), Price_fallback, Price)
    ) %>%
    select(-Price_fallback) %>%
    mutate(Value = `Total Weight` * Price)
}
```

#### Data Processing

```{r}
# Standardise the data
offal_corowa_packaging_650301_10001816_new_std <- offal_corowa_packaging_650301_10001816_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

# Standardise the data
offal_corowa_pallet_650303_10001816_new_std <- offal_corowa_pallet_650303_10001816_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

# Prepare the edible offal volume data
corowa_edible_offal_volume_data <- volume_bone_raw %>% 
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(Type %in% c("OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    Period         = match(Month, toupper(month.name)),
    `Customer Group`  = case_when(
      Type == "OFFALS"      ~ "Edible Offal",
      Type == "BACON CUTS"  ~ "Edible Offal",
      TRUE ~ NA_character_
    )
  ) 


# Apply the function to add missing price using other variants
corowa_edible_offal_volume_packaging_calculated <- join_packaging_price(corowa_edible_offal_volume_data, "PACKAGING", variant = 3)
corowa_edible_offal_volume_pallet_calculated    <- join_packaging_price(corowa_edible_offal_volume_data, "PALLETS",   variant = 3)

# Join the calculated value with the account to create the final data
offal_corowa_packaging_650301_10001816_calculated <- offal_corowa_packaging_650301_10001816_new_std %>%
  left_join(
    corowa_edible_offal_volume_packaging_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

# Join the calculated value with the account to create the final data
offal_corowa_pallet_650303_10001816_calculated <- offal_corowa_pallet_650303_10001816_new_std %>%
  left_join(
    corowa_edible_offal_volume_pallet_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

all_expense_packaging_pallet_edible_offal_corowa_calculated <- bind_rows(offal_corowa_packaging_650301_10001816_calculated, offal_corowa_pallet_650303_10001816_calculated)
```

### 6Way

```{r}
# Standardise the data
corowa_6way_packaging_frz_650301_10501816_new_std <- corowa_6way_packaging_frz_650301_10501816_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

corowa_6way_pallet_frz_650303_10501816_new_std <- corowa_6way_pallet_frz_650303_10501816_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

corowa_volume_6way_data <- volume_bone_raw %>%
  mutate(
    Tab         = toupper(Tab),
    Abattoir    = toupper(Abattoir),
    Month       = toupper(Month),
    Units       = as.numeric(Units),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code` = str_trim(`Item Code`)
  ) %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(toupper(Run) == "6 WAY") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = "6 Way",
    Period         = match(Month, toupper(month.name))
    ) 

# Add the price and calculating the value for 6way packaging
corowa_volume_6way_packaging_calculated <- corowa_volume_6way_data %>%
  select(-Price) %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PACKAGING) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  rename(Price = PACKAGING) %>%
  mutate(Value = `Total Weight` * Price)

# Add the price and calculating the value for 6way pallet
corowa_volume_6way_pallet_calculated <- corowa_volume_6way_data %>%
  select(-Price) %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PALLETS) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  rename(Price = PALLETS) %>%
  mutate(Value = `Total Weight` * Price)

# Join the calculated value with the account to create the final data
corowa_6way_packaging_frz_650301_10501816_calculated <- corowa_6way_packaging_frz_650301_10501816_new_std %>%
  left_join(
    corowa_volume_6way_packaging_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

# Join the calculated value with the account to create the final data
corowa_6way_pallet_frz_650303_10501816_calculated <- corowa_6way_pallet_frz_650303_10501816_new_std %>%
  left_join(
    corowa_volume_6way_pallet_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

all_expense_packaging_pallet_6way_corowa_calculated <- bind_rows(corowa_6way_packaging_frz_650301_10501816_calculated, corowa_6way_pallet_frz_650303_10501816_calculated)
```

### Commodity

```{r}
# Standardise the data
corowa_commodity_packaging_frz_650301_10501816_new_std <- corowa_commodity_packaging_frz_650301_10501816_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

corowa_commodity_pallet_frz_650303_10501816_new_std <- corowa_commodity_pallet_frz_650303_10501816_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

# Reuse value from commodity data external sales for corowa since we already did this calculation before
volume_commodity_corowa_packaging_pallet <- volume_commodity_corowa_400000 %>% 
  mutate(Period         = match(Month, toupper(month.name)))

# Add the price and calculating the value for commodity packaging
corowa_volume_commodity_packaging_calculated <- volume_commodity_corowa_packaging_pallet %>%
  select(-Price) %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PACKAGING) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  rename(Price = PACKAGING) %>%
  mutate(Value = `Total Weight` * Price)

# Add the price and calculating the value for commodity pallet
corowa_volume_commodity_pallet_calculated <- volume_commodity_corowa_packaging_pallet %>%
  select(-Price) %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PALLETS) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  rename(Price = PALLETS) %>%
  mutate(Value = `Total Weight` * Price)

# Join the calculated value with the account to create the final data
corowa_commodity_packaging_frz_650301_10501816_calculated <- corowa_commodity_packaging_frz_650301_10501816_new_std %>%
  left_join(
    corowa_volume_commodity_packaging_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

# Join the calculated value with the account to create the final data
corowa_commodity_pallet_frz_650303_10501816_calculated <- corowa_commodity_pallet_frz_650303_10501816_new_std %>%
  left_join(
    corowa_volume_commodity_pallet_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

all_expense_packaging_pallet_commodity_corowa_calculated <- bind_rows(corowa_commodity_packaging_frz_650301_10501816_calculated, corowa_commodity_pallet_frz_650303_10501816_calculated)
```

## Corowa expense margin special

```{r}
# Percentage Parameter
hot_to_cold_parameter <- 90.9
cold_to_meat_parameter <- 88
# Packaging fee
ww_packaging_fee <- 0.137
DRJ_packaging_fee <- 0.15
# Margin percentage
ww_margin <- 45.26
DRJ_margin <- 10
# Margin Fee
ww_packaging_margin_fee <-  ww_packaging_fee*(1+(ww_margin/100))
DRJ_packaging_margin_fee <- DRJ_packaging_fee*(1+(DRJ_margin/100))
```

### Woolworth (special contract)

```{r}
# Standardise the data
corowa_ww_packaging_650301_11901816_new_std <- corowa_ww_packaging_650301_11901816_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

corowa_ww_packaging_margin_650311_11901816_new_std <- corowa_ww_packaging_margin_650311_11901816_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

# Prepare the data
corowa_volume_ww_data <- volume_farm_raw %>%
  mutate(
    Tab         = toupper(Tab),
    Abattoir    = toupper(Abattoir),
    Month       = toupper(Month),
    Units       = as.numeric(Units),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code` = str_trim(`Item Code`)
  ) %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Tab) == "BONE") %>% 
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(toupper(`Customer name`) == "WOOLWORTHS") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = "2.Meat Processing",
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = "Woolworths",
    Period         = match(Month, toupper(month.name))
    )

# Calculate the data using special parameter and its own logic
corowa_volume_ww_data_packaging_calculated <- corowa_volume_ww_data %>%
  group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
  summarise(
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Value = `Total Weight` * ww_packaging_fee * (hot_to_cold_parameter / 100) * (cold_to_meat_parameter / 100))

corowa_volume_ww_data_packaging_margin_calculated <- corowa_volume_ww_data %>%
  group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
  summarise(
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Value = `Total Weight` * ww_packaging_margin_fee * (hot_to_cold_parameter / 100) * (cold_to_meat_parameter / 100))

# Join the calculated value with the account to create the final data
corowa_ww_packaging_650301_11901816_calculated <- corowa_ww_packaging_650301_11901816_new_std %>%
  left_join(
    corowa_volume_ww_data_packaging_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) 

# Join the calculated value with the account to create the final data
corowa_ww_packaging_margin_650311_11901816_calculated <- corowa_ww_packaging_margin_650311_11901816_new_std %>%
  left_join(
    corowa_volume_ww_data_packaging_margin_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

all_expense_packaging_margin_woolworth_corowa_calculated <- bind_rows(corowa_ww_packaging_650301_11901816_calculated, corowa_ww_packaging_margin_650311_11901816_calculated)
```

### DRJ (special contract)

```{r}
# Standardise the data
corowa_DRJ_packaging_650301_11901816_new_std <- corowa_DRJ_packaging_650301_11901816_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

corowa_DRJ_packaging_margin_650311_11901816_new_std <- corowa_DRJ_packaging_margin_650311_11901816_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

# Prepare the data
corowa_volume_DRJ_data <- volume_farm_raw %>%
  mutate(
    Tab         = toupper(Tab),
    Abattoir    = toupper(Abattoir),
    Month       = toupper(Month),
    Units       = as.numeric(Units),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code` = str_trim(`Item Code`)
  ) %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Tab) == "BONE") %>% 
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(toupper(`Customer name`) == "DR JOHNSTON") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = "2.Meat Processing",
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = "DRJ",
    Period         = match(Month, toupper(month.name))
    )

# Calculate the data using special parameter and its own logic
corowa_volume_DRJ_data_packaging_calculated <- corowa_volume_DRJ_data %>%
  group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
  summarise(
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Value = `Total Weight` * DRJ_packaging_fee * (hot_to_cold_parameter / 100) * (cold_to_meat_parameter / 100))

corowa_volume_DRJ_data_packaging_margin_calculated <- corowa_volume_DRJ_data %>%
  group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
  summarise(
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Value = `Total Weight` * DRJ_packaging_margin_fee * (hot_to_cold_parameter / 100) * (cold_to_meat_parameter / 100))

# Join the calculated value with the account to create the final data
corowa_DRJ_packaging_650301_11901816_calculated <- corowa_DRJ_packaging_650301_11901816_new_std %>%
  left_join(
    corowa_volume_DRJ_data_packaging_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  )

# Join the calculated value with the account to create the final data
corowa_DRJ_packaging_margin_650311_11901816_calculated <- corowa_DRJ_packaging_margin_650311_11901816_new_std %>%
  left_join(
    corowa_volume_DRJ_data_packaging_margin_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

all_expense_packaging_margin_DRJ_corowa_calculated <- bind_rows(corowa_DRJ_packaging_650301_11901816_calculated, corowa_DRJ_packaging_margin_650311_11901816_calculated)
```

## Laverton Packaging and Pallet Expense Account

### Edible Offal

```{r}
# Standardise the data
offal_laverton_packaging_650301_10001854_new_std <- offal_laverton_packaging_650301_10001854_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

# Standardise the data
offal_laverton_pallet_650303_10001854_new_std <- offal_laverton_pallet_650303_10001854_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

# Prepare the edible offal volume data
laverton_edible_offal_volume_data <- volume_bone_raw %>% 
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(Type %in% c("OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    Period         = match(Month, toupper(month.name)),
    `Customer Group`  = case_when(
      Type == "OFFALS"      ~ "Edible Offal",
      Type == "BACON CUTS"  ~ "Edible Offal",
      TRUE ~ NA_character_
    )
  ) 

# Apply the function created in corowa section to add missing price using other variants
laverton_edible_offal_volume_packaging_calculated <- join_packaging_price(laverton_edible_offal_volume_data, "PACKAGING", variant = 3)
laverton_edible_offal_volume_pallet_calculated    <- join_packaging_price(laverton_edible_offal_volume_data, "PALLETS",   variant = 3)

# Join the calculated value with the account to create the final data
offal_laverton_packaging_650301_10001854_calculated <- offal_laverton_packaging_650301_10001854_new_std %>%
  left_join(
    laverton_edible_offal_volume_packaging_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

# Join the calculated value with the account to create the final data
offal_laverton_pallet_650303_10001854_calculated <- offal_laverton_pallet_650303_10001854_new_std %>%
  left_join(
    laverton_edible_offal_volume_pallet_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

all_expense_packaging_pallet_edible_offal_laverton_calculated <- bind_rows(offal_laverton_packaging_650301_10001854_calculated, offal_laverton_pallet_650303_10001854_calculated)
```

### 6 Way

```{r}
# Standardise the data
laverton_6way_packaging_frz_650301_10501854_new_std <- laverton_6way_packaging_frz_650301_10501854_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

laverton_6way_pallet_frz_650303_10501854_new_std <- laverton_6way_pallet_frz_650303_10501854_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

# Prepare the data
laverton_volume_6way_data <- volume_bone_raw %>%
  mutate(
    Tab         = toupper(Tab),
    Abattoir    = toupper(Abattoir),
    Month       = toupper(Month),
    Units       = as.numeric(Units),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code` = str_trim(`Item Code`)
  ) %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(toupper(Run) == "6 WAY") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = "6 Way",
    Period         = match(Month, toupper(month.name))
    ) 

# Add the price and calculating the value for 6way packaging
laverton_volume_6way_packaging_calculated <- laverton_volume_6way_data %>%
  select(-Price) %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PACKAGING) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  rename(Price = PACKAGING) %>%
  mutate(Value = `Total Weight` * Price)

# Add the price and calculating the value for 6way pallet
laverton_volume_6way_pallet_calculated <- laverton_volume_6way_data %>%
  select(-Price) %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PALLETS) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  rename(Price = PALLETS) %>%
  mutate(Value = `Total Weight` * Price)

# Join the calculated value with the account to create the final data
laverton_6way_packaging_frz_650301_10501854_calculated <- laverton_6way_packaging_frz_650301_10501854_new_std %>%
  left_join(
    laverton_volume_6way_packaging_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

# Join the calculated value with the account to create the final data
laverton_6way_pallet_frz_650303_10501854_calculated <- laverton_6way_pallet_frz_650303_10501854_new_std %>%
  left_join(
    laverton_volume_6way_pallet_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

all_expense_packaging_pallet_6way_laverton_calculated <- bind_rows(laverton_6way_packaging_frz_650301_10501854_calculated, laverton_6way_pallet_frz_650303_10501854_calculated)
```

### Commodity

```{r}
# Standardise the data
laverton_commodity_packaging_frz_650301_10501854_new_std <- laverton_commodity_packaging_frz_650301_10501854_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

laverton_commodity_pallet_frz_650303_10501854_new_std <- laverton_commodity_pallet_frz_650303_10501854_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

# Prepare the data
laverton_volume_commodity_data <- volume_bone_raw %>%
  mutate(
    Tab         = toupper(Tab),
    Abattoir    = toupper(Abattoir),
    Month       = toupper(Month),
    Units       = as.numeric(Units),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code` = str_trim(`Item Code`)
  ) %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(toupper(Run) == "COMMODITY BONE") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = "Commodity",
    Period         = match(Month, toupper(month.name))
    ) 

# Add the price and calculating the value for commodity packaging
laverton_volume_commodity_packaging_calculated <- laverton_volume_commodity_data %>%
  select(-Price) %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PACKAGING) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  rename(Price = PACKAGING) %>%
  mutate(Value = `Total Weight` * Price)

# Add the price and calculating the value for commodity pallet
laverton_volume_commodity_pallet_calculated <- laverton_volume_commodity_data %>%
  select(-Price) %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PALLETS) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  rename(Price = PALLETS) %>%
  mutate(Value = `Total Weight` * Price)

# Join the calculated value with the account to create the final data
laverton_commodity_packaging_frz_650301_10501854_calculated <- laverton_commodity_packaging_frz_650301_10501854_new_std %>%
  left_join(
    laverton_volume_commodity_packaging_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

# Join the calculated value with the account to create the final data
laverton_commodity_pallet_frz_650303_10501854_calculated <- laverton_commodity_pallet_frz_650303_10501854_new_std %>%
  left_join(
    laverton_volume_commodity_pallet_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

all_expense_packaging_pallet_commodity_laverton_calculated <- bind_rows(laverton_commodity_packaging_frz_650301_10501854_calculated, laverton_commodity_pallet_frz_650303_10501854_calculated)
```

### Sow

```{r}
laverton_sow_packaging_fee <- 0.095
# Standardise the data
laverton_sow_packaging_frz_650301_10501854_new_std <- laverton_sow_packaging_frz_650301_10501854_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

laverton_sow_pallet_frz_650303_10501854_new_std <- laverton_sow_pallet_frz_650303_10501854_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

# Prepare the data
laverton_volume_sow_data <- volume_bone_raw %>%
  mutate(
    Tab         = toupper(Tab),
    Abattoir    = toupper(Abattoir),
    Month       = toupper(Month),
    Units       = as.numeric(Units),
    `Total Weight` = as.numeric(`Total Weight`),
    `Item Code` = str_trim(`Item Code`)
  ) %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(toupper(Run) == "SOW BONE") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = "Sow",
    Period         = match(Month, toupper(month.name))
    ) 

# Add the price and calculating the value for sow packaging
laverton_volume_sow_packaging_calculated <- laverton_volume_sow_data %>%
  select(-Price) %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PACKAGING) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  rename(Price = PACKAGING) %>%
  # TEMPORARY: sow packaging price is missing from packaging_price_data (VARIANT == 4)
  # Replace with custom fee until fixed
  mutate(Price = laverton_sow_packaging_fee) %>%
  mutate(Value = `Total Weight` * Price)

# Add the price and calculating the value for sow pallet
laverton_volume_sow_pallet_calculated <- laverton_volume_sow_data %>%
  select(-Price) %>%
  left_join(
    packaging_price_data %>%
      filter(VARIANT == 4) %>%
      select(BOM, PALLETS) %>%
      mutate(BOM = as.character(BOM)),
    by = c("Item Code" = "BOM")
  ) %>%
  rename(Price = PALLETS) %>%
  mutate(Value = `Total Weight` * Price)

# Join the calculated value with the account to create the final data
laverton_sow_packaging_frz_650301_10501854_calculated <- laverton_sow_packaging_frz_650301_10501854_new_std %>%
  left_join(
    laverton_volume_sow_packaging_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

# Join the calculated value with the account to create the final data
laverton_sow_pallet_frz_650303_10501854_calculated <- laverton_sow_pallet_frz_650303_10501854_new_std %>%
  left_join(
    laverton_volume_sow_pallet_calculated %>%
      group_by(Tab, Abattoir, Month, Period, `Customer Group`) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        Value          = sum(Value, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)

all_expense_packaging_pallet_sow_laverton_calculated <- bind_rows(laverton_sow_packaging_frz_650301_10501854_calculated, laverton_sow_pallet_frz_650303_10501854_calculated)
```

### Export

```{r}
export_packaging_fee <- 12.30
# Pre-standardise keys once
laverton_export_packaging_650301_10201854_new_std <- laverton_export_packaging_650301_10201854_new %>%
  mutate(
    `SOP Unicode` = toupper(`SOP Unicode`),
    BU            = toupper(BU),
    Abattoir      = toupper(Abattoir),
    Month         = toupper(month.name[Period])
  ) 

# Join volume_farm_raw on SOP Unicode
laverton_export_packaging_650301_10201854_calculated <- laverton_export_packaging_650301_10201854_new_std %>%
  left_join(
    volume_farm_raw %>%
      filter(Service == "Kill") %>% 
      mutate(
        Unicode        = toupper(Unicode),
        Abattoir       = toupper(Abattoir),
        Month          = toupper(Month),
        Tab            = toupper(Tab),
        Units          = as.numeric(Units),
        `Avg Weight`   = as.numeric(`Avg Weight`),
        `Total Weight` = as.numeric(`Total Weight`)
      ) %>%
      group_by(Unicode, Month) %>%
      summarise(
        Units          = sum(Units, na.rm = TRUE),
        `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
        `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("SOP Unicode" = "Unicode", "Month")
  ) %>%
  mutate(Value = Units * export_packaging_fee) %>%
  mutate(Value = -Value)


all_expense_packaging_export_laverton_calculated <- laverton_export_packaging_650301_10201854_calculated
```

## Trade Allowance Expense

### 3.Meat Sales

```{r}
trade_allowance_meat_sales_volume <- all_revenue_meat_sales  %>%
  left_join(
    trade_allowance_data %>% select(Period, Brand, `Trade Spend %`, `Trade Spend Value`),
    by = c("Period", "Customer name" = "Brand")
  ) %>%
  mutate(
    `Trade Spend %`     = replace_na(`Trade Spend %`, 0),
    `Trade Spend Value` = replace_na(`Trade Spend Value`, 0)
  ) %>%
  mutate(
    `Trade Spend % Calculated`     = `Trade Spend %` * Value,
    `Trade Spend Value Calculated` = `Trade Spend Value`,
    Value                          = `Trade Spend % Calculated` + `Trade Spend Value Calculated`
  ) %>%
  group_by(Tab, Abattoir, Month, Period, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  )

trade_allowance_meat_sales_calculated <- trade_allowance_meat_sales_450050_10001814_new %>%
  left_join(
    trade_allowance_meat_sales_volume %>% select(-Tab, -Abattoir),
    by = c("Customer name", "Period")
  ) %>%
  mutate(Value = -Value)
```

### 6.Laverton Processing

```{r}
rebates_BE_camp <- 5.80
laverton_trade_allowance_volume <- volume_farm_raw %>% 
  filter(Tab == "Kill") %>% 
  filter(Abattoir == "LAVERTON") %>% 
  filter(`Customer name` %in% c("BE Campbells Bacon", "B.E. Campbell"))

laverton_trade_allowance_calculated <- laverton_trade_allowance_volume %>%
  mutate(
    Units = as.numeric(Units),
    Period = match(toupper(Month), toupper(month.name)),
    Value = Units * rebates_BE_camp
  ) %>%
  group_by(Tab, Abattoir, Month, Period, `Customer name`) %>%
  summarise(
    Units = sum(Units, na.rm = TRUE),
    Value = sum(Value, na.rm = TRUE),
    .groups = "drop"
  )

trade_allowance_laverton_calculated <- laverton_trade_allowance_450050_10201854_new %>%
  left_join(
    laverton_trade_allowance_calculated %>% select(-Tab, -Abattoir),
    by = c("Customer name", "Period")
  ) %>%
  mutate(Value = -Value)
```

```{r}
all_expense_trade_allowance_calculated <- bind_rows(trade_allowance_meat_sales_calculated, trade_allowance_laverton_calculated)
```

## Storage Expense Account

### Parameters

```{r}
corowa_hold_volume <- 1100000
laverton_hold_volume <- 200000
value_add_hold_volume <- 60000
cost_in_rate <- 0.14
cost_out_rate <- 0.08
hold_cost_rate <- 0.01
```

### Corowa Frozen Stock

#### Offal

```{r}
# Prepare the data for frozen offal
volume_offal_frz_corowa <- volume_bone_price_calculated %>%
  # Add condition to filter frozen offal only
  filter(`Storage` == "FROZEN") %>% 
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(Type %in% c("INEDIBLE", "OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = case_when(
      Type == "INEDIBLE"    ~ "Inedible Offal",
      Type == "OFFALS"      ~ "Edible Offal",
      Type == "BACON CUTS"  ~ "Edible Offal",
      TRUE ~ NA_character_
    )
  ) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  filter(`Customer Group` == "Edible Offal")

# Pre-standardise keys once
edible_offal_storage_730010_10001816_new_std <- edible_offal_storage_730010_10001816_new %>%
  mutate(
    BU       = toupper(BU),
    Abattoir = toupper(Abattoir),
    Month    = toupper(month.name[Period])
  )

# Calculate storage value split by Cost Type (doubles rows)
volume_offal_storage_corowa <- bind_rows(
  volume_offal_frz_corowa %>% mutate(`Cost Type` = "Cost In",  Value = `Total Weight` * cost_in_rate),
  volume_offal_frz_corowa %>% mutate(`Cost Type` = "Cost Out", Value = `Total Weight` * cost_out_rate)
) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Cost Type`) %>%
  summarise(
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  mutate(`Total Weight` = if_else(`Cost Type` == "Cost Out", 0, `Total Weight`))


# Join the calculated storage value with the account
edible_offal_storage_730010_10001816_calculated <- edible_offal_storage_730010_10001816_new_std %>%
  left_join(
    volume_offal_storage_corowa,
    by = c("BU" = "Tab", "Abattoir", "Month", "Customer Group")
  )
```

#### Commodity

```{r}
# Prepare the frozen data for commodity
volume_commodity_frz_corowa_400000_calculated <- volume_commodity_corowa_400000_calculated %>% 
  filter(`Storage` == "FROZEN")

# Pre-standardise keys once
corowa_commodity_frz_storage_7300100_10501816_new_std <- corowa_commodity_frz_storage_7300100_10501816_new %>%
  mutate(
    BU       = toupper(BU),
    Abattoir = toupper(Abattoir),
    Month    = toupper(month.name[Period])
  )

# Calculate storage value split by Cost Type (doubles rows)
volume_commodity_storage_corowa <- bind_rows(
  volume_commodity_frz_corowa_400000_calculated %>% mutate(`Customer Group` = "Commodity", `Cost Type` = "Cost In",  Value = `Total Weight` * cost_in_rate),
  volume_commodity_frz_corowa_400000_calculated %>% mutate(`Customer Group` = "Commodity", `Cost Type` = "Cost Out", Value = `Total Weight` * cost_out_rate)
) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Cost Type`) %>%
  summarise(
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  mutate(`Total Weight` = if_else(`Cost Type` == "Cost Out", 0, `Total Weight`))

# Join the calculated storage value with the account
corowa_commodity_frz_storage_7300100_10501816_calculated <- corowa_commodity_frz_storage_7300100_10501816_new_std %>%
  left_join(
    volume_commodity_storage_corowa,
    by = c("BU" = "Tab", "Abattoir", "Month", "Customer Group")
  )
```

#### 6 Way

```{r}
# Prepare the data for frozen 6Way item only
volume_6way_frz_corowa <- volume_bone_price_calculated %>%
  filter(`Storage` == "FROZEN") %>% 
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "COROWA") %>%
  filter(toupper(Run) == "6 WAY") %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group`  = "6 Way"
    ) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  )

# Pre-standardise keys once
corowa_6way_frz_storage_730010_10501816_new_std <- corowa_6way_frz_storage_730010_10501816_new %>%
  mutate(
    BU       = toupper(BU),
    Abattoir = toupper(Abattoir),
    Month    = toupper(month.name[Period])
  )

# Calculate storage value split by Cost Type (doubles rows)
volume_6way_storage_corowa <- bind_rows(
  volume_6way_frz_corowa %>% mutate(`Cost Type` = "Cost In",  Value = `Total Weight` * cost_in_rate),
  volume_6way_frz_corowa %>% mutate(`Cost Type` = "Cost Out", Value = `Total Weight` * cost_out_rate)
) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Cost Type`) %>%
  summarise(
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  mutate(`Total Weight` = if_else(`Cost Type` == "Cost Out", 0, `Total Weight`))

# Join the calculated storage value with the account
corowa_6way_frz_storage_730010_10501816_calculated <- corowa_6way_frz_storage_730010_10501816_new_std %>%
  left_join(
    volume_6way_storage_corowa,
    by = c("BU" = "Tab", "Abattoir", "Month", "Customer Group")
  )
```

#### Meat Trade

```{r, eval=FALSE}
# Prepare the data for Meat Trade (only Frozen)
volume_meat_trade_6way_frz <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(toupper(Run) %in% c("6 WAY")) %>%
  filter(`Storage` == "FROZEN") %>% 
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group` = "Meat Trade",
    `Customer name`  = "Meat Trade") %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  mutate(Period = match(Month, toupper(month.name))) %>% 
  mutate(Service = "6 Way")

volume_meat_trade_commodity_frz <- volume_meat_trade_commodity

volume_meat_trade_edible_offal_frz <- volume_bone_price_calculated %>%
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(Type %in% c("OFFALS", "BACON CUTS")) %>%
  filter(toupper(Run) == "TOTAL KILL") %>%
  filter(`Storage` == "FROZEN") %>% 
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group` = "Meat Trade",
    `Customer name`  = "Meat Trade") %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Period = match(Month, toupper(month.name))) %>% 
  mutate(Service = "Edible Offal")

volume_meat_trade_frz_combined <- bind_rows(volume_meat_trade_6way_frz, volume_meat_trade_commodity_frz, volume_meat_trade_edible_offal_frz) %>% 
  mutate(Abattoir = "COROWA") %>% # remap Laverton → Corowa
  mutate(Tab = "2.MEAT PROCESSING")
```

```{r}
# Pre-standardise keys once
meat_trade_storage_data_new_std <- meat_trade_storage_data_new %>%
  mutate(
    BU       = toupper(BU),
    Abattoir = toupper(Abattoir),
    Month    = toupper(month.name[Period])
  )

# Calculate storage value split by Cost Type (doubles rows)
volume_meat_trade_storage <- bind_rows(
  volume_meat_trade_combined %>% mutate(`Cost Type` = "Cost In",  Value = `Total Weight` * cost_in_rate),
  volume_meat_trade_combined %>% mutate(`Cost Type` = "Cost Out", Value = `Total Weight` * cost_out_rate)
) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Cost Type`) %>%
  summarise(
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  mutate(`Total Weight` = if_else(`Cost Type` == "Cost Out", 0, `Total Weight`))

# Join the calculated storage value with the account
# distinct() on join keys to avoid row multiplication from multiple Service rows per month
meat_trade_storage_data_calculated <- meat_trade_storage_data_new_std %>%
  distinct(BU, Abattoir, Month, Period, `Customer Group`, .keep_all = TRUE) %>%
  left_join(
    volume_meat_trade_storage,
    by = c("BU" = "Tab", "Abattoir", "Month", "Customer Group")
  )
```

### Laverton Frozen Stock

#### Sow

```{r}
# Prepare the frozen sow data for laverton
volume_sow_frz_laverton <- volume_bone_price_calculated %>%
  # Another condition to filter frozen item
  filter(`Storage` == "FROZEN") %>% 
  mutate(Type = toupper(Type)) %>%
  filter(toupper(Abattoir) == "LAVERTON") %>%
  filter(toupper(Run) %in% c("6 WAY", "SOW BONE")) %>%
  mutate(
    Unicode           = toupper(Unicode),
    Abattoir          = toupper(Abattoir),
    Month             = toupper(Month),
    Tab               = toupper(Tab),
    Units             = as.numeric(Units),
    `Avg Weight`      = as.numeric(`Avg Weight`),
    `Total Weight`    = as.numeric(`Total Weight`),
    `Customer Group` = case_when(
    toupper(Run) == "6 WAY" ~ "6 Way",
    toupper(Run) == "SOW BONE"   ~ "Sow",
    TRUE ~ NA_character_
    )) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Customer name`) %>%
  summarise(
    Units          = sum(Units, na.rm = TRUE),
    `Avg Weight`   = mean(`Avg Weight`, na.rm = TRUE),
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Value = if_else(`Customer Group` == "6 Way", Value - 0.51 * `Total Weight`, Value)) %>%
  filter(`Customer Group` == "Sow") 

# Pre-standardise keys once
laverton_sow_frz_storage_730010_10501854_new_std <- laverton_sow_frz_storage_730010_10501854_new %>%
  mutate(
    BU       = toupper(BU),
    Abattoir = toupper(Abattoir),
    Month    = toupper(month.name[Period])
  )

# Calculate storage value split by Cost Type (doubles rows)
volume_sow_storage_laverton <- bind_rows(
  volume_sow_frz_laverton %>% mutate(`Cost Type` = "Cost In",  Value = `Total Weight` * cost_in_rate),
  volume_sow_frz_laverton %>% mutate(`Cost Type` = "Cost Out", Value = `Total Weight` * cost_out_rate)
) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Cost Type`) %>%
  summarise(
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  mutate(`Total Weight` = if_else(`Cost Type` == "Cost Out", 0, `Total Weight`))

# Join the calculated storage value with the account
laverton_sow_frz_storage_730010_10501854_calculated <- laverton_sow_frz_storage_730010_10501854_new_std %>%
  left_join(
    volume_sow_storage_laverton,
    by = c("BU" = "Tab", "Abattoir", "Month", "Customer Group")
  )
```

### Value Add

```{r}
# Pre-standardise keys once
meat_sales_storage_730010_10001814_new_std <- meat_sales_storage_730010_10001814_new %>%
  mutate(
    Abattoir = "Value Add",
    BU       = toupper(BU),
    Abattoir = toupper(Abattoir),
    Month    = toupper(month.name[Period])
  ) 

# Calculate storage value split by Cost Type (doubles rows)
volume_meat_sales_storage <- bind_rows(
  all_revenue_meat_sales %>% mutate(`Cost Type` = "Cost In",  Value = `Total Weight` * cost_in_rate),
  all_revenue_meat_sales %>% mutate(`Cost Type` = "Cost Out", Value = `Total Weight` * cost_out_rate)
) %>%
  group_by(Tab, Abattoir, Month, `Customer Group`, `Cost Type`) %>%
  summarise(
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  mutate(`Total Weight` = if_else(`Cost Type` == "Cost Out", 0, `Total Weight`))

# Join the calculated storage value with the account
meat_sales_storage_730010_10001814_calculated <- meat_sales_storage_730010_10001814_new_std %>%
  left_join(
    volume_meat_sales_storage,
    by = c("BU" = "Tab", "Abattoir", "Month", "Customer Group")
  ) %>% 
  mutate(Value = 0)
# Special adjustment temporary
```

### Hold Stock Cost

```{r}
corowa_stock_on_hand_730010_10501816_calculated <- corowa_stock_on_hand_730010_10501816_new %>%
  mutate(
    `Total Weight` = corowa_hold_volume,
    Value          = `Total Weight` * hold_cost_rate
  )

laverton_stock_on_hand_730010_10501854_calculated <- laverton_stock_on_hand_730010_10501854_new %>%
  mutate(
    `Total Weight` = laverton_hold_volume,
    Value          = `Total Weight` * hold_cost_rate
  )

value_add_stock_on_hand_730010_10001814_calculated <- value_add_stock_on_hand_730010_10001814_new %>%
  mutate(
    `Total Weight` = value_add_hold_volume,
    Value          = `Total Weight` * hold_cost_rate
  )
```

### Join all storage cost

```{r}
all_expense_storage_calculated <- bind_rows(
  edible_offal_storage_730010_10001816_calculated,
  corowa_commodity_frz_storage_7300100_10501816_calculated,
  corowa_6way_frz_storage_730010_10501816_calculated,
  meat_trade_storage_data_calculated,
  laverton_sow_frz_storage_730010_10501854_calculated,
  meat_sales_storage_730010_10001814_calculated,
  corowa_stock_on_hand_730010_10501816_calculated,
  laverton_stock_on_hand_730010_10501854_calculated,
  value_add_stock_on_hand_730010_10001814_calculated
) %>% 
  mutate(Value = -Value)
```

## Freight Out Account

### Value Add

```{r}
# Standardise freight out account keys
freight_out_500192_10001814_new_std <- freight_out_500192_10001814_new %>%
  mutate(
    Abattoir = "VALUE ADD",
    BU       = toupper(BU),
    Abattoir = toupper(Abattoir),
    Month    = toupper(month.name[Period])
  )

# Calculate freight out value per customer group using $/kg Rate
volume_freight_out_meat_sales <- all_revenue_meat_sales %>%
  left_join(
    rates_and_allocation_data %>% select(Brand, `Cost Type` = State, `$/kg Rate`, `%`),
    by = c("Customer Group" = "Brand")
  ) %>%
  mutate(
    `$/kg Rate`    = as.numeric(replace_na(`$/kg Rate`, 0)),
    `%`            = as.numeric(replace_na(`%`, 0)),
    `Total Weight` = `Total Weight` * `%`,
    Value          = `Total Weight` * `$/kg Rate`
  ) %>%
  group_by(Tab, Abattoir, Month, Period, `Customer Group`, `Cost Type`) %>%
  summarise(
    `Total Weight` = sum(`Total Weight`, na.rm = TRUE),
    Value          = sum(Value, na.rm = TRUE),
    .groups = "drop"
  )

# Join calculated freight value with the GL account structure
freight_out_500192_10001814_calculated <- freight_out_500192_10001814_new_std %>%
  left_join(
    volume_freight_out_meat_sales,
    by = c("BU" = "Tab", "Abattoir", "Month", "Period", "Customer Group")
  ) %>%
  mutate(Value = -Value)
```

# Rejoin all calculated data together before writing it down

```{r}
final_file <- bind_rows(
  all_revenue_offal_data_calculated,
  all_revenue_farm_calculated,
  all_revenue_6way_sow_data_calculated,
  all_revenue_commodity_corowa_calculated,
  all_revenue_commodity_laverton_calculated,
  all_revenue_meat_trade_data_calculated,
  all_revenue_meat_sales_data_calculated,
  all_expense_new_team_calculated,
  all_expense_corowa_laverton_expense_farm,
  all_expense_meat_trade_laverton_corowa_calculated,
  all_expense_meat_sales_internal_external_calculated,
  all_expense_packaging_pallet_meat_sales_calculated,
  all_expense_packaging_pallet_edible_offal_corowa_calculated,
  all_expense_packaging_pallet_6way_corowa_calculated,
  all_expense_packaging_pallet_commodity_corowa_calculated,
  all_expense_packaging_margin_woolworth_corowa_calculated,
  all_expense_packaging_margin_DRJ_corowa_calculated,
  all_expense_packaging_pallet_edible_offal_laverton_calculated,
  all_expense_packaging_pallet_6way_laverton_calculated,
  all_expense_packaging_pallet_commodity_laverton_calculated,
  all_expense_packaging_pallet_sow_laverton_calculated,
  all_expense_packaging_export_laverton_calculated,
  all_expense_trade_allowance_calculated,
  all_expense_storage_calculated,
  freight_out_500192_10001814_calculated
)
```

# Write down the file

```{r}
write.csv(final_file, "GL_DB Template.csv", row.names = FALSE)
```
